---
title: "01_datawrangling"
author: "Lena Kuschel"
date: "13 October 2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Library
```{r Library}
library(car)
library(psych)
library(ggplot2)
library(formr)
library(dplyr)
library(codebook)
```


## Data
Load selected data based on 00_dataimport
```{r Data}
fulldata_selected_lim = read.csv(file = "fulldata_selected_lim.csv")[,-1]
```


## Inspect Data
```{r Inspect Data}
colnames(fulldata_selected_lim)

fulldata_selected_lim_wrangled = fulldata_selected_lim
```


### Age
Participants younger than 18 were able to insert age but the survey was ended for them afterwards.
```{r Age}
table(fulldata_selected_lim_wrangled$age)
```
Set all numbers > 100 as missing:
```{r Age 2}
sum(fulldata_selected_lim_wrangled$age > 100)
# This means that age is set as missing for 15 people (for the limited data frame 0 people)

fulldata_selected_lim_wrangled = fulldata_selected_lim_wrangled %>%
  mutate(age = ifelse(age > 100, NA, age))

table(is.na(fulldata_selected_lim_wrangled$age))

table(fulldata_selected_lim_wrangled$age < 18)
# 26638 people were not allowed to participate in the survey because they were younger than 18 (for the limited data frame 15 people)
```

### Political Orientation
Political Orientation item should range from 0 to 6
```{r Political Orientation}
fulldata_selected_lim_wrangled %>%
  select("political_orientation") %>%
  lapply(table)

qplot(fulldata_selected_lim_wrangled$political_orientation)
#Political orientation ranges from 0 to 6 
```

### Preferred Relationship Options
Interest in being single, interest in sexual (non-romantic) relationships, interest in non-monogamous relationships and interest in monogamous relationships items should range from 0 to 6 
```{r Preferred Relationship Options}
fulldata_selected_lim_wrangled %>%
  select(starts_with("interest_")) %>%
  lapply(table)

qplot(fulldata_selected_lim_wrangled$interest_single)
qplot(fulldata_selected_lim_wrangled$interest_sexrel)
qplot(fulldata_selected_lim_wrangled$interest_nonmonrel)
qplot(fulldata_selected_lim_wrangled$inteterst_monrel)
# variables for preferred relationship options range from 0 to 6 
```
@PROBLEM @Laura Variable interest monogamous relationships ist im limitierten Datensatz falsch geschrieben 

### Political, ethnical, religious similarity
Preferences for political, ethnical and religious similarity items should range from 0 to 6 
```{r Political, ethnical and religious similarity}
fulldata_selected_lim_wrangled %>%
  select("pref_politicalsim", "pref_ethnicalsim", "pref_religioussim") %>%
  lapply(table)

qplot(fulldata_selected_lim_wrangled$pref_politicalsim)
qplot(fulldata_selected_lim_wrangled$pref_ethnicalsim)
qplot(fulldata_selected_lim_wrangled$pref_religioussim)

#Political, ethnical and religious similarity all range from 0 to 6 
```

### Ideal Partner Preferences
All ideal partner preference items should range from 0 to 6 
```{r Ideal Partner Preferences}
fulldata_selected_lim_wrangled %>%
  select(starts_with("pref_")) %>%
  select(-pref_politicalsim, -pref_ethnicalsim, -pref_religioussim) %>%
  lapply(table)

qplot(fulldata_selected_lim_wrangled$pref_level_kind)
qplot(fulldata_selected_lim_wrangled$pref_level_supportive)
qplot(fulldata_selected_lim_wrangled$pref_level_attractive_body)
qplot(fulldata_selected_lim_wrangled$pref_level_attractive_face)
qplot(fulldata_selected_lim_wrangled$pref_level_financially_secure)
qplot(fulldata_selected_lim_wrangled$pref_level_successful_ambitous)
qplot(fulldata_selected_lim_wrangled$pref_level_confident)
qplot(fulldata_selected_lim_wrangled$pref_level_assertive)
qplot(fulldata_selected_lim_wrangled$pref_level_intelligence)
qplot(fulldata_selected_lim_wrangled$pref_level_educated)

# I presume that all items range from 0 to 6 (here in the limited data frame some have a smaller range)

fulldata_selected_lim_wrangled %>%
  select(starts_with("pref_")) %>%
  select(-pref_politicalsim, -pref_ethnicalsim, -pref_religioussim) %>%
  md_pattern()
```


### Ideal Age and Ideal Height
## Importance Age
Item should range from 0 to 6 
```{r Importance Age}
fulldata_selected_lim_wrangled %>%
  select("imp_age") %>%
  lapply(table)

qplot(fulldata_selected_lim_wrangled$imp_age)

#Importance Age item ranges from 0 to 6 
```

## Ideal Age
This item is in open format style
```{r Ideal Age}
fulldata_selected_lim_wrangled %>%
  select("ideal_age") %>%
  lapply(table)

qplot(fulldata_selected_lim_wrangled$ideal_age)
#Ideal Age item ranges from 15 to 45 (in limited data frame)
```
Variable ideal_age was not restricted to a reasonable number, thus numbers larger than 100 were possible. To deal with this we will set all numbers >= 100 as missing.
```{r Ideal Age 2}
sum(fulldata_selected_lim_wrangled$ideal_age > 100, na.rm = T)
# This means that ideal_age is set as missing for 0 people (for limited data frame)


fulldata_selected_lim_wrangled = fulldata_selected_lim_wrangled %>%
  mutate(ideal_age = ifelse(ideal_age > 100, NA, ideal_age))
          
table(is.na(fulldata_selected_lim_wrangled$ideal_age))

fulldata_selected_lim_wrangled %>%
  select(ideal_age) %>%
  lapply(table)

qplot(fulldata_selected_lim_wrangled$ideal_age)
```


## Importance Height
Item should range from 0 to 6 
```{r Importance Height}
fulldata_selected_lim_wrangled %>%
  select("imp_height") %>%
  lapply(table)

qplot(fulldata_selected_lim_wrangled$imp_height)
#Importance Height item ranges from 0 to 6
```

##Ideal Height
Item has the options: much shorter than me, shorter than me, around the same height as me, taller than me, much taller than me
```{r Ideal Height}
# Transforming variable ideal_height in a numeric variable
#as factor
fulldata_selected_lim_wrangled$ideal_height <- as.factor(fulldata_selected_lim_wrangled$ideal_height)

# much shorter than me = -2, shorter than me = -1, around the same height as me = 0, taller than me = 1, much taller than me = 2 

recode(fulldata_selected_lim_wrangled$ideal_height, 'much shorter than me' = -2,'shorter than me' = -1, 'around the same height as me' = 0, 'taller than me' = 1, 'much taller than me' = 2, .default = NULL, .missing = NULL)


fulldata_selected_lim_wrangled$ideal_height <- as.numeric(fulldata_selected_lim_wrangled$ideal_height)
#hier nimmt R scheinbar willkürliche Werte statt die oben mir recode() zugewiesenen 


fulldata_selected_lim_wrangled %>%
  select("ideal_height") %>%
  lapply(table)

qplot(fulldata_selected_lim_wrangled$ideal_height)
```
@PROBLEM: imp_height still needs to be transformed to a numeric variable ranging from -2 to 2 

### Country
```{r Country}
table(fulldata_selected_lim_wrangled$country)
table(is.na(fulldata_selected_lim_wrangled$country))
# in the limited data set FALSE in 100 cases -> no n.a. 
```

### Language
Chinese, Danish, English, French, German, Japanese, Portuguese, Russian, Spanish, Italian
```{r Language}
table(fulldata_selected_lim_wrangled$language)
table(is.na(fulldata_selected_lim_wrangled$country))
# in the limited data set 100 participants, who answered the survey in russian. FALSE in 100 cases -> no n.a.
```

### Sex
Categories: Woman; Genderqueer/Nonbinary; Man; None of the above; Prefer not to say; Other
```{r Sex}
table(fulldata_selected_lim_wrangled$sex)
# 15 missing values in limited data set, Genderqueer/Nonbinary:2, Man: 6, Prefer not to say: 1, Woman: 76

# Set missing values as NA
fulldata_selected_lim_wrangled = fulldata_selected_lim_wrangled %>%
  mutate(sex = as.character(sex),
         sex = ifelse(sex == "", NA, sex),
         sex = factor(sex))

table(fulldata_selected_lim_wrangled$sex)

table(is.na(fulldata_selected_lim_wrangled$sex))
# in the limited data set, 15 NA for sex
```

### Sexual Orientation
heterosexual; Lesbian/Gay/Homosexual; Bisexual/Pansexual; Queer; Asexual; Prefer not to say; Other
```{r Sexual Orientation}
table(fulldata_selected_lim_wrangled$sexual_orientation)
# in the limited dataset: 15 missing cases, bisexual/pansexual:11, Lesbian/Gay/Homosexual: 1, Other: 1, Prefer not to say:1, Straight/Heterosexual: 71

# Set missing values as NA
fulldata_selected_lim_wrangled = fulldata_selected_lim_wrangled %>%
  mutate(sexual_orientation = as.character(sexual_orientation),
         sexual_orientation = ifelse(sexual_orientation == "", NA, sexual_orientation),
         sexual_orientation = factor(sexual_orientation))

table(fulldata_selected_lim_wrangled$sexual_orientation)

table(is.na(fulldata_selected_lim_wrangled$sexual_orientation))
# true in 15 cases -> 15 NA for sexual orientation (in limited dataset)
```

### Relationship Variable
```{r Relationship variable}
table(fulldata_selected_lim_wrangled$relationship) #No romantic or sexual relationships during the past 3 months
table(fulldata_selected_lim_wrangled$relationship1) #Other
table(fulldata_selected_lim_wrangled$relationship2) #Short-term (casual) sexual relationship (e.g. hookups or one-night-stands)
table(fulldata_selected_lim_wrangled$relationship3) #New (less than 1 month old) romantic and/or sexual relationship 
table(fulldata_selected_lim_wrangled$relationship4) #Ongoing (longer than 1 month) uncommitted/non-exclusive romantic and/or sexual relationship
table(fulldata_selected_lim_wrangled$relationship5)#Long-term committed/exclusive sexual relationship with one or more partners

fulldata_selected_lim_wrangled = fulldata_selected_lim_wrangled %>%
  mutate(relationship = ifelse(relationship == "True",
                               "No romantic or sexual relationships during the past 3 months, ",
                               ""),
         relationship = ifelse(relationship1 == "True",
                               paste(relationship,
                                     "Other, "),
                               relationship),
         relationship = ifelse(relationship2 == "True",
                               paste(relationship,
                                     "Short-term (casual) sexual relationship (e.g. hookups or one-night-stands), "),
                               relationship),
         relationship = ifelse(relationship3 == "True",
                               paste(relationship,
                                     "New (less than 1 month old) romantic and/or sexual relationship, "),
                               relationship),
         relationship = ifelse(relationship4 == "True",
                               paste(relationship,
                                     "Ongoing (longer than 1 month) uncommitted/non-exclusive romantic and/or sexual relationship, "),
                               relationship),
         relationship = ifelse(relationship5 == "True", 
                               paste(relationship,
                                     "Long-term committed/exclusive sexual relationship with one or more partners, "), 
                               relationship),
         relationship = ifelse(relationship == "", NA, relationship))

table(fulldata_selected_lim_wrangled$relationship)

# Check whether command worked correctly
table(fulldata_selected_lim_wrangled$relationship %contains% "No romantic or sexual relationships during the past 3 months") 
#true in 26 cases, false in 57 cases -> for the limited data frame: 26 singles
```


### Answer accuracy
I took the survey seriously; please use my information in the study.; I did not answer seriously, please disregard my information; I choose not to answer
```{r Answer accuracy}
table(fulldata_selected_lim_wrangled$answer_accuracy)
# 25 missing cases, I choose not to answer:1, I did not answer seriously; please disregard my information: 1, I took the survey seriously; please use my information in the study:73

# Set missing values as NA
fulldata_selected_lim_wrangled = fulldata_selected_lim_wrangled %>%
  mutate(answer_accuracy = as.character(answer_accuracy),
         answer_accuracy = ifelse(answer_accuracy == "", NA, answer_accuracy),
         answer_accuracy = factor(answer_accuracy))

table(fulldata_selected_lim_wrangled$answer_accuracy)

table(is.na(fulldata_selected_lim_wrangled$answer_accuracy))
# false in 75 cases, true in 25 cases (25 NA)

fulldata_selected_lim_wrangled %>%
  select(sex, answer_accuracy) %>%
  md_pattern()
```


## Creating new variables for Ideal Partner Preferences
```{r}
fulldata_selected_lim_wrangled = fulldata_selected_lim_wrangled %>% 
  mutate(pref_level_kind_supportive = (pref_level_kind + pref_level_supportive)/2,
         pref_level_attractiveness = (pref_level_attractive_body +
                                        pref_level_attractive_face)/2,
         pref_level_financially_secure_successful_ambitious = (pref_level_financially_secure + pref_level_successful_ambitous)/2,
         pref_level_confident_assertive = (pref_level_confident + pref_level_assertive)/2, 
         pref_level_intelligence_educated = (pref_level_intelligence + pref_level_educated)/2)

table(fulldata_selected_lim_wrangled$pref_level_kind_supportive)
table(fulldata_selected_lim_wrangled$pref_level_attractiveness)
table(fulldata_selected_lim_wrangled$pref_level_financially_secure_successful_ambitious)
table(fulldata_selected_lim_wrangled$pref_level_confident_assertive)
table(fulldata_selected_lim_wrangled$pref_level_intelligence_educated)


qplot(fulldata_selected_lim_wrangled$pref_level_kind_supportive)
qplot(fulldata_selected_lim_wrangled$pref_level_attractiveness)
qplot(fulldata_selected_lim_wrangled$pref_level_financially_secure_successful_ambitious)
qplot(fulldata_selected_lim_wrangled$pref_level_confident_assertive)
qplot(fulldata_selected_lim_wrangled$pref_level_intelligence_educated)
```
@Laura item pref_level_successful_ambitious is written incorrectly in limited data frame (pref_level_successful_ambitous)

### Trying out a simple linear regression
```{r Trying out a simple linear regression}
lm(political_orientation ~ age, data = fulldata_selected_lim_wrangled)
```

## Save Data
```{r Save data}
write.csv(fulldata_selected_lim_wrangled, file = "fulldata_selected_lim_wrangled.csv")
```


