---
title: "02_exclusion"
author: "Lena Kuschel"
date: "19 October 2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Library
```{r Library}
library(formr)
library(dplyr)
```


## Data
Load selected data based on 01_datawrangling
```{r Data}
fulldata_selected_wrangled = read.csv(file = "fulldata_selected_wrangled.csv")[,-1]
```

## Exclusion Process
```{r Exclusion Process}
data_included = fulldata_selected_wrangled
```

### All participants younger than 18
In total, we will exclude `r sum(fulldata_selected_wrangled$age < 18, na.rm = T)` participants because they are younger than 18.
```{r Age}
data_included = fulldata_selected_wrangled %>%
  filter(age >= 18 |
         is.na(age))

table(is.na(data_included$age))
```

### All participants who do not identify as women
In total, we will exclude `r sum(fulldata_selected_wrangled$sex == "Man", fulldata_selected_wrangled$sex == "Genderqueer/Nonbinary", fulldata_selected_wrangled$sex == "None of the above", fulldata_selected_wrangled$sex == "Prefer not to say", fulldata_selected_wrangled$sex == "Other", na.rm = T)` participants because they did not identify as women (Men, Genderqueer/Nonbinary; None of the above; Prefer not to say; Other)

Consecutively, this means we will exclude `r sum(data_included$sex == "Man", data_included$sex == "Genderqueer/Nonbinary", data_included$sex == "None of the above", data_included$sex == "Prefer not to say", data_included$sex == "Other", na.rm = T)` participants because they did not identify as women (Men, Genderqueer/Nonbinary; None of the above; Prefer not to say; Other)

```{r Sex}
table(data_included$sex)

data_included = data_included %>%
  filter((sex != "Man" &
         sex != "Genderqueer/Nonbinary" &
         sex != "None of the above" &
         sex != "Prefer not to say" &
         sex != "Other")  |
         is.na(sex))

table(data_included$sex)
table(is.na(data_included$sex))
```


### All participants who do not identify as heterosexual
In total, we will exclude `r sum(fulldata_selected_wrangled$sexual_orientation == "Lesbian/Gay/Homosexual", fulldata_selected_wrangled$sexual_orientation == "Bisexual/Pansexual", fulldata_selected_wrangled$sexual_orientation == "Queer", fulldata_selected_wrangled$sexual_orientation == "Asexual", fulldata_selected_wrangled$sexual_orientation == "Prefer not to say", fulldata_selected_wrangled$sexual_orientation == "Other", na.rm = T)` participants because they did not identify as heterosexual (Lesbian/Gay/Homosexual; Bisexual/Pansexual; Queer; Asexual; Prefer not to say; Other)

Consecutively, this means we will exclude `r sum(data_included$sexual_orientation == "Lesbian/Gay/Homosexual", data_included$sexual_orientation == "Bisexual/Pansexual", data_included$sexual_orientation == "Queer", data_included$sexual_orientation == "Asexual", data_included$sexual_orientation == "Prefer not to say", data_included$sexual_orientation == "Other", na.rm = T)` participants because they did not identify as heterosexual (Lesbian/Gay/Homosexual; Bisexual/Pansexual; Queer; Asexual; Prefer not to say; Other)  
```{r Sexuality}
table(data_included$sexual_orientation)

data_included = data_included %>%
  filter((sexual_orientation != "Lesbian/Gay/Homosexual" & sexual_orientation != "Bisexual/Pansexual" &
         sexual_orientation != "Queer" & sexual_orientation != "Asexual" &
         sexual_orientation != "Prefer not to say" & sexual_orientation != "Other") |
         is.na(sexual_orientation))

table(data_included$sexual_orientation)
table(is.na(data_included$sexual_orientation)) 
```

### All participants who indicated being in a relationship
In total, we will exclude `r sum(fulldata_selected_wrangled$relationship %contains% "New (less than 1 month old) romantic and/or sexual relationship", fulldata_selected_wrangled$relationship %contains% "Ongoing (longer than 1 month) uncommitted/non-exclusive romantic and/or sexual relationship", fulldata_selected_wrangled$relationship %contains% "Long-term committed/exclusive sexual relationship with one or more partners", na.rm = T)` participants because they indicated being in a relationship (New (less than 1 month old) romantic and/or sexual relationship ; Ongoing (longer than 1 month) uncommitted/non-exclusive romantic and/or sexual relationship; Long-term committed/exclusive sexual relationship with one or more partners) and `r sum(fulldata_selected_wrangled$relationship %contains% "Other", na.rm = T)` participants where it was not sure whether they were currently single (Other).

Consecutively, we will exclude `r sum(data_included$relationship %contains% "New (less than 1 month old) romantic and/or sexual relationship", data_included$relationship %contains% "Ongoing (longer than 1 month) uncommitted/non-exclusive romantic and/or sexual relationship", data_included$relationship %contains% "Long-term committed/exclusive sexual relationship with one or more partners", na.rm = T)` participants because they indicated being in a relationship (New (less than 1 month old) romantic and/or sexual relationship ; Ongoing (longer than 1 month) uncommitted/non-exclusive romantic and/or sexual relationship; Long-term committed/exclusive sexual relationship with one or more partners) and `r sum(data_included$relationship %contains% "Other", na.rm = T)` participants where it was not sure whether they were currently single (Other).


```{r Relationship}
table(data_included$relationship)

data_included_test1 = data_included %>%
  filter((!(relationship %contains% "New (less than 1 month old) romantic and/or sexual relationship") &
         !(relationship %contains% "Ongoing (longer than 1 month) uncommitted/non-exclusive romantic and/or sexual relationship") &
         !(relationship %contains% "Long-term committed/exclusive sexual relationship with one or more partners") &
         !(relationship %contains% "Other")) |
         is.na(relationship))

table(data_included_test1$relationship)
table(is.na(data_included_test1$relationship))
```

#### Relationship check: With old relationships variable
Just to make sure, that our data wrangling earlier worked, we will check the exclusion process based on old relationships variable
```{r Relationship Check}
data_included_test2 = data_included %>%
  filter(relationship1 != "True") %>%
  filter(relationship3 != "True") %>%
  filter(relationship4 != "True") %>%
  filter(relationship5 != "True")

data_included = data_included_test1 %>%
  # Drop unneccessary relationship variables
  select(-relationship1, -relationship2, -relationship3, -relationship4, -relationship5) 
```

### All participants who did not specify their political orientation
```{r Political Orientation}
data_included = data_included %>%
  mutate(political_orientation = ifelse(political_orientation == "", NA, political_orientation))

table(is.na(data_included$political_orientation))

data_included = data_included %>%
  filter(!is.na(political_orientation))
```

### All participants who did not answer the survey seriously or chose not to answer the seriousness question
In total, we will exclude `r sum(fulldata_selected_wrangled$answer_accuracy == "I did not answer seriously; please disregard my information.", fulldata_selected_wrangled$answer_accuracy == "I choose not to answer.", na.rm = T)` participants because they indicated not answering the survey seriously (I did not answer seriously, please disregard my information; I choose not to answer)

Consecutively, we will exclude `r sum(data_included$answer_accuracy == "I did not answer seriously; please disregard my information.", data_included$answer_accuracy == "I choose not to answer.", na.rm = T)` participants because they indicated not answering the survey seriously (I did not answer seriously, please disregard my information; I choose not to answer)

```{r Accuracy}
table(data_included$answer_accuracy)
data_included = data_included %>%
  filter((answer_accuracy != "I did not answer seriously; please disregard my information." &
         answer_accuracy != "I choose not to answer.") |
         is.na(answer_accuracy))
```

We have `r sum(is.na(data_included$answer_accuracy))` missings for answer_accuracy here. As mentioned in the preregistration, we will include these participants in our analyses.
```{r Accuracy Missings}
missings = data_included %>% filter(is.na(answer_accuracy))
```


## Save Data
```{r Save Data}
write.csv(data_included, file = "data_included.csv")
```
