---
title: <font color="#66C2A5">Main Analyses</font>
csl: apa-custom-no-issue.csl
output: 
  html_document:
    code_folding: "hide"
editor_options: 
  chunk_output_type: console
---

## {.tabset}

### Library
```{r Library}
library(formr)
library(effects)
library(effectsize)
#library(lme4)
library(sjstats)
library(lmerTest)
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(tidyverse)
library(mgcv)         
library(stringr)     
library(sandwich)     
library(lmtest) 
library(minqa)
```

### Data
Load selected data based on 03_codebook
```{r}
data_included_documented = read.csv(file = "data_included_documented.csv")[,-1]
```

### Analysis {.tabset .active}
If the model does not converge, we will first exclude the random slope for country. If the model does still not converge, we will subsequently exclude the random intercept for country.
Instead we will z-standardize outcomes separately for each country.

#### Preferred Relationship Options {.tabset}
##### S1 Interest in Single Life {.tabset}
H1a There is a negative linear link between right-wing political orientation and women’s interest in being single.  
Outcome: Ratings for interest in single life. Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_interest_single <- lmer(interest_single ~ political_orientation + (1+political_orientation|country), data = data_included_documented, control =lmerControl(optimizer = "bobyqa"))
```

###### Summary
```{r}
summary(model_interest_single)
confint(model_interest_single, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_interest_single, method = "basic", ci = 0.997)
```

###### Plot {.active}
```{r}
lmer(interest_single ~ political_orientation + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### S2 Interest in Sexual, Non-Romantic Relationships {.tabset}
H1b There is a negative linear link between right-wing political orientation and women’s interest in having sexual, non-romantic relationships (e.g., hookups, one-night stands).
Outcome: Ratings for interest in having sexual, non-romantic relationships. Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_interest_sexrel <- lmer(interest_sexrel ~ political_orientation + (1+political_orientation|country), data = data_included_documented, control =lmerControl(optimizer = "bobyqa"))
```

###### Summary
```{r}
summary(model_interest_sexrel)
confint(model_interest_sexrel, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_interest_sexrel, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_interest_sexrel, method = "basic"), ci = 0.997)
```

###### Plot {.active}
```{r}
lmer(interest_sexrel ~ political_orientation + (1 + political_orientation| country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### S3 Interest in Non-Monogamous Relationships {.tabset}
H1c There is a negative linear link between right-wing political orientation and women’s interest in having non-monogamous relationships.
Outcome: Ratings for interest in having non-monogamous relationships. Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_interest_nonmonrel <- lmer(interest_nonmonrel ~ political_orientation + (1+political_orientation|country), data = data_included_documented, control =lmerControl(optimizer = "bobyqa"))
```

###### Summary
```{r}
summary(model_interest_nonmonrel)
confint(model_interest_nonmonrel, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_interest_nonmonrel, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_interest_nonmonrel, method = "basic"), ci = 0.997)
```

###### Plot {.active}
```{r}
lmer(interest_nonmonrel ~ political_orientation + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### S4 Interest in Monogamous Relationships {.tabset}
H1d There is no link between right-wing political orientation and women’s interest in having monogamous relationships.
Outcome: Ratings for interest in having monogamous relationships. Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_interest_monrel <- lmer(interest_monrel ~ political_orientation + (1+political_orientation|country), data = data_included_documented, control =lmerControl(optimizer = "bobyqa"))
```

###### Summary
```{r}
summary(model_interest_monrel)
confint(model_interest_monrel, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_interest_monrel, method = "basic", ci = 0.997)

ci(standardize_parameters(model_interest_monrel, method = "basic"), ci = 0.997) #calculate by hand to get exact numbers
```

######  Plot {.active}
```{r}
lmer(interest_monrel ~ political_orientation + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

#### Political, Ethnic, and Religious Similarity {.tabset}
##### H1a Preference for Similarity in Political Beliefs {.tabset}
H1a(1) There is no linear link between right-wing political orientation and women’s preferences for partner’s similar political beliefs and values.
H1a(2) There is a positive quadratic link between right-wing political orientation and women’s preferences for partner’s similar political beliefs and values.
Outcome: Preference ratings for partner's similar political beliefs and values.
Predictor: Political Orientation. Random intercept and random slope for country.


###### H1a(1) Linear Effect
###### Models
```{r}
model_pref_politicalsim_lin = lmer(pref_politicalsim ~ political_orientation +
                       (1+political_orientation|country),
                               data = data_included_documented, 
                       control =lmerControl(optimizer = "bobyqa"))
```

###### Summary
```{r}
summary(model_pref_politicalsim_lin)
confint(model_pref_politicalsim_lin, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_politicalsim_lin, method = "refit", ci = 0.997)
#ci(standardize_parameters(model_pref_politicalsim, method = "refit"), ci = 0.997)
```

######  Plot {.active}
```{r}
lmer(pref_politicalsim ~ political_orientation + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

###### H1a(2) Quadratic Effect
Here, we are examining the quadratic effect of right-wing political orientation on preferred political similarity in a partner using the Two Lines Approach (Simonsohn, 2018). We are using the Robin Hood Algorithm in order to set the breaking point. Then, we are calculating two multilevel regressions on either side of the breaking point.
Outcome: Preference ratings for partner's similar political beliefs and values.
Predictors: Political Orientation & Age. Random intercept and random slope for country.

###### Algorithm: Find breaking point
See 11_twolines_analyses_multilevel


###### Run Multilevel Regression
###### Regression 1 (x <= breaking_point)
```{r}
model_pref_politicalsim_1 = lmer(pref_politicalsim ~ political_orientation +
                                 (1+political_orientation|country),
                               data = data_included_documented %>%
                                 dplyr::filter(political_orientation <= 3), control =lmerControl(optimizer = "bobyqa"))

summary(model_pref_politicalsim_1)
confint(model_pref_politicalsim_1, level = 0.997)

standardize_parameters(model_pref_politicalsim_1, method = "basic", ci = 0.997)

plot(allEffects(model_pref_politicalsim_1))
```

###### Regression 2 (x >= breaking_point)
```{r}
model_pref_politicalsim_2 = lmer(pref_politicalsim ~ political_orientation +
                                 (1+political_orientation|country),
                               data = data_included_documented %>%
                                 dplyr::filter(political_orientation >= 3), control =lmerControl(optimizer = "bobyqa"))

summary(model_pref_politicalsim_2)
confint(model_pref_politicalsim_2, level = 0.997)

standardize_parameters(model_pref_politicalsim_2, method = "basic", ci = 0.997)

plot(allEffects(model_pref_politicalsim_2))
```

##### H1b Preference for Similarity in Ethnicity/Race {.tabset}
H1b There is a positive linear link between right-wing political orientation and women’s preferences for partner’s similar ethnicity/race. 
Outcome: Preference ratings for partner's similar ethnicity/race.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_pref_ethnicalsim <- lmer(pref_ethnicalsim ~ political_orientation + (1+political_orientation|country), data = data_included_documented, control =lmerControl(optimizer = "bobyqa"))
```

###### Summary
```{r}
summary(model_pref_ethnicalsim)
confint(model_pref_ethnicalsim, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_ethnicalsim, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_pref_ethnicalsim, method = "basic"), ci = 0.997)
```

######  Plot {.active}
```{r}
lmer(pref_ethnicalsim ~ political_orientation + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H1c Preference for Similarity in Religion {.tabset}
H1c There is a positive linear link between right-wing political orientation and women’s preferences for partner’s similar religious beliefs.  
Outcome: Preference ratings for partner's similar religious beliefs.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_pref_religioussim <- lmer(pref_religioussim ~ political_orientation + (1+political_orientation|country), data = data_included_documented, control =lmerControl(optimizer = "bobyqa"))
```

###### Summary
```{r}
summary(model_pref_religioussim)
confint(model_pref_religioussim, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_religioussim, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_pref_religioussim, method = "basic"), ci = 0.997)
```

######  Plot {.active}
```{r}
lmer(pref_religioussim ~ political_orientation + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

#### Ideal Partner Preferences {.tabset}
##### H2a Preference for the Level of Financial Security- Successfulness {.tabset}
H2a There is a positive linear link between right-wing political orientation and women’s preferences for the level of financial security and successfulness.
Outcome: Level ratings for partner's financial security-successfulness.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_pref_level_financially_secure_successful_ambitious <- lmer(pref_level_financially_secure_successful_ambitious ~ political_orientation + (1+political_orientation|country), data = data_included_documented, control =lmerControl(optimizer = "bobyqa"))
```

###### Summary
```{r}
summary(model_pref_level_financially_secure_successful_ambitious)
confint(model_pref_level_financially_secure_successful_ambitious, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_level_financially_secure_successful_ambitious, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_pref_level_financially_secure_successful_ambitious, method = "basic"), ci = 0.997)
```

######  Plot {.active}
```{r}
lmer(pref_level_financially_secure_successful_ambitious ~ political_orientation + (1|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H2b Preference for the Level of Kindness-Supportiveness {.tabset}
H2b There is no link between right-wing political orientation and women’s preferences for the level of kindness and supportiveness.  
Outcome: Level ratings for partner's kindness-supportiveness.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_pref_level_kind_supportive <- lmer(pref_level_kind_supportive ~ political_orientation + (1+political_orientation|country), data = data_included_documented, control =lmerControl(optimizer = "bobyqa"))
```

###### Summary
```{r}
summary(model_pref_level_kind_supportive)
confint(model_pref_level_kind_supportive, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_level_kind_supportive, method = "basic", ci = 0.997)

ci(standardize_parameters(model_pref_level_kind_supportive, method = "basic"), ci = 0.997)
#calculate by hand to get exact numbers
```

######  Plot {.active}
```{r}
lmer(pref_level_kind_supportive ~ political_orientation + (1|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H2c Preference for the Level of Attractiveness {.tabset}
H2c There is no link between right-wing political orientation and women’s preferences for the level of attractiveness.  
Outcome: Level ratings for partner's attractiveness.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_pref_level_attractiveness <- lmer(pref_level_attractiveness ~ political_orientation + (1+political_orientation|country), data = data_included_documented, control =lmerControl(optimizer = "bobyqa"))
```

###### Summary
```{r}
summary(model_pref_level_attractiveness)
confint(model_pref_level_attractiveness, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_level_attractiveness, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_pref_level_attractiveness, method = "basic"), ci = 0.997)
```

######  Plot {.active}
```{r}
lmer(pref_level_attractiveness ~ political_orientation + (1|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H2d Preference for the Level of Confidence-Assertiveness {.tabset}
H2d There is a positive linear link between right-wing political orientation and women’s preferences for the level of confidence and assertiveness.  
Outcome: Level ratings for partner's confidence-assertiveness.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_pref_level_confident_assertive <- lmer(pref_level_confident_assertive ~ political_orientation + (1+political_orientation|country), data = data_included_documented, control =lmerControl(optimizer = "bobyqa"))
```

###### Summary
```{r}
summary(model_pref_level_confident_assertive)
confint(model_pref_level_confident_assertive, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_level_confident_assertive, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_pref_level_confident_assertive, method = "basic"), ci = 0.997)
```

######  Plot {.active}
```{r}
lmer(pref_level_confident_assertive ~ political_orientation + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H2e Preference for the Level of Education-Intelligence {.tabset}
H2e There is no link between right-wing political orientation and women’s preferences for the level of education and intelligence.  
Outcome: Level ratings for partner's education-intelligence.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_pref_level_intelligence_educated <- lmer(pref_level_intelligence_educated ~ political_orientation + (1+political_orientation|country), data = data_included_documented, control =lmerControl(optimizer = "bobyqa"))
```

###### Summary
```{r}
summary(model_pref_level_intelligence_educated)
confint(model_pref_level_intelligence_educated, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_level_intelligence_educated, method = "basic", ci = 0.997)

ci(standardize_parameters(model_pref_level_intelligence_educated, method = "basic"), ci = 0.997)
#calculate by hand to get exact numbers
```

######  Plot {.active}
```{r}
lmer(pref_level_intelligence_educated ~ political_orientation + (1|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

#### Ideal Age and Height {.tabset}
##### H3a(1) Importance Ratings for Partner's Age {.tabset}
H3a(1) There is a positive linear link between right-wing political orientation and women’s importance ratings for partner’s age. 
Outcome: Importance ratings for partner's age.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_imp_age <- lmer(imp_age ~ political_orientation + (1+political_orientation|country), data = data_included_documented, control =lmerControl(optimizer = "bobyqa"))
```

###### Summary
```{r}
summary(model_imp_age)
confint(model_imp_age, level= 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_imp_age, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_imp_age, method = "basic"), ci = 0.997)
```

######  Plot {.active}
```{r}
lmer(imp_age ~ political_orientation + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H3a(2) Level Ratings for Partner's Age {.tabset}
H3a(2) There is a positive linear link between right-wing political orientation and the relative age discrepancy between ideal partner’s age and women’s age. (discrepancy calculated as ideal partner’s age – women’s age)
Outcome: Discrepancy between level ratings for ideal partner's age and women's age (ideal_age_rel)
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_ideal_age_rel <- lmer(ideal_age_rel ~ political_orientation + (1+political_orientation|country), data = data_included_documented, control =lmerControl(optimizer = "bobyqa"))
```

###### Summary
```{r}
summary(model_ideal_age_rel)
confint(model_ideal_age_rel, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_ideal_age_rel, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_ideal_age_rel, method = "basic"), ci = 0.997)
```

###### Plot {.active}
```{r}
lmer(ideal_age_rel ~ political_orientation + (1|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H3b(1) Importance Ratings for Partner's Height {.tabset}
H3b(1) There is a positive linear link between right-wing political orientation and women’s importance ratings for partner’s height.
Outcome: Importance ratings for partner's height.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_imp_height <- lmer(imp_height ~ political_orientation + (1+political_orientation|country), data = data_included_documented, control =lmerControl(optimizer = "bobyqa"))
```

###### Summary
```{r}
summary(model_imp_height)
confint(model_imp_height, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_imp_height, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_imp_height, method = "basic"), ci = 0.997)
```

######  Plot {.active}
```{r}
lmer(imp_height ~ political_orientation + (1|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H3b(2) Level Ratings for Partner's Height {.tabset}
H3b(2) There is a positive linear link between right-wing political orientation and ideal partner’s height.
Outcome: Level ratings for ideal partner's height.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_ideal_height <- lmer(ideal_height ~ political_orientation + (1+political_orientation|country), data = data_included_documented, control =lmerControl(optimizer = "bobyqa"))
```

###### Summary
```{r}
summary(model_ideal_height)
confint(model_ideal_height, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_ideal_height, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_ideal_height, method = "basic"), ci = 0.997)
```

######  Plot {.active}
```{r}
lmer(ideal_height ~ political_orientation + (1|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```
