---
title: "05_analyses"
author: "Lena Kuschel"
date: "02 November 2020"
output: 
  html_document:
    code_folding: "hide"
editor_options: 
  chunk_output_type: console
---

## Analyses {.tabset}

### Library
```{r Library}
library(formr)
library(effects)
library(effectsize)
library(lme4)
library(sjstats)
library(lmerTest)
library(dplyr)
```

### Data
Load selected data based on 03_codebook
```{r}
data_included_documented = read.csv(file = "data_included_documented.csv")[,-1]
```

### Analysis {.tabset}
If the model does not converge, we will first exclude the random slope for country. If the model does still not converge, we will subsequently exclude the random intercept for country.
Instead we will z-standardize outcomes separately for each country.

#### Preferred Relationship Options {.tabset}
##### H1a Interest in Single Life {.tabset}
H1a There is a negative linear link between right-wing political orientation and women’s interest in being single.  
Outcome: Ratings for interest in single life. Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
#model_interest_single <- lmer(interest_single ~ political_orientation + (1+political_orientation|country), data = data_included_documented)

#drop random slope as model did not converge:
model_interest_single <- lmer(interest_single ~ political_orientation + (1|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_interest_single)
confint(model_interest_single, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_interest_single, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_interest_single, method = "basic"), ci = 0.997)
```

###### Plot
```{r}
lmer(interest_single ~ political_orientation + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H1b Interest in sexual, non-romantic relationships {.tabset}
H1b There is a negative linear link between right-wing political orientation and women’s interest in having sexual, non-romantic relationships (e.g., hookups, one-night stands).
Outcome: Ratings for interest in having sexual, non-romantic relationships. Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_interest_sexrel <- lmer(interest_sexrel ~ political_orientation + (1+political_orientation|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_interest_sexrel)
confint(model_interest_sexrel, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_interest_sexrel, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_interest_sexrel, method = "basic"), ci = 0.997)
```

###### Plot
```{r}
lmer(interest_sexrel ~ political_orientation + (1 + political_orientation| country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H1c Interest in non-monogamous relationships {.tabset}
H1c There is a negative linear link between right-wing political orientation and women’s interest in having non-monogamous relationships.
Outcome: Ratings for interest in having non-monogamous relationships. Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
#model_interest_nonmonrel <- lmer(interest_nonmonrel ~ political_orientation + (1+political_orientation|country), data = data_included_documented)

#drop random slope as model did not converge:
model_interest_nonmonrel <- lmer(interest_nonmonrel ~ political_orientation + (1|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_interest_nonmonrel)
confint(model_interest_nonmonrel, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_interest_nonmonrel, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_interest_nonmonrel, method = "basic"), ci = 0.997)
```

###### Plot
```{r}
lmer(interest_nonmonrel ~ political_orientation + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H1d Interest in monogamous relationships {.tabset}
H1d There is no link between right-wing political orientation and women’s interest in having monogamous relationships.
Outcome: Ratings for interest in having monogamous relationships. Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_interest_monrel <- lmer(interest_monrel ~ political_orientation + (1+political_orientation|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_interest_monrel)
confint(model_interest_monrel, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_interest_monrel, method = "basic", ci = 0.997)

ci(standardize_parameters(model_interest_monrel, method = "basic"), ci = 0.997) #calculate by hand to get exact numbers
```

###### Plot
```{r}
lmer(interest_monrel ~ political_orientation + (1 + political_orientation| country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

#### Political, ethnic and religious similarity {.tabset}
##### H2a Preference for similarity in political beliefs {.tabset}
H2a There is no linear link between right-wing political orientation and women’s preferences for partner’s similar political beliefs and values when controlling for a quadratic link. 
There is a positive quadratic link between right-wing political orientation and women’s preferences for partner’s similar political beliefs and values when controlling for a linear link.
Outcome: Preference ratings for partner's similar political beliefs and values.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
library(ggplot2)
ggplot(data_included_documented, (aes(x = political_orientation, y = pref_politicalsim))) +
  geom_jitter(alpha = 0.05) +
  stat_summary(geom="ribbon", fun.data=mean_cl_normal, width=0.1, conf.int=0.95, fill="lightblue")+
  stat_summary(geom="line", fun.y=mean, linetype="dashed")

#graph to look for u shaped pattern

model_pref_politicalsim = lmer(pref_politicalsim ~ political_orientation + I(political_orientation^2) +
                                 (1+political_orientation|country),
                               data = data_included_documented)
```

###### Summary
```{r}
summary(model_pref_politicalsim)
confint(model_pref_politicalsim, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_politicalsim, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_pref_politicalsim, method = "basic"), ci = 0.997)
```

###### Plot
```{r}
library(RColorBrewer)#evtl. installieren

effects1 = lmer(pref_politicalsim ~ political_orientation + (1 | country),
             data = data_included_documented) %>%
  allEffects(confidence.level = 0.997, xlevels = 49) %>%
  as.data.frame()

effects1 = as.data.frame(effects1$political_orientation)

n = data_included_documented %>%
  filter(!is.na(pref_politicalsim)) %>%
  count()

plot1 = ggplot() +
  geom_jitter(data = data_included_documented, aes(x = political_orientation, y = pref_politicalsim),
              alpha = 0.05) +
  geom_line(data = effects1, aes(x = political_orientation, y = fit)) +
  geom_ribbon(data = effects1, aes(x = political_orientation, ymin = lower, ymax = upper),
              fill = brewer.pal(9,"Blues")[8], alpha = 0.8) +
  scale_x_continuous(name = "Political Orientation") +
  scale_y_continuous(name = "Importance\nPolitical Similarity",
                     limits = c(-0.5,6.5),
                     breaks = c(0,1,2,3,4,5,6)) +
  ggtitle(paste0(
      "H2a Preference for similarity in political beliefs (n = ",
      prettyNum(n$n, big.mark = ",", preserve.width = "none"),
      ")"))
plot1


effects2 = lmer(pref_politicalsim ~ political_orientation + I(political_orientation^2) +
                  (1 + political_orientation | country),
             data = data_included_documented) %>%
  allEffects(confidence.level = 0.997, xlevels = 49) %>%
  as.data.frame()

effects2 = as.data.frame(effects2$political_orientation)

n = data_included_documented %>%
  filter(!is.na(pref_politicalsim)) %>%
  count()

plot2 = ggplot() +
  geom_jitter(data = data_included_documented, aes(x = political_orientation,
                                                   y = pref_politicalsim), alpha = 0.05) +
  geom_line(data = effects2, aes(x = political_orientation, y = fit)) +
  geom_ribbon(data = effects2, aes(x = political_orientation, ymin = lower, ymax = upper),
              fill = brewer.pal(9,"Blues")[8], alpha = 0.8) +
  scale_x_continuous(name = "Political Orientation") +
  scale_y_continuous(name = "Importance\nPolitical Similarity",
                     limits = c(-0.5,6.5),
                     breaks = c(0,1,2,3,4,5,6)) +
  ggtitle(paste0(
      "H2a Preference for similarity in political beliefs (n = ",
      prettyNum(n$n, big.mark = ",", preserve.width = "none"),
      ")"))
plot2
```


##### H2b Preference for similarity in ethnicity/race {.tabset}
H2b There is a positive linear link between right-wing political orientation and women’s preferences for partner’s similar ethnicity/race. 
Outcome: Preference ratings for partner's similar ethnicity/race.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_pref_ethnicalsim <- lmer(pref_ethnicalsim ~ political_orientation + (1+political_orientation|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_pref_ethnicalsim)
confint(model_pref_ethnicalsim, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_ethnicalsim, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_pref_ethnicalsim, method = "basic"), ci = 0.997)
```

###### Plot
```{r}
lmer(pref_ethnicalsim ~ political_orientation + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H2c Preference for similarity in religion {.tabset}
H2c There is a positive linear link between right-wing political orientation and women’s preferences for partner’s similar religious beliefs.  
Outcome: Preference ratings for partner's similar religious beliefs.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_pref_religioussim <- lmer(pref_religioussim ~ political_orientation + (1+political_orientation|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_pref_religioussim)
confint(model_pref_religioussim, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_religioussim, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_pref_religioussim, method = "basic"), ci = 0.997)
```

###### Plot
```{r}
lmer(pref_religioussim ~ political_orientation + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

#### Ideal Partner Preferences {.tabset}
##### H3a Preference for the level of financial security- successfulness {.tabset}
H3a There is a positive linear link between right-wing political orientation and women’s preferences for the level of financial security and successfulness.
Outcome: Level ratings for partner's financial security-successfulness.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
#model_pref_level_financially_secure_successful_ambitious <- lmer(pref_level_financially_secure_successful_ambitious ~ political_orientation + (1+political_orientation|country), data = data_included_documented)

#drop random slope as model did not converge
model_pref_level_financially_secure_successful_ambitious <- lmer(pref_level_financially_secure_successful_ambitious ~ political_orientation + (1|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_pref_level_financially_secure_successful_ambitious)
confint(model_pref_level_financially_secure_successful_ambitious, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_level_financially_secure_successful_ambitious, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_pref_level_financially_secure_successful_ambitious, method = "basic"), ci = 0.997)
```
@PROBLEM? Bei Berechnung der CI kommen NA für die sigma(R: Es gab 50 oder mehr Warnungen (Anzeige der ersten 50 mit warnings())) --> Laura!
Update 10.11.20: Fehlermeldung kommt nun nicht mehr mit Modell ohne random slope
###### Plot
```{r}
lmer(pref_level_financially_secure_successful_ambitious ~ political_orientation + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H3b Preference for the level of kindness-supportiveness {.tabset}
H3b There is no link between right-wing political orientation and women’s preferences for the level of kindness and supportiveness.  
Outcome: Level ratings for partner's kindness-supportiveness.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_pref_level_kind_supportive <- lmer(pref_level_kind_supportive ~ political_orientation + (1+political_orientation|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_pref_level_kind_supportive)
confint(model_pref_level_kind_supportive, level = 0.997)
```
@PROBLEM @Laura Bei der Berechnung der (unstandardisierten) KI kommt die Fehlermeldung: 
Es gab 50 oder mehr Warnungen (Anzeige der ersten 50 mit warnings())
obwohl Modell konvergiert

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_level_kind_supportive, method = "basic", ci = 0.997)

ci(standardize_parameters(model_pref_level_kind_supportive, method = "basic"), ci = 0.997)
#calculate by hand to get exact numbers
```

###### Plot
```{r}
lmer(pref_level_kind_supportive ~ political_orientation + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H3c Preference for the level of attractiveness {.tabset}
H3c There is no link between right-wing political orientation and women’s preferences for the level of attractiveness.  
Outcome: Level ratings for partner's attractiveness.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
#model_pref_level_attractiveness <- lmer(pref_level_attractiveness ~ political_orientation + (1+political_orientation|country), data = data_included_documented)

#Model failed to converge with 1 negative eigenvalue, drop random slope:
model_pref_level_attractiveness <- lmer(pref_level_attractiveness ~ political_orientation + (1|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_pref_level_attractiveness)
confint(model_pref_level_attractiveness, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_level_attractiveness, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_pref_level_attractiveness, method = "basic"), ci = 0.997)
```

###### Plot
```{r}
lmer(pref_level_attractiveness ~ political_orientation + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H3d Preference for the level of confidence-assertiveness {.tabset}
H3d There is a positive linear link between right-wing political orientation and women’s preferences for the level of confidence and assertiveness.  
Outcome: Level ratings for partner's confidence-assertiveness.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_pref_level_confident_assertive <- lmer(pref_level_confident_assertive ~ political_orientation + (1+political_orientation|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_pref_level_confident_assertive)
confint(model_pref_level_confident_assertive, level = 0.997)
```
@PROBLEM @Laura Warnmeldung s. oben

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_level_confident_assertive, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_pref_level_confident_assertive, method = "basic"), ci = 0.997)
```

###### Plot
```{r}
lmer(pref_level_confident_assertive ~ political_orientation + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H3e Preference for the level of education-intelligence {.tabset}
H3e There is no link between right-wing political orientation and women’s preferences for the level of education and intelligence.  
Outcome: Level ratings for partner's education-intelligence.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_pref_level_intelligence_educated <- lmer(pref_level_intelligence_educated ~ political_orientation + (1+political_orientation|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_pref_level_intelligence_educated)
confint(model_pref_level_intelligence_educated, level = 0.997)
```
@PROBLEM @Laura Warnmeldung s. oben

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_level_intelligence_educated, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_pref_level_intelligence_educated, method = "basic"), ci = 0.997)

```

###### Plot
```{r}
lmer(pref_level_intelligence_educated ~ political_orientation + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

#### Ideal age and height {.tabset}
##### H4a(1) Importance Ratings for partner's age {.tabset}
H4a(1) There is a positive linear link between right-wing political orientation and women’s importance ratings for partner’s age. 
Outcome: Importance ratings for partner's age.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_imp_age <- lmer(imp_age ~ political_orientation + (1+political_orientation|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_imp_age)
confint(model_imp_age, level= 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_imp_age, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_imp_age, method = "basic"), ci = 0.997)
```

###### Plot
```{r}
lmer(imp_age ~ political_orientation + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H4a(2)Level Ratings for partner's age {.tabset}
H4a(2) There is a positive linear link between right-wing political orientation and the relative age discrepancy between ideal partner’s age and women’s age. (discrepancy calculated as ideal partner’s age – women’s age)
Outcome: Discrepancy between level ratings for ideal partner's age and women's age (ideal_age_rel)
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
model_ideal_age_rel <- lmer(ideal_age_rel ~ political_orientation + (1+political_orientation|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_ideal_age_rel)
confint(model_ideal_age_rel, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_ideal_age_rel, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_ideal_age_rel, method = "basic"), ci = 0.997)
```

###### Plot
```{r}
lmer(ideal_age_rel ~ political_orientation + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H4b(1) Importance Ratings for partner's height {.tabset}
H4b(1) There is a positive linear link between right-wing political orientation and women’s importance ratings for partner’s height.
Outcome: Importance ratings for partner's height.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
#model_imp_height <- lmer(imp_height ~ political_orientation + (1+political_orientation|country), data = data_included_documented)

#drop random slope as model did not converge
model_imp_height <- lmer(imp_height ~ political_orientation + (1|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_imp_height)
confint(model_imp_height, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_imp_height, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_imp_height, method = "basic"), ci = 0.997)
```

###### Plot
```{r}
lmer(imp_height ~ political_orientation + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H4b(2)Level Ratings for partner's height {.tabset}
H4b(2) There is a positive linear link between right-wing political orientation and ideal partner’s height.
Outcome: Level ratings for ideal partner's height.
Predictor: Political Orientation. Random intercept and random slope for country.

###### Models
```{r}
#model_ideal_height <- lmer(ideal_height ~ political_orientation + (1+political_orientation|country), data = data_included_documented)

#drop random slope as model did not converge
model_ideal_height <- lmer(ideal_height ~ political_orientation + (1|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_ideal_height)
confint(model_ideal_height, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_ideal_height, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_ideal_height, method = "basic"), ci = 0.997)
```

###### Plot
```{r}
lmer(ideal_height ~ political_orientation + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

@IMPORTANT: Check assumptions & perform robustness checks (including age as a covariate in all models)
