---
title: "06_robustness_analyses"
author: "Lena Kuschel"
date: "10 November 2020"
output: html_document
editor_options: 
  chunk_output_type: console
---
## Robustness Analyses {.tabset}
Here, we perform additional robustness checks including age in each model as a covariate. 

### Library
```{r Library}
library(formr)
library(effects)
library(effectsize)
library(lme4)
library(sjstats)
library(lmerTest)
library(dplyr)
```

### Data
Load selected data based on 03_codebook
```{r}
data_included_documented = read.csv(file = "data_included_documented.csv")[,-1]
```

#### Preferred Relationship Options {.tabset}
##### H1a Interest in Single Life {.tabset}
H1a There is a negative linear link between right-wing political orientation and women’s interest in being single.  
Outcome: Ratings for interest in single life. 
Predictors: Political Orientation & Age. Random intercept and random slope for country.

###### Models
```{r}
model_interest_single_robustcheck <- lmer(interest_single ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_interest_single_robustcheck)
confint(model_interest_single_robustcheck, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_interest_single_robustcheck, method = "basic", ci = 0.997)
```

###### Plot
```{r}
lmer(interest_single ~ political_orientation + age + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H1b Interest in sexual, non-romantic relationships {.tabset}
H1b There is a negative linear link between right-wing political orientation and women’s interest in having sexual, non-romantic relationships (e.g., hookups, one-night stands).
Outcome: Ratings for interest in having sexual, non-romantic relationships. Predictors: Political Orientation & Age. Random intercept and random slope for country.

###### Models
```{r}
model_interest_sexrel_robustcheck <- lmer(interest_sexrel ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_interest_sexrel_robustcheck)
confint(model_interest_sexrel_robustcheck, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_interest_sexrel_robustcheck, method = "basic", ci = 0.997)
```

###### Plot
```{r}
lmer(interest_sexrel ~ political_orientation + age + (1 + political_orientation| country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H1c Interest in non-monogamous relationships {.tabset}
H1c There is a negative linear link between right-wing political orientation and women’s interest in having non-monogamous relationships.
Outcome: Ratings for interest in having non-monogamous relationships. Predictors: Political Orientation & Age. Random intercept and random slope for country.

###### Models
```{r}
model_interest_nonmonrel_robustcheck <- lmer(interest_nonmonrel ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_interest_nonmonrel_robustcheck)
confint(model_interest_nonmonrel_robustcheck, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_interest_nonmonrel_robustcheck, method = "basic", ci = 0.997)
```

###### Plot
```{r}
lmer(interest_nonmonrel ~ political_orientation + age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H1d Interest in monogamous relationships {.tabset}
H1d There is no link between right-wing political orientation and women’s interest in having monogamous relationships.
Outcome: Ratings for interest in having monogamous relationships. 
Predictors: Political Orientation & Age. Random intercept and random slope for country.

###### Models
```{r}
#model_interest_monrel_robustcheck <- lmer(interest_monrel ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented)

#drop random slope as model did not converge
model_interest_monrel_robustcheck <- lmer(interest_monrel ~ political_orientation + age + (1|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_interest_monrel_robustcheck)
confint(model_interest_monrel_robustcheck, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_interest_monrel_robustcheck, method = "basic", ci = 0.997)
```

###### Plot
```{r}
lmer(interest_monrel ~ political_orientation + age + (1| country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

#### Political, ethnic and religious similarity {.tabset}
##### H2a Preference for similarity in political beliefs {.tabset}
H2a There is no linear link between right-wing political orientation and women’s preferences for partner’s similar political beliefs and values when controlling for a quadratic link. 
There is a positive quadratic link between right-wing political orientation and women’s preferences for partner’s similar political beliefs and values when controlling for a linear link.
Outcome: Preference ratings for partner's similar political beliefs and values.
Predictors: Political Orientation & Age. Random intercept and random slope for country.

###### Models
```{r}
library(ggplot2)
ggplot(data_included_documented, (aes(x = political_orientation, y = pref_politicalsim))) +
  geom_jitter(alpha = 0.05) +
  stat_summary(geom="ribbon", fun.data=mean_cl_normal, width=0.1, conf.int=0.95, fill="lightblue")+
  stat_summary(geom="line", fun.y=mean, linetype="dashed")

#graph to look for u shaped pattern

model_pref_politicalsim = lmer(pref_politicalsim ~ political_orientation + I(political_orientation^2) +
                                 (1+political_orientation|country),
                               data = data_included_documented)
```

###### Summary
```{r}
summary(model_pref_politicalsim)
confint(model_pref_politicalsim, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_politicalsim, method = "basic", ci = 0.997)
#ci(standardize_parameters(model_pref_politicalsim, method = "basic"), ci = 0.997)
```

###### Plot
```{r}
library(RColorBrewer)#evtl. installieren

effects1 = lmer(pref_politicalsim ~ political_orientation + (1 | country),
             data = data_included_documented) %>%
  allEffects(confidence.level = 0.997, xlevels = 49) %>%
  as.data.frame()

effects1 = as.data.frame(effects1$political_orientation)

n = data_included_documented %>%
  filter(!is.na(pref_politicalsim)) %>%
  count()

plot1 = ggplot() +
  geom_jitter(data = data_included_documented, aes(x = political_orientation, y = pref_politicalsim),
              alpha = 0.05) +
  geom_line(data = effects1, aes(x = political_orientation, y = fit)) +
  geom_ribbon(data = effects1, aes(x = political_orientation, ymin = lower, ymax = upper),
              fill = brewer.pal(9,"Blues")[8], alpha = 0.8) +
  scale_x_continuous(name = "Political Orientation") +
  scale_y_continuous(name = "Importance\nPolitical Similarity",
                     limits = c(-0.5,6.5),
                     breaks = c(0,1,2,3,4,5,6)) +
  ggtitle(paste0(
      "H2a Preference for similarity in political beliefs (n = ",
      prettyNum(n$n, big.mark = ",", preserve.width = "none"),
      ")"))
plot1


effects2 = lmer(pref_politicalsim ~ political_orientation + I(political_orientation^2) +
                  (1 + political_orientation | country),
             data = data_included_documented) %>%
  allEffects(confidence.level = 0.997, xlevels = 49) %>%
  as.data.frame()

effects2 = as.data.frame(effects2$political_orientation)

n = data_included_documented %>%
  filter(!is.na(pref_politicalsim)) %>%
  count()

plot2 = ggplot() +
  geom_jitter(data = data_included_documented, aes(x = political_orientation,
                                                   y = pref_politicalsim), alpha = 0.05) +
  geom_line(data = effects2, aes(x = political_orientation, y = fit)) +
  geom_ribbon(data = effects2, aes(x = political_orientation, ymin = lower, ymax = upper),
              fill = brewer.pal(9,"Blues")[8], alpha = 0.8) +
  scale_x_continuous(name = "Political Orientation") +
  scale_y_continuous(name = "Importance\nPolitical Similarity",
                     limits = c(-0.5,6.5),
                     breaks = c(0,1,2,3,4,5,6)) +
  ggtitle(paste0(
      "H2a Preference for similarity in political beliefs (n = ",
      prettyNum(n$n, big.mark = ",", preserve.width = "none"),
      ")"))
plot2
```
@Lena skipped robustness analyses for political similarity

##### H2b Preference for similarity in ethnicity/race {.tabset}
H2b There is a positive linear link between right-wing political orientation and women’s preferences for partner’s similar ethnicity/race. 
Outcome: Preference ratings for partner's similar ethnicity/race.
Predictors: Political Orientation & Age. Random intercept and random slope for country.

###### Models
```{r}
#model_pref_ethnicalsim_robustcheck <- lmer(pref_ethnicalsim ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented)

#drop random slope as model did not converge
model_pref_ethnicalsim_robustcheck <- lmer(pref_ethnicalsim ~ political_orientation + age + (1|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_pref_ethnicalsim_robustcheck)
confint(model_pref_ethnicalsim_robustcheck, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_ethnicalsim_robustcheck, method = "basic", ci = 0.997)
```

###### Plot
```{r}
lmer(pref_ethnicalsim ~ political_orientation + age + (1|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H2c Preference for similarity in religion {.tabset}
H2c There is a positive linear link between right-wing political orientation and women’s preferences for partner’s similar religious beliefs.  
Outcome: Preference ratings for partner's similar religious beliefs.
Predictors: Political Orientation & Age. Random intercept and random slope for country.

###### Models
```{r}
model_pref_religioussim_robustcheck <- lmer(pref_religioussim ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_pref_religioussim_robustcheck)
confint(model_pref_religioussim_robustcheck, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_religioussim_robustcheck, method = "basic", ci = 0.997)
```

###### Plot
```{r}
lmer(pref_religioussim ~ political_orientation + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

#### Ideal Partner Preferences {.tabset}
##### H3a Preference for the level of financial security- successfulness {.tabset}
H3a There is a positive linear link between right-wing political orientation and women’s preferences for the level of financial security and successfulness.
Outcome: Level ratings for partner's financial security-successfulness.
Predictors: Political Orientation & Age. Random intercept and random slope for country.

###### Models
```{r}
#model_pref_level_financially_secure_successful_ambitious_robustcheck <- lmer(pref_level_financially_secure_successful_ambitious ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented)

#drop random slope as model did not converge
model_pref_level_financially_secure_successful_ambitious_robustcheck <- lmer(pref_level_financially_secure_successful_ambitious ~ political_orientation + age + (1|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_pref_level_financially_secure_successful_ambitious_robustcheck)
confint(model_pref_level_financially_secure_successful_ambitious_robustcheck, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_level_financially_secure_successful_ambitious_robustcheck, method = "basic", ci = 0.997)

ci(standardize_parameters(model_pref_level_financially_secure_successful_ambitious_robustcheck, method = "basic"), ci = 0.997)
#calculate by hand to get exact numbers
```

###### Plot
```{r}
lmer(pref_level_financially_secure_successful_ambitious ~ political_orientation + age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H3b Preference for the level of kindness-supportiveness {.tabset}
H3b There is no link between right-wing political orientation and women’s preferences for the level of kindness and supportiveness.  
Outcome: Level ratings for partner's kindness-supportiveness.
Predictors: Political Orientation & Age. Random intercept and random slope for country.

###### Models
```{r}
#model_pref_level_kind_supportive_robustcheck <- lmer(pref_level_kind_supportive ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented)

#drop random slope as model did not converge
model_pref_level_kind_supportive_robustcheck <- lmer(pref_level_kind_supportive ~ political_orientation + age + (1|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_pref_level_kind_supportive_robustcheck)
confint(model_pref_level_kind_supportive_robustcheck, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_level_kind_supportive_robustcheck, method = "basic", ci = 0.997)

ci(standardize_parameters(model_pref_level_kind_supportive_robustcheck, method = "basic"), ci = 0.997)
#calculate by hand to get exact numbers
```

###### Plot
```{r}
lmer(pref_level_kind_supportive ~ political_orientation + age + (1|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H3c Preference for the level of attractiveness {.tabset}
H3c There is no link between right-wing political orientation and women’s preferences for the level of attractiveness.  
Outcome: Level ratings for partner's attractiveness.
Predictors: Political Orientation & Age. Random intercept and random slope for country.

###### Models
```{r}
#model_pref_level_attractiveness_robustcheck <- lmer(pref_level_attractiveness ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented)

#Model failed to converge with 1 negative eigenvalue, drop random slope:
model_pref_level_attractiveness_robustcheck <- lmer(pref_level_attractiveness ~ political_orientation + age + (1|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_pref_level_attractiveness_robustcheck)
confint(model_pref_level_attractiveness_robustcheck, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_level_attractiveness_robustcheck, method = "basic", ci = 0.997)
```

###### Plot
```{r}
lmer(pref_level_attractiveness ~ political_orientation + age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```


##### H3d Preference for the level of confidence-assertiveness {.tabset}
H3d There is a positive linear link between right-wing political orientation and women’s preferences for the level of confidence and assertiveness.  
Outcome: Level ratings for partner's confidence-assertiveness.
Predictors: Political Orientation & Age. Random intercept and random slope for country.

###### Models
```{r}
#model_pref_level_confident_assertive_robustcheck <- lmer(pref_level_confident_assertive ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented) 

#drop random slope as model did not converge
model_pref_level_confident_assertive_robustcheck <- lmer(pref_level_confident_assertive ~ political_orientation + age + (1|country), data = data_included_documented) 
```

###### Summary
```{r}
summary(model_pref_level_confident_assertive_robustcheck)
confint(model_pref_level_confident_assertive_robustcheck, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_level_confident_assertive_robustcheck, method = "basic", ci = 0.997)
```

###### Plot
```{r}
lmer(pref_level_confident_assertive ~ political_orientation + age + (1|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H3e Preference for the level of education-intelligence {.tabset}
H3e There is no link between right-wing political orientation and women’s preferences for the level of education and intelligence.  
Outcome: Level ratings for partner's education-intelligence.
Predictors: Political Orientation & Age. Random intercept and random slope for country.

###### Models
```{r}
model_pref_level_intelligence_educated_robustcheck <- lmer(pref_level_intelligence_educated ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_pref_level_intelligence_educated_robustcheck)
confint(model_pref_level_intelligence_educated_robustcheck, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_level_intelligence_educated_robustcheck, method = "basic", ci = 0.997)

ci(standardize_parameters(model_pref_level_intelligence_educated_robustcheck, method = "basic"), ci = 0.997)
#calculate by hand to get exact numbers
```

###### Plot
```{r}
lmer(pref_level_intelligence_educated ~ political_orientation + age + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

#### Ideal age and height {.tabset}
##### H4a(1) Importance Ratings for partner's age {.tabset}
H4a(1) There is a positive linear link between right-wing political orientation and women’s importance ratings for partner’s age. 
Outcome: Importance ratings for partner's age.
Predictors: Political Orientation & Age. Random intercept and random slope for country.

###### Models
```{r}
model_imp_age_robustcheck <- lmer(imp_age ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_imp_age_robustcheck)
confint(model_imp_age_robustcheck, level= 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_imp_age_robustcheck, method = "basic", ci = 0.997)
```

###### Plot
```{r}
lmer(imp_age ~ political_orientation + age + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H4a(2)Level Ratings for partner's age {.tabset}
H4a(2) There is a positive linear link between right-wing political orientation and the relative age discrepancy between ideal partner’s age and women’s age. (discrepancy calculated as ideal partner’s age – women’s age)
Outcome: Discrepancy between level ratings for ideal partner's age and women's age (ideal_age_rel)
Predictors: Political Orientation & Age. Random intercept and random slope for country.

###### Models
```{r}
model_ideal_age_rel_robustcheck <- lmer(ideal_age_rel ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_ideal_age_rel_robustcheck)
confint(model_ideal_age_rel_robustcheck, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_ideal_age_rel_robustcheck, method = "basic", ci = 0.997)
```

###### Plot
```{r}
lmer(ideal_age_rel ~ political_orientation + age + (1+political_orientation|country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H4b(1) Importance Ratings for partner's height {.tabset}
H4b(1) There is a positive linear link between right-wing political orientation and women’s importance ratings for partner’s height.
Outcome: Importance ratings for partner's height.
Predictors: Political Orientation & Age. Random intercept and random slope for country.

###### Models
```{r}
#model_imp_height_robustcheck <- lmer(imp_height ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented)

#drop random slope as model did not converge
model_imp_height_robustcheck <- lmer(imp_height ~ political_orientation + age + (1|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_imp_height_robustcheck)
confint(model_imp_height_robustcheck, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_imp_height_robustcheck, method = "basic", ci = 0.997)

ci(standardize_parameters(model_imp_height_robustcheck, method = "basic"), ci = 0.997)
#calculate by hand to get exact numbers
```

###### Plot
```{r}
lmer(imp_height ~ political_orientation + age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### H4b(2)Level Ratings for partner's height {.tabset}
H4b(2) There is a positive linear link between right-wing political orientation and ideal partner’s height.
Outcome: Level ratings for ideal partner's height.
Predictors: Political Orientation & Age. Random intercept and random slope for country.

###### Models
```{r}
#model_ideal_height_robustcheck <- lmer(ideal_height ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented)

#drop random slope as model did not converge
model_ideal_height_robustcheck <- lmer(ideal_height ~ political_orientation + age + (1|country), data = data_included_documented)
```

###### Summary
```{r}
summary(model_ideal_height_robustcheck)
confint(model_ideal_height_robustcheck, level = 0.997)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_ideal_height_robustcheck, method = "basic", ci = 0.997)
```

###### Plot
```{r}
lmer(ideal_height ~ political_orientation + age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

