---
title: "07_graphs"
author: "Lena Kuschel"
date: "17 November 2020"
output: 
  html_document:
    code_folding: "hide"
editor_options: 
  chunk_output_type: console
---

## Graphs {.tabset}

### Library
```{r Library}
library(formr)
library(effects)
library(effectsize)
library(lme4)
library(sjstats)
library(lmerTest)
library(ggplot2)
library(tidyr)
library(ggpubr)
library(RColorBrewer)
library(coefplot)
library(dplyr)
library(tidyverse)
library (gridExtra)
library(cowplot)


apatheme = theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(),
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5))
```


### Data
Load selected data based on 03_codebook
```{r}
data_included_documented = read.csv(file = "data_included_documented.csv")[,-1]
data_included_documented = data_included_documented %>%
  filter(!is.na(political_orientation)) #check
```

### Figure 2 {.tabset}
Effect size estimates of linear effects of political orientation on preferred relationship options for main analyses and one robustness analysis.

#### Main Analyses
```{r}
model_interest_single <-
  as.data.frame(
    standardize_parameters(
      lmer(
        interest_single ~ political_orientation + (1|country),
        data = data_included_documented),
      method = "basic", ci = 0.997))

model_interest_sexrel <-
  as.data.frame(
    standardize_parameters(
      lmer(
        interest_sexrel ~ political_orientation + (1+political_orientation|country),
        data = data_included_documented),
      method = "basic", ci = 0.997))

model_interest_nonmonrel <-
  as.data.frame(
    standardize_parameters(
      lmer(
        interest_nonmonrel ~ political_orientation + (1|country),
        data = data_included_documented),
      method = "basic", ci = 0.997))

model_interest_monrel <-
  as.data.frame(
    standardize_parameters(
      lmer(
        interest_monrel ~ political_orientation + (1+political_orientation|country),                              data = data_included_documented),
      method = "basic", ci = 0.997))
```

#### Robustness Analyses
Additionally including age as a predictor
```{r}
model_interest_single_robustcheck <-
  as.data.frame(
    standardize_parameters(
      lmer(
        interest_single ~political_orientation + age + (1+political_orientation|country),
        data = data_included_documented),
      method = "basic", ci = 0.997))

model_interest_sexrel_robustcheck <-
  as.data.frame(
    standardize_parameters(
      lmer(
        interest_sexrel ~ political_orientation + age + (1+political_orientation|country),
        data = data_included_documented),
      method = "basic", ci = 0.997))

model_interest_nonmonrel_robustcheck <-
  as.data.frame(
    standardize_parameters(
      lmer(
        interest_nonmonrel ~ political_orientation + age + (1+political_orientation|country),
        data = data_included_documented),
      method = "basic", ci = 0.997))

model_interest_monrel_robustcheck  <-
  as.data.frame(
    standardize_parameters(
      lmer(
        interest_monrel ~ political_orientation + age + (1|country),
        data = data_included_documented),
      method = "basic", ci = 0.997))
```


#### Combine {.active}
```{r}
all_models_interest <- rbind(
  model_interest_single,
  model_interest_sexrel,
  model_interest_nonmonrel,
  model_interest_monrel,
  model_interest_single_robustcheck,
  model_interest_sexrel_robustcheck,
  model_interest_nonmonrel_robustcheck,
  model_interest_monrel_robustcheck) %>%
  filter(Parameter == "political_orientation")

all_models_interest$hypothesis = factor(
  rep(c("H1a) Interest in Single Life", "H1b) Interest in Sexual,\nNon-Romantic Relationships",
        "H1c) Interest in \nNon-Monogamous Relationships",
        "H1d) Interest in \nMonogamous Relationships"),
      2),
  levels = c("H1d) Interest in \nMonogamous Relationships",
             "H1c) Interest in \nNon-Monogamous Relationships",
             "H1b) Interest in Sexual,\nNon-Romantic Relationships",
             "H1a) Interest in Single Life"))

all_models_interest$type = factor(
  c(rep("Main Analyses", 4), rep("Robustness Analyses", 4)),
  levels = c("Robustness Analyses", "Main Analyses"))


multiplot = ggplot(all_models_interest, aes(hypothesis, Std_Coefficient)) +
  geom_pointrange(data = all_models_interest,
                  mapping = aes(x = hypothesis, y = Std_Coefficient,
                                ymin = CI_low, ymax = CI_high, group = type,
                                color = type),
                  position = position_dodge(width=0.3)) + 
  geom_hline(yintercept = 0, size = 1.5)  +
  geom_hline(yintercept = -.05, linetype = "dotted", size = 1.5) + 
  geom_hline(yintercept = .05, linetype = "dotted", size = 1.5) +
  coord_flip() +
  apatheme +
  scale_colour_manual(values = c("#86BDDB", "#084594"))  +
  labs(y = "Linear Effect of Right-Wing Political Orientation", x = "Outcome") +
  theme(text = element_text(size=20), axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        plot.title = element_text(hjust = 0),
        legend.background = element_rect(fill="grey", 
                                         size=0.5, linetype="solid")) +
  #theme(legend.position=c(0.8, 0.8)) +
  guides(col = guide_legend(reverse= TRUE)) 
multiplot
```

#### Save image
```{r}
jpeg("Figure2.jpeg", width = 1050, height = 700)
multiplot
dev.off()
```

###Figure 3 {.tabset}
Effect size estimated of quadratic effect of political orientation on preferred political similarity for main analysis and one robustness analysis.  

#### Main Analyses
```{r}
data_included_nomiss_politicalsim = data_included_documented %>%
  filter(!is.na(pref_politicalsim))

data_included_nomiss_politicalsim_age = data_included_nomiss_politicalsim %>%
  filter(!is.na(age))

#Model for empirical values of preferred political similarity
model_pref_politicalsim = lmer(pref_politicalsim ~
                                 political_orientation + 
                                 I(political_orientation^2) +
                                 (1+political_orientation|country),
                               data = data_included_nomiss_politicalsim)

model_pref_politicalsim_rob = lmer(pref_politicalsim ~
                                 political_orientation + 
                                 I(political_orientation^2) +
                                   age +
                                 (1+political_orientation|country),
                               data = data_included_nomiss_politicalsim_age)

#Model for predicted values of preferred political similarity
model_pref_politicalsim_pred = predict(model_pref_politicalsim)
model_pref_politicalsim_rob_pred = predict(model_pref_politicalsim_rob)


data_included_nomiss_politicalsim$pref_politicalsim_pred =
  model_pref_politicalsim_pred

data_included_nomiss_politicalsim_age$pref_politicalsim_rob_pred =
  model_pref_politicalsim_rob_pred

#Plotting empirical values
graph_emp =
  ggplot(data = data_included_nomiss_politicalsim,
       aes(x = political_orientation, y = pref_politicalsim)) +
  geom_jitter(alpha = .10) +
  stat_summary(geom="ribbon", fun.data=mean_cl_normal,
               fun.args = list(mult = 3),
               fill="#86BDDB")+
  stat_summary(geom="line", fun=mean, linetype="dashed", color="#084594")+
  stat_summary(geom="point", fun=mean, color="#084594") +
  apatheme +
  labs(y = "Preferred Political Similarity\n(Empirical Values)", x = "Right-Wing Political Orientation")+
 scale_x_continuous(breaks=c(0, 1, 2, 3, 4, 5, 6)) +
 scale_y_continuous(breaks=c(0, 1, 2, 3, 4, 5, 6)) +
  theme(text = element_text(size=20), axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15))
graph_emp

# Dataset predicted values main analyses and robustness analyses
 data_included_nomiss_politicalsim_graph =
  rbind(data_included_nomiss_politicalsim %>%
            select(political_orientation, pref_politicalsim_pred) %>%
             mutate(analysis = "Main Analysis"),
          data_included_nomiss_politicalsim_age %>%
            select(political_orientation, pref_politicalsim_rob_pred) %>%
            rename(pref_politicalsim_pred = pref_politicalsim_rob_pred) %>%
             mutate(analysis = "Robustness Analysis"))

#Plotting predicted values
graph_pred_main = 
  ggplot(data = data_included_nomiss_politicalsim_graph %>%
         filter(analysis == "Main Analysis"),
       aes(x = political_orientation, y = pref_politicalsim_pred)) +
  geom_jitter(alpha = .10) +
  stat_summary(geom="ribbon", fun.data=mean_cl_normal,
               fun.args = list(mult = 3), #adjust mult to 99.7% CI
               fill="#86BDDB")+
  stat_summary(geom="line", fun=mean, linetype="dashed", color="#084594")+
  stat_summary(geom="point", fun=mean, color="#084594") +
  apatheme +
  labs(y = "Preferred Political Similarity\n(Predicted Values Based on Main Analysis)", x = "Right-Wing Political Orientation")+
 scale_x_continuous(breaks=c(0, 1, 2, 3, 4, 5, 6))+
 scale_y_continuous(breaks=c(0, 1, 2, 3, 4, 5, 6),
                    limits = c(1.8,5.5)) +
  theme(text = element_text(size=20), axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15))
graph_pred_main

graph_pred_rob = 
  ggplot(data = data_included_nomiss_politicalsim_graph %>%
         filter(analysis == "Robustness Analysis"),
       aes(x = political_orientation, y = pref_politicalsim_pred)) +
  geom_jitter(alpha = .10) +
  stat_summary(geom="ribbon", fun.data=mean_cl_normal,
               fun.args = list(mult = 3), #adjust mult to 99.7% CI
               fill="#86BDDB")+
  stat_summary(geom="line", fun=mean, linetype="dashed", color="#084594")+
  stat_summary(geom="point", fun=mean, color="#084594") +
  apatheme +
  labs(y = "Preferred Political Similarity\n(Predicted Values Based on Robustness Analysis)", x = "Right-Wing Political Orientation")+
 scale_x_continuous(breaks=c(0, 1, 2, 3, 4, 5, 6))+
 scale_y_continuous(breaks=c(0, 1, 2, 3, 4, 5, 6),
                    limits = c(1.8,5.5))+
  theme(text = element_text(size=20), axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15))
graph_pred_rob
```

#### Combine 
```{r}
graph_mult =
  ggarrange(graph_emp,
          ggarrange(graph_pred_main, graph_pred_rob,
                    nrow = 1,
                    labels = c("B", "C")),
          nrow = 2,
          labels = c("A"))
```

#### Save image
```{r}
jpeg("Figure3.jpeg", width = 1000, height = 1200)
graph_mult
dev.off()
```

### Figure 4 {.tabset}
Effect size estimates of linear effects of political orientation on preferred ethnical and religious similarity for main analyses and one robustness analysis.

#### Main Analyses
```{r}
model_pref_ethnicalsim <-
  as.data.frame(
    standardize_parameters(
      lmer(
        pref_ethnicalsim ~ political_orientation + (1+political_orientation|country), data = data_included_documented),
      method = "basic", ci = 0.997))

model_pref_religioussim <-
  as.data.frame(
    standardize_parameters(
      lmer(
        pref_religioussim ~ political_orientation + (1+political_orientation|country), data = data_included_documented),
      method = "basic", ci = 0.997))
```

#### Robustness Analyses
Additionally including age as a predictor
```{r}
model_pref_ethnicalsim_robustcheck <-
  as.data.frame(
    standardize_parameters(
      lmer(
        pref_ethnicalsim ~ political_orientation + age + (1|country), data = data_included_documented),
      method = "basic", ci = 0.997))

model_pref_religioussim_robustcheck <-
  as.data.frame(
    standardize_parameters(
      lmer(
        pref_religioussim ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented),
      method = "basic", ci = 0.997))
```


#### Combine {.active}
```{r}
all_models_similarity <- rbind(
  model_pref_ethnicalsim,
  model_pref_religioussim,
  model_pref_ethnicalsim_robustcheck,
  model_pref_religioussim_robustcheck) %>%
  filter(Parameter == "political_orientation")

all_models_similarity$hypothesis = factor(
  rep(c("H2b) Preferred \nEthnic Similarity", "H2c) Preferred \nReligious Similarity"),
      2),
  levels = c("H2c) Preferred \nReligious Similarity", "H2b) Preferred \nEthnic Similarity"))

all_models_similarity$type = factor(
  c(rep("Main Analyses", 2), rep("Robustness Analyses", 2)),
  levels = c("Robustness Analyses", "Main Analyses"))


multiplot = ggplot(all_models_similarity, aes(hypothesis, Std_Coefficient)) +
  geom_pointrange(data = all_models_similarity,
                  mapping = aes(x = hypothesis, y = Std_Coefficient,
                                ymin = CI_low, ymax = CI_high, group = type,
                                color = type),
                  position = position_dodge(width=0.3)) + 
  geom_hline(yintercept = 0, size = 1.5)  +
  geom_hline(yintercept = -.05, linetype = "dotted", size = 1.5) + 
  geom_hline(yintercept = .05, linetype = "dotted", size = 1.5) +
  coord_flip() +
  apatheme +
  scale_colour_manual(values = c("#86BDDB", "#084594"))  +
  labs(y = "Linear Effect of Right-Wing Political Orientation", x = "Outcome") +
  theme(text = element_text(size=20), axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        plot.title = element_text(hjust = 0),
        legend.background = element_rect(fill="grey", 
                                         size=0.5, linetype="solid"))+ guides(col = guide_legend(reverse= TRUE))
multiplot
```


#### Save image
```{r}
jpeg("Figure4.jpeg", width = 1050, height = 700)
multiplot
dev.off()
```

### Figure 5 {.tabset}
Effect size estimates of linear effects of political orientation on ideal partner preferences for main analyses and one robustness analysis.

#### Main Analyses
```{r}
model_pref_level_financially_secure_successful_ambitious <-
  as.data.frame(
    standardize_parameters(
      lmer(
        pref_level_financially_secure_successful_ambitious ~ political_orientation + (1|country), data = data_included_documented),
      method = "basic", ci = 0.997))

model_pref_level_kind_supportive <-
  as.data.frame(
    standardize_parameters(
      lmer(
        pref_level_kind_supportive ~ political_orientation + (1+political_orientation|country), data = data_included_documented),
      method = "basic", ci = 0.997))

model_pref_level_attractiveness <-
  as.data.frame(
    standardize_parameters(
      lmer(
        pref_level_attractiveness ~ political_orientation + (1|country), data = data_included_documented),
      method = "basic", ci = 0.997))

model_pref_level_confident_assertive <-
  as.data.frame(
    standardize_parameters(
      lmer(
        pref_level_confident_assertive ~ political_orientation + (1+political_orientation|country), data = data_included_documented),
      method = "basic", ci = 0.997))

model_pref_level_intelligence_educated <-
  as.data.frame(
    standardize_parameters(
      lmer(
        pref_level_intelligence_educated ~ political_orientation + (1+political_orientation|country), data = data_included_documented),
      method = "basic", ci = 0.997))
```

#### Robustness Analyses
Additionally including age as a predictor
```{r}
model_pref_level_financially_secure_successful_ambitious_robustcheck <-
  as.data.frame(
    standardize_parameters(
      lmer(
        pref_level_financially_secure_successful_ambitious ~ political_orientation + age + (1|country), data = data_included_documented),
      method = "basic", ci = 0.997))

model_pref_level_kind_supportive_robustcheck <-
  as.data.frame(
    standardize_parameters(
      lmer(
        pref_level_kind_supportive ~ political_orientation + age + (1|country), data = data_included_documented),
      method = "basic", ci = 0.997))

model_pref_level_attractiveness_robustcheck <-
  as.data.frame(
    standardize_parameters(
      lmer(
        pref_level_attractiveness ~ political_orientation + age + (1|country), data = data_included_documented),
      method = "basic", ci = 0.997))

model_pref_level_confident_assertive_robustcheck  <-
  as.data.frame(
    standardize_parameters(
      lmer(
        pref_level_confident_assertive ~ political_orientation + age + (1|country), data = data_included_documented),
      method = "basic", ci = 0.997))

model_pref_level_intelligence_educated_robustcheck  <-
  as.data.frame(
    standardize_parameters(
      lmer(
        pref_level_intelligence_educated ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented),
      method = "basic", ci = 0.997))
```



#### Combine {.active}
```{r}
all_models_ipp <- rbind(
  model_pref_level_financially_secure_successful_ambitious,
  model_pref_level_kind_supportive,
  model_pref_level_attractiveness,
  model_pref_level_confident_assertive,
  model_pref_level_intelligence_educated,
  model_pref_level_financially_secure_successful_ambitious_robustcheck,
  model_pref_level_kind_supportive_robustcheck,
  model_pref_level_attractiveness_robustcheck,
  model_pref_level_confident_assertive_robustcheck,
  model_pref_level_intelligence_educated_robustcheck) %>%
  filter(Parameter == "political_orientation")

all_models_ipp$hypothesis = factor(
  rep(c("H3a) Financial Security-\nSuccessfulness", "H3b) Kindness-\nSupportiveness",
        "H3c) Attractiveness", "H3d) Confidence-\nAssertiveness", "H3e) Education-\nIntelligence"),
      2),
  levels = c("H3e) Education-\nIntelligence", "H3d) Confidence-\nAssertiveness",
             "H3c) Attractiveness", "H3b) Kindness-\nSupportiveness", "H3a) Financial Security-\nSuccessfulness" ))

all_models_ipp$type = factor(
  c(rep("Main Analyses", 5), rep("Robustness Analyses", 5)),
  levels = c("Robustness Analyses", "Main Analyses"))


multiplot = ggplot(all_models_ipp, aes(hypothesis, Std_Coefficient)) +
  geom_pointrange(data = all_models_ipp,
                  mapping = aes(x = hypothesis, y = Std_Coefficient,
                                ymin = CI_low, ymax = CI_high, group = type,
                                color = type),
                  position = position_dodge(width=0.3)) + 
  geom_hline(yintercept = 0, size = 1.5)  +
  geom_hline(yintercept = -.05, linetype = "dotted", size = 1.5) + 
  geom_hline(yintercept = .05, linetype = "dotted", size = 1.5) +
  coord_flip() +
  apatheme +
  scale_colour_manual(values = c("#86BDDB", "#084594"))  +
  labs(y = "Linear Effect of Right-Wing Political Orientation", x = "Outcome") +
  theme(text = element_text(size=20), axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        plot.title = element_text(hjust = 0),
        legend.background = element_rect(fill="grey", 
                                         size=0.5, linetype="solid"))+ guides(col = guide_legend(reverse= TRUE))
multiplot
```


#### Save image
```{r}
jpeg("Figure5.jpeg", width = 1050, height = 700)
multiplot
dev.off()
```

### Figure 6 {.tabset}
Effect size estimates of linear effects of political orientation on ideal partner's age and height for main analyses and one robustness analysis.

#### Main Analyses
```{r}
model_imp_age <-
  as.data.frame(
    standardize_parameters(
      lmer(
        imp_age ~ political_orientation + (1+political_orientation|country), data = data_included_documented),
      method = "basic", ci = 0.997))

model_ideal_age_rel <-
  as.data.frame(
    standardize_parameters(
      lmer(
        ideal_age_rel ~ political_orientation + (1+political_orientation|country), data = data_included_documented),
      method = "basic", ci = 0.997))

model_imp_height <-
  as.data.frame(
    standardize_parameters(
      lmer(
        imp_height ~ political_orientation + (1|country), data = data_included_documented),
      method = "basic", ci = 0.997))

model_ideal_height <-
  as.data.frame(
    standardize_parameters(
      lmer(
        ideal_height ~ political_orientation + (1|country), data = data_included_documented),
      method = "basic", ci = 0.997))
```

#### Robustness Analyses
Additionally including age as a predictor
```{r}
model_imp_age_robustcheck <-
  as.data.frame(
    standardize_parameters(
      lmer(
        imp_age ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented),
      method = "basic", ci = 0.997))

model_ideal_age_rel_robustcheck <-
  as.data.frame(
    standardize_parameters(
      lmer(
        ideal_age_rel ~ political_orientation + age + (1+political_orientation|country), data = data_included_documented),
      method = "basic", ci = 0.997))

model_imp_height_robustcheck <-
  as.data.frame(
    standardize_parameters(
      lmer(
        imp_height ~ political_orientation + age + (1|country), data = data_included_documented),
      method = "basic", ci = 0.997))

model_ideal_height_robustcheck  <-
  as.data.frame(
    standardize_parameters(
      lmer(
        ideal_height ~ political_orientation + age + (1|country), data = data_included_documented),
      method = "basic", ci = 0.997))
```



#### Combine {.active}
```{r}
all_models_ageheight <- rbind(
  model_imp_age,
  model_ideal_age_rel,
  model_imp_height,
  model_ideal_height,
  model_imp_age_robustcheck,
  model_ideal_age_rel_robustcheck,
  model_imp_height_robustcheck,
  model_ideal_height_robustcheck) %>%
  filter(Parameter == "political_orientation")

all_models_ageheight$hypothesis = factor(
  rep(c("H4a(1)) Ideal Age \n(Importance)", "H4a(2)) Ideal Age \n(Level)",
        "H4b(1)) Ideal Height \n(Importance)", "H4b(2)) Ideal Height \n(Level)"),
      2),
  levels = c("H4b(2)) Ideal Height \n(Level)", "H4b(1)) Ideal Height \n(Importance)",
             "H4a(2)) Ideal Age \n(Level)", "H4a(1)) Ideal Age \n(Importance)"))

all_models_ageheight$type = factor(
  c(rep("Main Analyses", 4), rep("Robustness Analyses", 4)),
  levels = c("Robustness Analyses", "Main Analyses"))


multiplot = ggplot(all_models_ageheight, aes(hypothesis, Std_Coefficient)) +
  geom_pointrange(data = all_models_ageheight,
                  mapping = aes(x = hypothesis, y = Std_Coefficient,
                                ymin = CI_low, ymax = CI_high, group = type,
                                color = type),
                  position = position_dodge(width=0.3)) + 
  geom_hline(yintercept = 0, size = 1.5)  +
  geom_hline(yintercept = -.05, linetype = "dotted", size = 1.5) + 
  geom_hline(yintercept = .05, linetype = "dotted", size = 1.5) +
  coord_flip() +
  apatheme +
  scale_colour_manual(values = c("#86BDDB", "#084594"))  +
  labs(y = "Linear Effect of Right-Wing Political Orientation", x = "Outcome") +
  theme(text = element_text(size=20), axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        plot.title = element_text(hjust = 0),
        legend.background = element_rect(fill="grey", 
                                         size=0.5, linetype="solid"))+ guides(col = guide_legend(reverse= TRUE))
multiplot
```


#### Save image
```{r}
jpeg("Figure6.jpeg", width = 1050, height = 700)
multiplot
dev.off()
```
