---
title: "08_graphs_exploratory"
author: "Lena Kuschel"
date: "30 November 2020"
output: 
  html_document:
    code_folding: "hide"
editor_options: 
  chunk_output_type: console
---


## Graphs {.tabset}

### Library
```{r Library}
library(formr)
library(effects)
library(effectsize)
library(lme4)
library(sjstats)
library(lmerTest)
library(ggplot2)
library(tidyr)
library(ggpubr)
library(RColorBrewer)
library(coefplot)
library(tibble)
library(purrr) # for running multiple regression
library(broom)
library(lm.beta)
library(dplyr)
library(stringr)
library(tidyr)



apatheme = theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(),
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5))
```


### Data
Load selected data based on 03_codebook
```{r}
data_included_documented = read.csv(file = "data_included_documented.csv")[,-1]
```


### Inclusion of data
```{r}
countries = as.data.frame(table(data_included_documented$country)) %>%
  arrange(-Freq)

countries
```
We will include all countries with more than 500 participants. This allows us to show effect sizes for a diverse range of countries.
Diversity of countries is indicated by:

* location: European (France, Germany, Italy, Spain); North American (United States of America); South American (Mexico, Brazil)
* language: French (France); German (Germany); English (United States of America); Spanish (Mexico, Spain); Italian (Italy); Portugues (Brazil)
* culture: Western (France, Germany, Italy, Spain, United States of America); Non-Western (Mexico, Brazil)

Sample sizes of other countries are too small (n < 500) to reach any conclusions.

```{r}
seven_countries = countries %>% filter(Freq > 500)
data_included_documented_rescon = data_included_documented %>%
  filter(country %in% seven_countries$Var1)
```

```{r}
countries_rescon = as.data.frame(table(data_included_documented_rescon$country)) %>%
  arrange(-Freq)
countries_rescon
```

### Models
#### H1a Interest in Single Life
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(interest_single, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_interest_single = data_included_documented_rescon_wide %>%
  select(-interest_single) %>%
  map(~lm(data_included_documented_rescon_wide$interest_single ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_interest_single_coef = models_interest_single %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_interest_single_confint_low = models_interest_single %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name)-7))

models_interest_single_confint_high = models_interest_single %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name)-8))

models_interest_single_graph = left_join(left_join(models_interest_single_coef,
                                         models_interest_single_confint_low,
                                         by = "name"),
                                         models_interest_single_confint_high,
                                         by = "name") %>%
  mutate(outcome = "H1a) Interest in Single Life")
```
####  H1b Interest in sexual, non-romantic relationships
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(interest_sexrel, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_interest_sexrel = data_included_documented_rescon_wide %>%
  select(-interest_sexrel) %>%
  map(~lm(data_included_documented_rescon_wide$interest_sexrel ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_interest_sexrel_coef = models_interest_sexrel %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_interest_sexrel_confint_low = models_interest_sexrel %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name)-7))

models_interest_sexrel_confint_high = models_interest_sexrel %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name)-8))

models_interest_sexrel_graph = left_join(left_join(models_interest_sexrel_coef,
                                         models_interest_sexrel_confint_low,
                                         by = "name"),
                                         models_interest_sexrel_confint_high,
                                         by = "name") %>%
  mutate(outcome = "H1b) Interest in Sexual,\nNon-Romantic Relationships")
```

#### H2a Preference for similarity in political beliefs
##### Linear Effect
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(pref_politicalsim, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_pref_politicalsim = data_included_documented_rescon_wide %>%
  select(-pref_politicalsim) %>%
  map(~lm(scale(data_included_documented_rescon_wide$pref_politicalsim) ~ scale(.x) +
            I(scale(.x)^2),
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_pref_politicalsim_lin_coef = models_pref_politicalsim %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_politicalsim_lin_confint_low = models_pref_politicalsim %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname  == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name)-7))

models_pref_politicalsim_lin_confint_high = models_pref_politicalsim %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname  == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name)-8))

models_pref_politicalsim_lin_graph = left_join(left_join(models_pref_politicalsim_lin_coef,
                                         models_pref_politicalsim_lin_confint_low,
                                         by = "name"),
                                         models_pref_politicalsim_lin_confint_high,
                                         by = "name") %>%
  mutate(outcome = "H2a) Preference for Similarity in\nPolitical beliefs - Linear Effect")
```

##### Quadratic Effect
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(pref_politicalsim, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_pref_politicalsim = data_included_documented_rescon_wide %>%
  select(-pref_politicalsim) %>%
  map(~lm(scale(data_included_documented_rescon_wide$pref_politicalsim) ~ scale(.x) +
            I(scale(.x)^2),
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_pref_politicalsim_quad_coef = models_pref_politicalsim %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname == "I(scale(.x)^2)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_politicalsim_quad_confint_low = models_pref_politicalsim %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname  == "I(scale(.x)^2)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name)-7))

models_pref_politicalsim_quad_confint_high = models_pref_politicalsim %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname  == "I(scale(.x)^2)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name)-8))

models_pref_politicalsim_quad_graph = left_join(left_join(models_pref_politicalsim_quad_coef,
                                         models_pref_politicalsim_quad_confint_low,
                                         by = "name"),
                                         models_pref_politicalsim_quad_confint_high,
                                         by = "name") %>%
  mutate(outcome = "H2a) Preference for Similarity in\nPolitical Beliefs - Quadratic Effect")
```


#### H3a Preference for the level of financial security- successfulness 
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(pref_level_financially_secure_successful_ambitious, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_pref_level_financially_secure_successful_ambitious = data_included_documented_rescon_wide %>%
  select(-pref_level_financially_secure_successful_ambitious) %>%
  map(~lm(data_included_documented_rescon_wide$pref_level_financially_secure_successful_ambitious ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_pref_level_financially_secure_successful_ambitious_coef = models_pref_level_financially_secure_successful_ambitious %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_level_financially_secure_successful_ambitious_confint_low = models_pref_level_financially_secure_successful_ambitious %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name)-7))

models_pref_level_financially_secure_successful_ambitious_confint_high = models_pref_level_financially_secure_successful_ambitious %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name)-8))

models_pref_level_financially_secure_successful_ambitious_graph = left_join(left_join(models_pref_level_financially_secure_successful_ambitious_coef,
                                         models_pref_level_financially_secure_successful_ambitious_confint_low,
                                         by = "name"),
                                         models_pref_level_financially_secure_successful_ambitious_confint_high,
                                         by = "name") %>%
  mutate(outcome = "H3a) Financial Security-Successfulness")
```

#### Combine
```{r}
data_graph = rbind(models_interest_single_graph, models_interest_sexrel_graph,
                   models_pref_level_financially_secure_successful_ambitious_graph,
                   models_pref_politicalsim_lin_graph, models_pref_politicalsim_quad_graph) %>%
  mutate(outcome = factor(outcome,
                          levels = c("H3a) Financial Security-Successfulness",
                                     "H2a) Preference for Similarity in\nPolitical Beliefs - Quadratic Effect",
                                     "H2a) Preference for Similarity in\nPolitical beliefs - Linear Effect",
                                     "H1b) Interest in Sexual,\nNon-Romantic Relationships",
                                   "H1a) Interest in Single Life")))


data_graph$name = factor(rep(c(
  paste0("France (n = ",
         sum(data_included_documented_rescon$country == "France"), ")"),
  paste0("Germany (n = ",
         sum(data_included_documented_rescon$country == "Germany"), ")"),
  paste0("United States of America (n = ",
         sum(data_included_documented_rescon$country == "United States of America"),
         ")"),
  paste0("Mexico (n = ",
         sum(data_included_documented_rescon$country == "Mexico"), ")"),
  paste0("Italy (n = ",
         sum(data_included_documented_rescon$country == "Italy"), ")"),
  paste0("Brazil (n = ",
         sum(data_included_documented_rescon$country == "Brazil"), ")"),
  paste0("Spain (n = ",
         sum(data_included_documented_rescon$country == "Spain"), ")")),
  5))

l_countries = levels(data_graph$name)
data_graph$name = factor(data_graph$name,
                         levels = rev(c(l_countries[2], l_countries[3],
                                    l_countries[7], l_countries[5],
                                    l_countries[4], l_countries[1],
                                    l_countries[6])))
```

### Graph Multiplot
```{r}
multiplot = ggplot(data_graph, aes(outcome, mean)) +
  geom_pointrange(data = data_graph,
                  mapping = aes(x = outcome, y = mean,
                                ymin = conf_low , ymax = conf_high , group = name,
                                color = name),
                  position = position_dodge(width=0.3)) + 
  geom_hline(yintercept = 0, size = 1.5)  +
  geom_hline(yintercept = -.05, linetype = "dotted", size = 1.5) + 
  geom_hline(yintercept = .05, linetype = "dotted", size = 1.5) +
  coord_flip() +
  apatheme +
  # scale_colour_manual(values = c("#86BDDB", "#084594"))  +
  labs(y = "Effect of Political Orientation", x = "Outcome") +
  theme(text = element_text(size=15), axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10),
        legend.text = element_text(size = 10),
        plot.title = element_text(hjust = 0),
        legend.background = element_rect(fill="grey", 
                                         size=0.5, linetype="solid")) +
  guides(col = guide_legend(reverse= TRUE))
multiplot
```

###Graph Political Similarity
Effect size estimated of quadratic effect of political orientation on preferred political similarity for main analysis and one robustness analysis.  

```{r}
data_included_nomiss_politicalsim = data_included_documented_rescon %>%
  filter(!is.na(pref_politicalsim))

model_pref_politicalsim = lmer(pref_politicalsim ~
                                 political_orientation + 
                                 I(political_orientation^2) +
                                 (1|country),
                               data = data_included_nomiss_politicalsim)

model_pref_politicalsim_pred = predict(model_pref_politicalsim)

data_included_nomiss_politicalsim$pref_politicalsim_pred =
  model_pref_politicalsim_pred

ggplot(data = data_included_nomiss_politicalsim,
       aes(x = political_orientation, y = pref_politicalsim,
           color = country, fill = country)) +
  geom_jitter(alpha = .10) +
  #stat_summary(geom="ribbon", fun.data=mean_cl_normal, width=0.1,
  #             conf.int=0.997, alpha = 0.05)+
  stat_summary(geom="line", fun.y=mean, linetype="solid")+
  stat_summary(geom="point", fun.y=mean) +
  apatheme

ggplot(data = data_included_nomiss_politicalsim,
       aes(x = political_orientation, y = pref_politicalsim_pred, color = country)) +
  geom_jitter(alpha = .10) +
  stat_summary(geom="ribbon", fun.data=mean_cl_normal, width=0.1,
               conf.int=0.997, fill="lightblue")+
  stat_summary(geom="line", fun.y=mean, linetype="dashed")+
  stat_summary(geom="point", fun.y=mean)
```
