---
title: <font color="#66C2A5">Exploratory Analyses</font>
csl: apa-custom-no-issue.csl
output: 
  html_document:
    code_folding: "hide"
editor_options: 
  chunk_output_type: console
---

## {.tabset}

### Library
```{r Library}
library(formr)
library(effects)
library(effectsize)
library(lme4)
library(sjstats)
library(lmerTest)
library(ggplot2)
library(tidyr)
library(ggpubr)
library(RColorBrewer)
library(coefplot)
library(tibble)
library(purrr) # for running multiple regression
library(broom)
library(mvmeta)
library(lm.beta)
library(dplyr)
library(stringr)
library(tidyr)

apatheme = theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(),
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5))
```

### Data
Load selected data based on 03_codebook
```{r}
data_included_documented = read.csv(file = "data_included_documented.csv")[,-1]
```

### Inclusion of Data
```{r}
countries = as.data.frame(table(data_included_documented$country)) %>%
  arrange(-Freq)

countries
```
We will include all countries with more than 500 participants. This allows us to show effect sizes for a diverse range of countries.
Diversity of countries is indicated by:

* location: European (France, Germany, Italy, Spain); North American (United States of America); South American (Mexico, Brazil)
* language: French (France); German (Germany); English (United States of America); Spanish (Mexico, Spain); Italian (Italy); Portuguese (Brazil)
* culture: Western (France, Germany, Italy, Spain, United States of America); Non-Western (Mexico, Brazil)

Sample sizes of other countries are too small (n < 500) to reach any conclusions.

```{r}
seven_countries = countries %>% filter(Freq > 500)
data_included_documented_rescon = data_included_documented %>%
  filter(country %in% seven_countries$Var1)
```

```{r}
countries_rescon =
  data_included_documented_rescon %>%
  select(country) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)


countries_rescon
```


#### Political, Ethnic, and Religious Similarity {.tabset}
##### H1a Preference for Similarity in Political Beliefs {.tabset}
###### H1a(1) Linear Effect
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(pref_politicalsim, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_pref_politicalsim = data_included_documented_rescon_wide %>%
  select(-pref_politicalsim) %>%
  map(~lm(scale(data_included_documented_rescon_wide$pref_politicalsim) ~ scale(.x),
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_pref_politicalsim_lin_coef = models_pref_politicalsim %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_politicalsim_lin_se = models_pref_politicalsim %>%
  map(summary) %>%
  tibble(models_pref_politicalsim_lin_se = ., Names = names(.)) %>%
  hoist(models_pref_politicalsim_lin_se, coefficients = "coefficients") %>%
  select(-models_pref_politicalsim_lin_se) %>%
  unnest_wider(., coefficients, names_repair = "universal") %>%
  select(...8, Names) %>%
  rename("name" = "Names",
         "se" = "...8") %>%
  mutate(name = ifelse(name == "United States of America",
                       "United.States.of.America", name))


models_pref_politicalsim_lin_analyses = left_join(models_pref_politicalsim_lin_coef,
                                            models_pref_politicalsim_lin_se,
                                            by = "name") %>%
  mutate(outcome = "H2a) Prefered Political Similarity - Linear Effect")

countries_rescon =
  data_included_documented_rescon %>%
  filter(!is.na(pref_politicalsim)) %>%
  select(country) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_pref_politicalsim_lin_analyses$n = countries_rescon$Freq

model = mvmeta(mean ~ 1, data = models_pref_politicalsim_lin_analyses, S = se^2,
               method = "fixed")
summary(model)
```

###### H1a(2) Quadratic Effect
###### Regression 1 (x <= breaking_point)
```{r}
data_included_documented_rescon_wide_reg1 = data_included_documented_rescon %>%
  dplyr::filter(political_orientation <= 3) %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(pref_politicalsim, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_pref_politicalsim_reg1 = data_included_documented_rescon_wide_reg1 %>%
  select(-pref_politicalsim) %>%
  map(~lm(scale(data_included_documented_rescon_wide_reg1$pref_politicalsim) ~
            scale(.x),
          data = data_included_documented_rescon_wide_reg1)) %>%
  map(lm.beta)

models_pref_politicalsim_quad_coef_reg1 = models_pref_politicalsim_reg1 %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)


models_pref_politicalsim_quad_se_reg1 = models_pref_politicalsim_reg1 %>%
  map(summary) %>%
  tibble(models_pref_politicalsim_quad_se_reg1 = ., Names = names(.)) %>%
  hoist(models_pref_politicalsim_quad_se_reg1, coefficients = "coefficients") %>%
  select(-models_pref_politicalsim_quad_se_reg1) %>%
  unnest_wider(., coefficients, names_repair = "universal") %>%
  select(...9, Names) %>%
  rename("name" = "Names",
         "se" = "...9") %>%
  mutate(name = ifelse(name == "United States of America",
                       "United.States.of.America", name))


models_pref_politicalsim_quad_analyses_reg1 = left_join(models_pref_politicalsim_quad_coef_reg1,
                                            models_pref_politicalsim_quad_se_reg1,
                                            by = "name") %>%
  mutate(outcome = "H2a(1)) Preferred Political Similarity - Quadratic Effect Regression 1")

models_pref_politicalsim_quad_analyses_reg1$n = countries_rescon$Freq

model = mvmeta(mean ~ 1, data = models_pref_politicalsim_quad_analyses_reg1, S = se^2,
               method = "fixed")
summary(model)
```

###### Regression 2 (x >= breaking_point)
```{r}
data_included_documented_rescon_wide_reg2 = data_included_documented_rescon %>%
  dplyr::filter(political_orientation >= 3) %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(pref_politicalsim, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_pref_politicalsim_reg2 = data_included_documented_rescon_wide_reg2 %>%
  select(-pref_politicalsim) %>%
  map(~lm(scale(data_included_documented_rescon_wide_reg2$pref_politicalsim) ~
            scale(.x),
          data = data_included_documented_rescon_wide_reg2)) %>%
  map(lm.beta)

models_pref_politicalsim_quad_coef_reg2 = models_pref_politicalsim_reg2 %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)


models_pref_politicalsim_quad_se_reg2 = models_pref_politicalsim_reg1 %>%
  map(summary) %>%
  tibble(models_pref_politicalsim_quad_se_reg2 = ., Names = names(.)) %>%
  hoist(models_pref_politicalsim_quad_se_reg2, coefficients = "coefficients") %>%
  select(-models_pref_politicalsim_quad_se_reg2) %>%
  unnest_wider(., coefficients, names_repair = "universal") %>%
  select(...9, Names) %>%
  rename("name" = "Names",
         "se" = "...9") %>%
  mutate(name = ifelse(name == "United States of America",
                       "United.States.of.America", name))


models_pref_politicalsim_quad_analyses_reg2 = left_join(models_pref_politicalsim_quad_coef_reg2,
                                            models_pref_politicalsim_quad_se_reg2,
                                            by = "name") %>%
  mutate(outcome = "H2a(1)) Preferred Political Similarity - Quadratic Effect Regression 2")

models_pref_politicalsim_quad_analyses_reg2$n = countries_rescon$Freq

model = mvmeta(mean ~ 1, data = models_pref_politicalsim_quad_analyses_reg2, S = se^2,
               method = "fixed")
summary(model)
```

##### H1b Preference for Similarity in Ethnicity/Race {.tabset}
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(pref_ethnicalsim, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_pref_ethnicalsim = data_included_documented_rescon_wide %>%
  select(-pref_ethnicalsim) %>%
  map(~lm(data_included_documented_rescon_wide$pref_ethnicalsim ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_pref_ethnicalsim_coef = models_pref_ethnicalsim %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_ethnicalsim_se = models_pref_ethnicalsim %>%
  map(summary) %>%
  tibble(models_pref_ethnicalsim_se = ., Names = names(.)) %>%
  hoist(models_pref_ethnicalsim_se, coefficients = "coefficients") %>%
  select(-models_pref_ethnicalsim_se) %>%
  unnest_wider(., coefficients, names_repair = "universal") %>%
  select(...5, Names) %>%
  rename("name" = "Names",
         "se" = "...5") %>%
  mutate(name = ifelse(name == "United States of America",
                       "United.States.of.America", name))


models_pref_ethnicalsim_analyses = left_join(models_pref_ethnicalsim_coef,
                                            models_pref_ethnicalsim_se,
                                            by = "name") %>%
  mutate(outcome = "H2b) Preferred Ethnic Similarity")

countries_rescon =
  data_included_documented_rescon %>%
  filter(!is.na(pref_ethnicalsim)) %>%
  select(country) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_pref_ethnicalsim_analyses$n = countries_rescon$Freq

model = mvmeta(mean ~ 1, data = models_pref_ethnicalsim_analyses, S = se^2,
               method = "fixed")
summary(model)
```

##### H1c Preference for Similarity in Religion {.tabset}
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(pref_religioussim, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_pref_religioussim = data_included_documented_rescon_wide %>%
  select(-pref_religioussim) %>%
  map(~lm(data_included_documented_rescon_wide$pref_religioussim ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_pref_religioussim_coef = models_pref_religioussim %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_religioussim_se = models_pref_religioussim %>%
  map(summary) %>%
  tibble(models_pref_religioussim_se = ., Names = names(.)) %>%
  hoist(models_pref_religioussim_se, coefficients = "coefficients") %>%
  select(-models_pref_religioussim_se) %>%
  unnest_wider(., coefficients, names_repair = "universal") %>%
  select(...5, Names) %>%
  rename("name" = "Names",
         "se" = "...5") %>%
  mutate(name = ifelse(name == "United States of America",
                       "United.States.of.America", name))


models_pref_religioussim_analyses = left_join(models_pref_religioussim_coef,
                                            models_pref_religioussim_se,
                                            by = "name") %>%
  mutate(outcome = "H2c) Preferred Religious Similarity")

countries_rescon =
  data_included_documented_rescon %>%
  filter(!is.na(pref_religioussim)) %>%
  select(country) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_pref_religioussim_analyses$n = countries_rescon$Freq

model = mvmeta(mean ~ 1, data = models_pref_religioussim_analyses, S = se^2,
               method = "fixed")
summary(model)
```

#### Ideal Partner Preferences {.tabset}
##### H2a Preference for the Level of Financial Security- Successfulness {.tabset}
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(pref_level_financially_secure_successful_ambitious, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_pref_level_financially_secure_successful_ambitious = data_included_documented_rescon_wide %>%
  select(-pref_level_financially_secure_successful_ambitious) %>%
  map(~lm(data_included_documented_rescon_wide$pref_level_financially_secure_successful_ambitious ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_pref_level_financially_secure_successful_ambitious_coef = models_pref_level_financially_secure_successful_ambitious %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_level_financially_secure_successful_ambitious_se = models_pref_level_financially_secure_successful_ambitious %>%
  map(summary) %>%
  tibble(models_pref_level_financially_secure_successful_ambitious_se = ., Names = names(.)) %>%
  hoist(models_pref_level_financially_secure_successful_ambitious_se, coefficients = "coefficients") %>%
  select(-models_pref_level_financially_secure_successful_ambitious_se) %>%
  unnest_wider(., coefficients, names_repair = "universal") %>%
  select(...5, Names) %>%
  rename("name" = "Names",
         "se" = "...5") %>%
  mutate(name = ifelse(name == "United States of America",
                       "United.States.of.America", name))


models_pref_level_financially_secure_successful_ambitious_analyses = left_join(models_pref_level_financially_secure_successful_ambitious_coef,
                                            models_pref_level_financially_secure_successful_ambitious_se,
                                            by = "name") %>%
  mutate(outcome = "H3a) Financial Security-Successfulness")

countries_rescon =
  data_included_documented_rescon %>%
  filter(!is.na(pref_level_financially_secure_successful_ambitious)) %>%
  select(country) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_pref_level_financially_secure_successful_ambitious_analyses$n = countries_rescon$Freq

model = mvmeta(mean ~ 1, data = models_pref_level_financially_secure_successful_ambitious_analyses, S = se^2,
               method = "fixed")
summary(model)
```

##### H2b Preference for the Level of Kindness-Supportiveness {.tabset}
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(pref_level_kind_supportive , France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_pref_level_kind_supportive = data_included_documented_rescon_wide %>%
  select(-pref_level_kind_supportive) %>%
  map(~lm(data_included_documented_rescon_wide$pref_level_kind_supportive ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_pref_level_kind_supportive_coef = models_pref_level_kind_supportive %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_level_kind_supportive_se = models_pref_level_kind_supportive %>%
  map(summary) %>%
  tibble(models_pref_level_kind_supportive_se = ., Names = names(.)) %>%
  hoist(models_pref_level_kind_supportive_se, coefficients = "coefficients") %>%
  select(-models_pref_level_kind_supportive_se) %>%
  unnest_wider(., coefficients, names_repair = "universal") %>%
  select(...5, Names) %>%
  rename("name" = "Names",
         "se" = "...5") %>%
  mutate(name = ifelse(name == "United States of America",
                       "United.States.of.America", name))


models_pref_level_kind_supportive_analyses = left_join(models_pref_level_kind_supportive_coef,
                                            models_pref_level_kind_supportive_se,
                                            by = "name") %>%
  mutate(outcome = "H3b) Kindness-Supportiveness")

countries_rescon =
  data_included_documented_rescon %>%
  filter(!is.na(pref_level_kind_supportive)) %>%
  select(country) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_pref_level_kind_supportive_analyses$n = countries_rescon$Freq

model = mvmeta(mean ~ 1, data = models_pref_level_kind_supportive_analyses, S = se^2,
               method = "fixed")
summary(model)
```

##### H2c Preference for the Level of Attractiveness {.tabset}
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(pref_level_attractiveness , France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_pref_level_attractiveness = data_included_documented_rescon_wide %>%
  select(-pref_level_attractiveness) %>%
  map(~lm(data_included_documented_rescon_wide$pref_level_attractiveness ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_pref_level_attractiveness_coef = models_pref_level_attractiveness %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_level_attractiveness_se = models_pref_level_attractiveness %>%
  map(summary) %>%
  tibble(models_pref_level_attractiveness_se = ., Names = names(.)) %>%
  hoist(models_pref_level_attractiveness_se, coefficients = "coefficients") %>%
  select(-models_pref_level_attractiveness_se) %>%
  unnest_wider(., coefficients, names_repair = "universal") %>%
  select(...5, Names) %>%
  rename("name" = "Names",
         "se" = "...5") %>%
  mutate(name = ifelse(name == "United States of America",
                       "United.States.of.America", name))


models_pref_level_attractiveness_analyses = left_join(models_pref_level_attractiveness_coef,
                                            models_pref_level_attractiveness_se,
                                            by = "name") %>%
  mutate(outcome = "H3c) Attractiveness")

countries_rescon =
  data_included_documented_rescon %>%
  filter(!is.na(pref_level_attractiveness)) %>%
  select(country) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_pref_level_attractiveness_analyses$n = countries_rescon$Freq

model = mvmeta(mean ~ 1, data = models_pref_level_attractiveness_analyses, S = se^2,
               method = "fixed")
summary(model)
```

##### H2d Preference for the Level of Confidence-Assertiveness {.tabset}
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(pref_level_confident_assertive , France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_pref_level_confident_assertive = data_included_documented_rescon_wide %>%
  select(-pref_level_confident_assertive) %>%
  map(~lm(data_included_documented_rescon_wide$pref_level_confident_assertive ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_pref_level_confident_assertive_coef = models_pref_level_confident_assertive %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_level_confident_assertive_se = models_pref_level_confident_assertive %>%
  map(summary) %>%
  tibble(models_pref_level_confident_assertive_se = ., Names = names(.)) %>%
  hoist(models_pref_level_confident_assertive_se, coefficients = "coefficients") %>%
  select(-models_pref_level_confident_assertive_se) %>%
  unnest_wider(., coefficients, names_repair = "universal") %>%
  select(...5, Names) %>%
  rename("name" = "Names",
         "se" = "...5") %>%
  mutate(name = ifelse(name == "United States of America",
                       "United.States.of.America", name))


models_pref_level_confident_assertive_analyses = left_join(models_pref_level_confident_assertive_coef,
                                            models_pref_level_confident_assertive_se,
                                            by = "name") %>%
  mutate(outcome = "H3d) Confidence-Assertiveness")

countries_rescon =
  data_included_documented_rescon %>%
  filter(!is.na(pref_level_confident_assertive)) %>%
  select(country) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_pref_level_confident_assertive_analyses$n = countries_rescon$Freq

model = mvmeta(mean ~ 1, data = models_pref_level_confident_assertive_analyses, S = se^2,
               method = "fixed")
summary(model)
```

##### H2e Preference for the Level of Education-Intelligence {.tabset}
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(pref_level_intelligence_educated, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_pref_level_intelligence_educated = data_included_documented_rescon_wide %>%
  select(-pref_level_intelligence_educated) %>%
  map(~lm(data_included_documented_rescon_wide$pref_level_intelligence_educated ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_pref_level_intelligence_educated_coef = models_pref_level_intelligence_educated %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_level_intelligence_educated_se = models_pref_level_intelligence_educated %>%
  map(summary) %>%
  tibble(models_pref_level_intelligence_educated_se = ., Names = names(.)) %>%
  hoist(models_pref_level_intelligence_educated_se, coefficients = "coefficients") %>%
  select(-models_pref_level_intelligence_educated_se) %>%
  unnest_wider(., coefficients, names_repair = "universal") %>%
  select(...5, Names) %>%
  rename("name" = "Names",
         "se" = "...5") %>%
  mutate(name = ifelse(name == "United States of America",
                       "United.States.of.America", name))


models_pref_level_intelligence_educated_analyses = left_join(models_pref_level_intelligence_educated_coef,
                                            models_pref_level_intelligence_educated_se,
                                            by = "name") %>%
  mutate(outcome = "H3e) Education-Intelligence")

countries_rescon =
  data_included_documented_rescon %>%
  filter(!is.na(pref_level_intelligence_educated)) %>%
  select(country) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_pref_level_intelligence_educated_analyses$n = countries_rescon$Freq

model = mvmeta(mean ~ 1, data = models_pref_level_intelligence_educated_analyses, S = se^2,
               method = "fixed")
summary(model)
```

#### Ideal Age and Height {.tabset}
##### H3a(1) Ideal Age (Importance) {.tabset}
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(imp_age, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_imp_age = data_included_documented_rescon_wide %>%
  select(-imp_age) %>%
  map(~lm(data_included_documented_rescon_wide$imp_age ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_imp_age_coef = models_imp_age %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_imp_age_se = models_imp_age %>%
  map(summary) %>%
  tibble(models_imp_age_se = ., Names = names(.)) %>%
  hoist(models_imp_age_se, coefficients = "coefficients") %>%
  select(-models_imp_age_se) %>%
  unnest_wider(., coefficients, names_repair = "universal") %>%
  select(...5, Names) %>%
  rename("name" = "Names",
         "se" = "...5") %>%
  mutate(name = ifelse(name == "United States of America",
                       "United.States.of.America", name))


models_imp_age_analyses = left_join(models_imp_age_coef,
                                            models_imp_age_se,
                                            by = "name") %>%
  mutate(outcome = "H4a(1)) Ideal Age (Importance)")

countries_rescon =
  data_included_documented_rescon %>%
  filter(!is.na(imp_age)) %>%
  select(country) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_imp_age_analyses$n = countries_rescon$Freq

model = mvmeta(mean ~ 1, data = models_imp_age_analyses, S = se^2,
               method = "fixed")
summary(model)
```

##### H3a(2) Ideal Age (Level) {.tabset}
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(ideal_age_rel, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_ideal_age_rel = data_included_documented_rescon_wide %>%
  select(-ideal_age_rel) %>%
  map(~lm(data_included_documented_rescon_wide$ideal_age_rel ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_ideal_age_rel_coef = models_ideal_age_rel %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_ideal_age_rel_se = models_ideal_age_rel %>%
  map(summary) %>%
  tibble(models_ideal_age_rel_se = ., Names = names(.)) %>%
  hoist(models_ideal_age_rel_se, coefficients = "coefficients") %>%
  select(-models_ideal_age_rel_se) %>%
  unnest_wider(., coefficients, names_repair = "universal") %>%
  select(...5, Names) %>%
  rename("name" = "Names",
         "se" = "...5") %>%
  mutate(name = ifelse(name == "United States of America",
                       "United.States.of.America", name))


models_ideal_age_rel_analyses = left_join(models_ideal_age_rel_coef,
                                            models_ideal_age_rel_se,
                                            by = "name") %>%
  mutate(outcome = "H4a(2)) Ideal Age (Level)")

countries_rescon =
  data_included_documented_rescon %>%
  filter(!is.na(ideal_age_rel)) %>%
  select(country) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_ideal_age_rel_analyses$n = countries_rescon$Freq

model = mvmeta(mean ~ 1, data = models_ideal_age_rel_analyses, S = se^2,
               method = "fixed")
summary(model)
```

##### H3b(1) Ideal Height (Importance) {.tabset}
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(imp_height, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_imp_height = data_included_documented_rescon_wide %>%
  select(-imp_height) %>%
  map(~lm(data_included_documented_rescon_wide$imp_height ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_imp_height_coef = models_imp_height %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_imp_height_se = models_imp_height %>%
  map(summary) %>%
  tibble(models_imp_height_se = ., Names = names(.)) %>%
  hoist(models_imp_height_se, coefficients = "coefficients") %>%
  select(-models_imp_height_se) %>%
  unnest_wider(., coefficients, names_repair = "universal") %>%
  select(...5, Names) %>%
  rename("name" = "Names",
         "se" = "...5") %>%
  mutate(name = ifelse(name == "United States of America",
                       "United.States.of.America", name))


models_imp_height_analyses = left_join(models_imp_height_coef,
                                            models_imp_height_se,
                                            by = "name") %>%
  mutate(outcome = "H4b(1)) Ideal Height (Importance)")

countries_rescon =
  data_included_documented_rescon %>%
  filter(!is.na(imp_height)) %>%
  select(country) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_imp_height_analyses$n = countries_rescon$Freq

model = mvmeta(mean ~ 1, data = models_imp_height_analyses, S = se^2,
               method = "fixed")
summary(model)
```

##### H3b(2) Ideal Height (Level) {.tabset}
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(ideal_height, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_ideal_height = data_included_documented_rescon_wide %>%
  select(-ideal_height) %>%
  map(~lm(data_included_documented_rescon_wide$ideal_height ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_ideal_height_coef = models_ideal_height %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_ideal_height_se = models_ideal_height %>%
  map(summary) %>%
  tibble(models_ideal_height_se = ., Names = names(.)) %>%
  hoist(models_ideal_height_se, coefficients = "coefficients") %>%
  select(-models_ideal_height_se) %>%
  unnest_wider(., coefficients, names_repair = "universal") %>%
  select(...5, Names) %>%
  rename("name" = "Names",
         "se" = "...5") %>%
  mutate(name = ifelse(name == "United States of America",
                       "United.States.of.America", name))


models_ideal_height_analyses = left_join(models_ideal_height_coef,
                                            models_ideal_height_se,
                                            by = "name") %>%
  mutate(outcome = "H4b(2)) Ideal Height (Level)")

countries_rescon =
  data_included_documented_rescon %>%
  filter(!is.na(ideal_height)) %>%
  select(country) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_ideal_height_analyses$n = countries_rescon$Freq

model = mvmeta(mean ~ 1, data = models_ideal_height_analyses, S = se^2,
               method = "fixed")
summary(model)
```
