---
title: <font color="#66C2A5">Exploratory Analyses Regions</font>
csl: apa-custom-no-issue.csl
output: 
  html_document:
    code_folding: "show"
editor_options: 
  chunk_output_type: console
---

## {.tabset}

### Library
```{r Library}
library(formr)
library(effects)
library(effectsize)
library(lme4)
library(sjstats)
library(lmerTest)
library(ggplot2)
library(tidyr)
library(ggpubr)
library(RColorBrewer)
library(coefplot)
library(tibble)
library(purrr) # for running multiple regression
library(broom)
library(mvmeta)
library(lm.beta)
library(dplyr)
library(stringr)
library(tidyr)
library(knitr)
library(countrycode)

apatheme = theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(),
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5))
```

### Data
Load selected data based on 03_codebook
```{r}
data_included_documented = read.csv(file = "data_included_documented.csv")[,-1]
```

### Inclusion of Data
```{r}
data_included_documented <- data_included_documented %>%
  mutate(region1 = countrycode(country,
                                 origin = "country.name",
                                 destination = "region"),
         region1 = ifelse(country == "Micronesia",
                            "East Asia & Pacific",
                            region1),
         region2 = countrycode(country,
                                 origin = "country.name",
                                 destination = "continent"),
         region2 = ifelse(country == "Micronesia",
                            "Oceania",
                            region2))

table(data_included_documented$region1)
table(data_included_documented$region2)

data_included_documented = data_included_documented %>%
  mutate(region_final = ifelse(region2 == "Africa", "Africa",
                                  ifelse(region2 == "Asia", "Asia",
                                         ifelse(region2 == "Europe", "Europe",
                           ifelse(region2 == "Oceania", "Oceania",
                                  ifelse(region1 == "Latin America & Caribbean",
                                         "Latin & South America",
                                         ifelse(region1 == "North America",
                                                "North America", NA)))))))

data_included_documented <- data_included_documented %>%
  mutate(region_final = ifelse(country %in% c("Afghanistan", "Bahrain", "Iran",
                                                 "Iraq", "Israel", "Jordan", 
                                                 "Kazakhstan", "Kuwait", "Kyrgyzstan",
                                                 "Lebanon", "Pakistan", 
                                                 "Palestinian Territories", "Qatar",
                                                 "Saudi Arabia", "Syria", 
                                                 "Turkey", "Turkmenistan",
                                                 "United Arab Emirates", "Indonesia"),
                                  "Middle East & Central Asia", region_final),
         region_final = ifelse(country %in% c("Armenia", "Burma",
                                                 "China",
                                                 "East Timor (see Timor-Leste)", 
                                                 "Georgia", "Hong Kong", "India",
                                                 "Japan", "Malaysia", "Maldives",
                                                 "Nepal", "Philippines", "Singapore",
                                                 "South Korea", "Sri Lanka", 
                                                 "Taiwan", "Thailand", "Vietnam"), 
                                  "South & East Asia", region_final))

x <- data_included_documented %>% 
  select(country, region_final) %>%
  group_by(country, region_final) %>%
  summarize(n = n()) %>%
  arrange(region_final, country)

write.csv2(x, file = "country_regions.csv")

regions <- x %>%
  group_by(region_final) %>%
  summarize(countries = n(),
            participants = sum(n))

regions
```
We will include all regions with more than 500 participants. This allows us to show effect sizes for a diverse range of regions.

These regions include the following countries (n)

Africa (108):
Algeria (7); Benin (2); Botswana (1); Cameroon (3); Central African Republic (2); Cote d'Ivoire (1); Egypt (3); Ethiopia (1); Ghana (3); Guinea-Bissau (1); Kenya (6); Madagascar (1); Mali (2); Mauritania (1); Mauritius (2); Morocco (16); Namibia (4); Nigeria (6); Senegal (5); South Africa (29); South Sudan (1); Swaziland (1); Tanzania (1); Tunisia (7); Uganda (1); Zimbabwe (1)

Europe (7,417):
Albania (2); Andorra (6); Austria (197); Belarus (13); Belgium (102); Bosnia and Herzegovina (6); Bulgaria (9); Croatia (6); Czechia (11); Denmark (395); Estonia (12); Finland (31); France (2013); Germany (1846); Greece (4); Hungary (9); Iceland (5); Ireland (59); Italy (968); Latvia (8); Liechtenstein (1); Lithuania (3); Luxembourg (13); Macedonia (1); Malta (2); Monaco (1); Montenegro (1); Netherlands (44); Norway (12); Poland (7); Portugal (51); Romania (24); Russia (155); Serbia (5); Slovakia (3); Slovenia (3); Spain (562); Sweden (27); Switzerland (280); Ukraine (21); United Kingdom (499)

Latin & South America (3,325):
Antigua and Barbuda (2); Argentina (217); Aruba (1); Bahamas, The (1); Barbados (1); Belize (1); Bolivia (23); Brazil (806); Chile (154); Colombia (387); Costa Rica (47); Cuba (1); Dominica (2); Dominican Republic (41); Ecuador (102); El Salvador (26); Grenada (1); Guatemala (61); Guyana (3); Haiti (4); Honduras (18); Jamaica (6); Mexico (1157); Nicaragua (15); Panama (15); Paraguay (11); Peru (119); Saint Lucia (2); Saint Vincent and the Grenadines (1); Sint Maarten (1); Trinidad and Tobago (8); Uruguay (24); Venezuela (67)

Middle East & Central Asia (103):
Afghanistan (1); Bahrain (3); Indonesia (18); Iran (7); Iraq (1); Israel (13); Jordan (2); Kazakhstan (9); Kuwait (1); Kyrgyzstan (2); Lebanon (3); Pakistan (8); Palestinian Territories (2); Qatar (2); Saudi Arabia (6); Syria (1); Turkey (8); Turkmenistan (2); United Arab Emirates (14)

North America (1,592):
Canada (338); United States of America (1254)

Oceania (170):
Australia (133); Fiji (1); Marshall Islands (1); Micronesia (1); New Zealand (34)

South & East Asia (542):
Armenia (2); Burma (1); China (90); East Timor (1); Georgia (3); Hong Kong (8); India (45); Japan (290); Malaysia (17); Maldives (1); Nepal (1); Philippines (36); Singapore (26); South Korea (5); Sri Lanka (3); Taiwan (7); Thailand (4); Vietnam (2)

For the exploratory analyses we can include the following regions: Europe (7,417), Latin & South America (3,325), North America (1,592), and South & East Asia (542). Sample sizes of other regions are too small (n < 500) to reach any conclusions.

```{r}
regions = regions %>% filter(participants > 500)
data_included_documented_reg = data_included_documented %>%
  filter(region_final %in% regions$region_final)
```

```{r}
regions_reg =
  data_included_documented_reg %>%
  select(region_final, country) %>%
  table() %>%
  as.data.frame() %>%
  filter(Freq != 0) %>%
  arrange(-Freq)


regions_reg
```


### Analyses {.tabset .active}
#### Political, Ethnic, and Religious Similarity {.tabset}
##### H1a Preference for Similarity in Political Beliefs {.tabset}
###### H1a(1) Linear Effect
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(pref_politicalsim, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_pref_politicalsim = data_included_documented_reg_wide %>%
  select(-pref_politicalsim) %>%
  map(~lm(scale(data_included_documented_reg_wide$pref_politicalsim) ~ scale(.x),
      data = data_included_documented_reg_wide)) %>%
  map(lm.beta)

models_pref_politicalsim_lin_coef = models_pref_politicalsim %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_politicalsim_lin_se = models_pref_politicalsim %>%
  map(tidy) %>%
  tibble(models_pref_politicalsim_lin_se = ., Names = names(.)) %>%
  hoist(models_pref_politicalsim_lin_se, coefficients = "std.error") %>%
  select(-models_pref_politicalsim_lin_se) %>%
  unnest_wider(., coefficients, names_sep = "_") %>%
  select(coefficients_2, Names) %>%
  rename("name" = "Names",
         "se" = "coefficients_2") %>%
  mutate(name = ifelse(name == "South & East Asia",
                       "South...East.Asia",
                       ifelse(name == "Latin & South America",
                       "Latin...South.America",
                       ifelse(name == "North America",
                       "North.America",
                       name))))


models_pref_politicalsim_lin_analyses = left_join(models_pref_politicalsim_lin_coef,
                                            models_pref_politicalsim_lin_se,
                                            by = "name") %>%
  mutate(outcome = "H2a) Prefered Political Similarity - Linear Effect")

countries_reg =
  data_included_documented_reg %>%
  filter(!is.na(pref_politicalsim)) %>%
  select(region_final) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_pref_politicalsim_lin_analyses$n = countries_reg$Freq
data_included_documented_reg %>% filter(!is.na(pref_politicalsim)) %>% nrow()

model = mvmeta(mean ~ 1, data = models_pref_politicalsim_lin_analyses, S = se^2,
               method = "fixed")
summary(model)
```

###### H1a(2) Quadratic Effect: Regression 1 (x <= breaking_point)

```{r}
data_included_documented_reg_wide_reg1 = data_included_documented_reg %>%
  dplyr::filter(political_orientation <= 3) %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(pref_politicalsim, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_pref_politicalsim_reg1 = data_included_documented_reg_wide_reg1 %>%
  select(-pref_politicalsim) %>%
  map(~lm(scale(data_included_documented_reg_wide_reg1$pref_politicalsim) ~
            scale(.x),
          data = data_included_documented_reg_wide_reg1)) %>%
  map(lm.beta)

models_pref_politicalsim_quad_coef_reg1 = models_pref_politicalsim_reg1 %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)


models_pref_politicalsim_quad_se_reg1 = models_pref_politicalsim_reg1 %>%
  map(tidy) %>%
  tibble(models_pref_politicalsim_lin_se = ., Names = names(.)) %>%
  hoist(models_pref_politicalsim_lin_se, coefficients = "std.error") %>%
  select(-models_pref_politicalsim_lin_se) %>%
  unnest_wider(., coefficients, names_sep = "_") %>%
  select(coefficients_2, Names) %>%
  rename("name" = "Names",
         "se" = "coefficients_2") %>%
  mutate(name = ifelse(name == "South & East Asia",
                       "South...East.Asia",
                       ifelse(name == "Latin & South America",
                       "Latin...South.America",
                       ifelse(name == "North America",
                       "North.America",
                       name))))


models_pref_politicalsim_quad_analyses_reg1 = left_join(models_pref_politicalsim_quad_coef_reg1,
                                            models_pref_politicalsim_quad_se_reg1,
                                            by = "name") %>%
  mutate(outcome = "H2a(1)) Preferred Political Similarity - Quadratic Effect Regression 1")

models_pref_politicalsim_quad_analyses_reg1$n = countries_reg$Freq

data_included_documented_reg %>% filter(political_orientation <= 3, !is.na(pref_politicalsim)) %>% nrow()

model = mvmeta(mean ~ 1, data = models_pref_politicalsim_quad_analyses_reg1, S = se^2,
               method = "fixed")
summary(model)
```

###### H1a(2) Quadratic Effect: Regression 2 (x >= breaking_point)
```{r}
data_included_documented_reg_wide_reg2 = data_included_documented_reg %>%
  dplyr::filter(political_orientation >= 3) %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(pref_politicalsim, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_pref_politicalsim_reg2 = data_included_documented_reg_wide_reg2 %>%
  select(-pref_politicalsim) %>%
  map(~lm(scale(data_included_documented_reg_wide_reg2$pref_politicalsim) ~
            scale(.x),
          data = data_included_documented_reg_wide_reg2)) %>%
  map(lm.beta)

models_pref_politicalsim_quad_coef_reg2 = models_pref_politicalsim_reg2 %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)


models_pref_politicalsim_quad_se_reg2 = models_pref_politicalsim_reg1 %>%
  map(tidy) %>%
  tibble(models_pref_politicalsim_lin_se = ., Names = names(.)) %>%
  hoist(models_pref_politicalsim_lin_se, coefficients = "std.error") %>%
  select(-models_pref_politicalsim_lin_se) %>%
  unnest_wider(., coefficients, names_sep = "_") %>%
  select(coefficients_2, Names) %>%
  rename("name" = "Names",
         "se" = "coefficients_2") %>%
  mutate(name = ifelse(name == "South & East Asia",
                       "South...East.Asia",
                       ifelse(name == "Latin & South America",
                       "Latin...South.America",
                       ifelse(name == "North America",
                       "North.America",
                       name))))


models_pref_politicalsim_quad_analyses_reg2 = left_join(models_pref_politicalsim_quad_coef_reg2,
                                            models_pref_politicalsim_quad_se_reg2,
                                            by = "name") %>%
  mutate(outcome = "H2a(1)) Preferred Political Similarity - Quadratic Effect Regression 2")

models_pref_politicalsim_quad_analyses_reg2$n = countries_reg$Freq

data_included_documented_reg %>% filter(political_orientation >= 3, !is.na(pref_politicalsim)) %>% nrow()

model = mvmeta(mean ~ 1, data = models_pref_politicalsim_quad_analyses_reg2, S = se^2,
               method = "fixed")
summary(model)
```

##### H1b Preference for Similarity in Ethnicity/Race {.tabset}
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(pref_ethnicalsim, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_pref_ethnicalsim = data_included_documented_reg_wide %>%
  select(-pref_ethnicalsim) %>%
  map(~lm(data_included_documented_reg_wide$pref_ethnicalsim ~ .x,
      data = data_included_documented_reg_wide)) %>%
  map(lm.beta)

models_pref_ethnicalsim_coef = models_pref_ethnicalsim %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_ethnicalsim_se = models_pref_ethnicalsim %>%
 map(tidy) %>%
  tibble(models_pref_politicalsim_lin_se = ., Names = names(.)) %>%
  hoist(models_pref_politicalsim_lin_se, coefficients = "std.error") %>%
  select(-models_pref_politicalsim_lin_se) %>%
  unnest_wider(., coefficients, names_sep = "_") %>%
  select(coefficients_2, Names) %>%
  rename("name" = "Names",
         "se" = "coefficients_2") %>%
  mutate(name = ifelse(name == "South & East Asia",
                       "South...East.Asia",
                       ifelse(name == "Latin & South America",
                       "Latin...South.America",
                       ifelse(name == "North America",
                       "North.America",
                       name))))


models_pref_ethnicalsim_analyses = left_join(models_pref_ethnicalsim_coef,
                                            models_pref_ethnicalsim_se,
                                            by = "name") %>%
  mutate(outcome = "H2b) Preferred Ethnic Similarity")

countries_reg =
  data_included_documented_reg %>%
  filter(!is.na(pref_ethnicalsim)) %>%
  select(region_final) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_pref_ethnicalsim_analyses$n = countries_reg$Freq
sum(models_pref_ethnicalsim_analyses$n)

model = mvmeta(mean ~ 1, data = models_pref_ethnicalsim_analyses, S = se^2,
               method = "fixed")
summary(model)
```

##### H1c Preference for Similarity in Religion {.tabset}
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(pref_religioussim, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_pref_religioussim = data_included_documented_reg_wide %>%
  select(-pref_religioussim) %>%
  map(~lm(data_included_documented_reg_wide$pref_religioussim ~ .x,
      data = data_included_documented_reg_wide)) %>%
  map(lm.beta)

models_pref_religioussim_coef = models_pref_religioussim %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_religioussim_se = models_pref_religioussim %>%
  map(tidy) %>%
  tibble(models_pref_politicalsim_lin_se = ., Names = names(.)) %>%
  hoist(models_pref_politicalsim_lin_se, coefficients = "std.error") %>%
  select(-models_pref_politicalsim_lin_se) %>%
  unnest_wider(., coefficients, names_sep = "_") %>%
  select(coefficients_2, Names) %>%
  rename("name" = "Names",
         "se" = "coefficients_2") %>%
  mutate(name = ifelse(name == "South & East Asia",
                       "South...East.Asia",
                       ifelse(name == "Latin & South America",
                       "Latin...South.America",
                       ifelse(name == "North America",
                       "North.America",
                       name))))


models_pref_religioussim_analyses = left_join(models_pref_religioussim_coef,
                                            models_pref_religioussim_se,
                                            by = "name") %>%
  mutate(outcome = "H2c) Preferred Religious Similarity")

countries_reg =
  data_included_documented_reg %>%
  filter(!is.na(pref_religioussim)) %>%
  select(region_final) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_pref_religioussim_analyses$n = countries_reg$Freq
sum(models_pref_religioussim_analyses$n)

model = mvmeta(mean ~ 1, data = models_pref_religioussim_analyses, S = se^2,
               method = "fixed")
summary(model)
```

#### Ideal Partner Preferences {.tabset}
##### H2a Preference for the Level of Financial Security- Successfulness {.tabset}
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(pref_level_financially_secure_successful_ambitious, Europe, 'South & East Asia', 'Latin & South America',
         'North America')

models_pref_level_financially_secure_successful_ambitious = data_included_documented_reg_wide %>%
  select(-pref_level_financially_secure_successful_ambitious) %>%
  map(~lm(data_included_documented_reg_wide$pref_level_financially_secure_successful_ambitious ~ .x,
      data = data_included_documented_reg_wide)) %>%
  map(lm.beta)

models_pref_level_financially_secure_successful_ambitious_coef = models_pref_level_financially_secure_successful_ambitious %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_level_financially_secure_successful_ambitious_se = models_pref_level_financially_secure_successful_ambitious %>%
  map(tidy) %>%
  tibble(models_pref_politicalsim_lin_se = ., Names = names(.)) %>%
  hoist(models_pref_politicalsim_lin_se, coefficients = "std.error") %>%
  select(-models_pref_politicalsim_lin_se) %>%
  unnest_wider(., coefficients, names_sep = "_") %>%
  select(coefficients_2, Names) %>%
  rename("name" = "Names",
         "se" = "coefficients_2") %>%
  mutate(name = ifelse(name == "South & East Asia",
                       "South...East.Asia",
                       ifelse(name == "Latin & South America",
                       "Latin...South.America",
                       ifelse(name == "North America",
                       "North.America",
                       name))))

models_pref_level_financially_secure_successful_ambitious_analyses = left_join(models_pref_level_financially_secure_successful_ambitious_coef,
                                            models_pref_level_financially_secure_successful_ambitious_se,
                                            by = "name") %>%
  mutate(outcome = "H3a) Financial Security-Successfulness")

countries_reg =
  data_included_documented_reg %>%
  filter(!is.na(pref_level_financially_secure_successful_ambitious)) %>%
  select(region_final) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_pref_level_financially_secure_successful_ambitious_analyses$n = countries_reg$Freq
sum(models_pref_level_financially_secure_successful_ambitious_analyses$n)

model = mvmeta(mean ~ 1, data = models_pref_level_financially_secure_successful_ambitious_analyses, S = se^2,
               method = "fixed")
summary(model)
```


##### H2b Preference for the Level of Confidence-Assertiveness {.tabset}
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(pref_level_confident_assertive, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_pref_level_confident_assertive = data_included_documented_reg_wide %>%
  select(-pref_level_confident_assertive) %>%
  map(~lm(data_included_documented_reg_wide$pref_level_confident_assertive ~ .x,
      data = data_included_documented_reg_wide)) %>%
  map(lm.beta)

models_pref_level_confident_assertive_coef = models_pref_level_confident_assertive %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_level_confident_assertive_se = models_pref_level_confident_assertive %>%
  map(tidy) %>%
  tibble(models_pref_politicalsim_lin_se = ., Names = names(.)) %>%
  hoist(models_pref_politicalsim_lin_se, coefficients = "std.error") %>%
  select(-models_pref_politicalsim_lin_se) %>%
  unnest_wider(., coefficients, names_sep = "_") %>%
  select(coefficients_2, Names) %>%
  rename("name" = "Names",
         "se" = "coefficients_2") %>%
  mutate(name = ifelse(name == "South & East Asia",
                       "South...East.Asia",
                       ifelse(name == "Latin & South America",
                       "Latin...South.America",
                       ifelse(name == "North America",
                       "North.America",
                       name))))


models_pref_level_confident_assertive_analyses = left_join(models_pref_level_confident_assertive_coef,
                                            models_pref_level_confident_assertive_se,
                                            by = "name") %>%
  mutate(outcome = "H3d) Confidence-Assertiveness")

countries_reg =
  data_included_documented_reg %>%
  filter(!is.na(pref_level_confident_assertive)) %>%
  select(region_final) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_pref_level_confident_assertive_analyses$n = countries_reg$Freq
sum(models_pref_level_confident_assertive_analyses$n)

model = mvmeta(mean ~ 1, data = models_pref_level_confident_assertive_analyses, S = se^2,
               method = "fixed")
summary(model)
```


##### H2c Preference for the Level of Education-Intelligence {.tabset}
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(pref_level_intelligence_educated, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_pref_level_intelligence_educated = data_included_documented_reg_wide %>%
  select(-pref_level_intelligence_educated) %>%
  map(~lm(data_included_documented_reg_wide$pref_level_intelligence_educated ~ .x,
      data = data_included_documented_reg_wide)) %>%
  map(lm.beta)

models_pref_level_intelligence_educated_coef = models_pref_level_intelligence_educated %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_level_intelligence_educated_se = models_pref_level_intelligence_educated %>%
  map(tidy) %>%
  tibble(models_pref_politicalsim_lin_se = ., Names = names(.)) %>%
  hoist(models_pref_politicalsim_lin_se, coefficients = "std.error") %>%
  select(-models_pref_politicalsim_lin_se) %>%
  unnest_wider(., coefficients, names_sep = "_") %>%
  select(coefficients_2, Names) %>%
  rename("name" = "Names",
         "se" = "coefficients_2") %>%
  mutate(name = ifelse(name == "South & East Asia",
                       "South...East.Asia",
                       ifelse(name == "Latin & South America",
                       "Latin...South.America",
                       ifelse(name == "North America",
                       "North.America",
                       name))))


models_pref_level_intelligence_educated_analyses = left_join(models_pref_level_intelligence_educated_coef,
                                            models_pref_level_intelligence_educated_se,
                                            by = "name") %>%
  mutate(outcome = "H3e) Education-Intelligence")

countries_reg =
  data_included_documented_reg %>%
  filter(!is.na(pref_level_intelligence_educated)) %>%
  select(region_final) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_pref_level_intelligence_educated_analyses$n = countries_reg$Freq
sum(models_pref_level_intelligence_educated_analyses$n)

model = mvmeta(mean ~ 1, data = models_pref_level_intelligence_educated_analyses, S = se^2,
               method = "fixed")
summary(model)
```

##### H2d Preference for the Level of Kindness-Supportiveness {.tabset}
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(pref_level_kind_supportive, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_pref_level_kind_supportive = data_included_documented_reg_wide %>%
  select(-pref_level_kind_supportive) %>%
  map(~lm(data_included_documented_reg_wide$pref_level_kind_supportive ~ .x,
      data = data_included_documented_reg_wide)) %>%
  map(lm.beta)

models_pref_level_kind_supportive_coef = models_pref_level_kind_supportive %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_level_kind_supportive_se = models_pref_level_kind_supportive %>%
  map(tidy) %>%
  tibble(models_pref_politicalsim_lin_se = ., Names = names(.)) %>%
  hoist(models_pref_politicalsim_lin_se, coefficients = "std.error") %>%
  select(-models_pref_politicalsim_lin_se) %>%
  unnest_wider(., coefficients, names_sep = "_") %>%
  select(coefficients_2, Names) %>%
  rename("name" = "Names",
         "se" = "coefficients_2") %>%
  mutate(name = ifelse(name == "South & East Asia",
                       "South...East.Asia",
                       ifelse(name == "Latin & South America",
                       "Latin...South.America",
                       ifelse(name == "North America",
                       "North.America",
                       name))))


models_pref_level_kind_supportive_analyses = left_join(models_pref_level_kind_supportive_coef,
                                            models_pref_level_kind_supportive_se,
                                            by = "name") %>%
  mutate(outcome = "H3b) Kindness-Supportiveness")

countries_reg =
  data_included_documented_reg %>%
  filter(!is.na(pref_level_kind_supportive)) %>%
  select(region_final) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_pref_level_kind_supportive_analyses$n = countries_reg$Freq
sum(models_pref_level_kind_supportive_analyses$n)

model = mvmeta(mean ~ 1, data = models_pref_level_kind_supportive_analyses, S = se^2,
               method = "fixed")
summary(model)
```

##### H2e Preference for the Level of Attractiveness {.tabset}
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(pref_level_attractiveness, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_pref_level_attractiveness = data_included_documented_reg_wide %>%
  select(-pref_level_attractiveness) %>%
  map(~lm(data_included_documented_reg_wide$pref_level_attractiveness ~ .x,
      data = data_included_documented_reg_wide)) %>%
  map(lm.beta)

models_pref_level_attractiveness_coef = models_pref_level_attractiveness %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_level_attractiveness_se = models_pref_level_attractiveness %>%
 map(tidy) %>%
  tibble(models_pref_politicalsim_lin_se = ., Names = names(.)) %>%
  hoist(models_pref_politicalsim_lin_se, coefficients = "std.error") %>%
  select(-models_pref_politicalsim_lin_se) %>%
  unnest_wider(., coefficients, names_sep = "_") %>%
  select(coefficients_2, Names) %>%
  rename("name" = "Names",
         "se" = "coefficients_2") %>%
  mutate(name = ifelse(name == "South & East Asia",
                       "South...East.Asia",
                       ifelse(name == "Latin & South America",
                       "Latin...South.America",
                       ifelse(name == "North America",
                       "North.America",
                       name))))


models_pref_level_attractiveness_analyses = left_join(models_pref_level_attractiveness_coef,
                                            models_pref_level_attractiveness_se,
                                            by = "name") %>%
  mutate(outcome = "H3c) Attractiveness")

countries_reg =
  data_included_documented_reg %>%
  filter(!is.na(pref_level_attractiveness)) %>%
  select(region_final) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_pref_level_attractiveness_analyses$n = countries_reg$Freq
sum(models_pref_level_attractiveness_analyses$n)

model = mvmeta(mean ~ 1, data = models_pref_level_attractiveness_analyses, S = se^2,
               method = "fixed")
summary(model)
```

#### Ideal Age and Height {.tabset}
##### H3a(1) Ideal Age (Importance) {.tabset}
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(imp_age, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_imp_age = data_included_documented_reg_wide %>%
  select(-imp_age) %>%
  map(~lm(data_included_documented_reg_wide$imp_age ~ .x,
      data = data_included_documented_reg_wide)) %>%
  map(lm.beta)

models_imp_age_coef = models_imp_age %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_imp_age_se = models_imp_age %>%
  map(tidy) %>%
  tibble(models_pref_politicalsim_lin_se = ., Names = names(.)) %>%
  hoist(models_pref_politicalsim_lin_se, coefficients = "std.error") %>%
  select(-models_pref_politicalsim_lin_se) %>%
  unnest_wider(., coefficients, names_sep = "_") %>%
  select(coefficients_2, Names) %>%
  rename("name" = "Names",
         "se" = "coefficients_2") %>%
  mutate(name = ifelse(name == "South & East Asia",
                       "South...East.Asia",
                       ifelse(name == "Latin & South America",
                       "Latin...South.America",
                       ifelse(name == "North America",
                       "North.America",
                       name))))


models_imp_age_analyses = left_join(models_imp_age_coef,
                                            models_imp_age_se,
                                            by = "name") %>%
  mutate(outcome = "H4a(1)) Ideal Age (Importance)")

countries_reg =
  data_included_documented_reg %>%
  filter(!is.na(imp_age)) %>%
  select(region_final) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_imp_age_analyses$n = countries_reg$Freq
sum(models_imp_age_analyses$n)

model = mvmeta(mean ~ 1, data = models_imp_age_analyses, S = se^2,
               method = "fixed")
summary(model)
```

##### H3a(2) Ideal Age (Level) {.tabset}
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(ideal_age_rel, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_ideal_age_rel = data_included_documented_reg_wide %>%
  select(-ideal_age_rel) %>%
  map(~lm(data_included_documented_reg_wide$ideal_age_rel ~ .x,
      data = data_included_documented_reg_wide)) %>%
  map(lm.beta)

models_ideal_age_rel_coef = models_ideal_age_rel %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_ideal_age_rel_se = models_ideal_age_rel %>%
  map(tidy) %>%
  tibble(models_pref_politicalsim_lin_se = ., Names = names(.)) %>%
  hoist(models_pref_politicalsim_lin_se, coefficients = "std.error") %>%
  select(-models_pref_politicalsim_lin_se) %>%
  unnest_wider(., coefficients, names_sep = "_") %>%
  select(coefficients_2, Names) %>%
  rename("name" = "Names",
         "se" = "coefficients_2") %>%
  mutate(name = ifelse(name == "South & East Asia",
                       "South...East.Asia",
                       ifelse(name == "Latin & South America",
                       "Latin...South.America",
                       ifelse(name == "North America",
                       "North.America",
                       name))))


models_ideal_age_rel_analyses = left_join(models_ideal_age_rel_coef,
                                            models_ideal_age_rel_se,
                                            by = "name") %>%
  mutate(outcome = "H4a(2)) Ideal Age (Level)")

countries_reg =
  data_included_documented_reg %>%
  filter(!is.na(ideal_age_rel)) %>%
  select(region_final) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_ideal_age_rel_analyses$n = countries_reg$Freq
sum(models_ideal_age_rel_analyses$n)

model = mvmeta(mean ~ 1, data = models_ideal_age_rel_analyses, S = se^2,
               method = "fixed")
summary(model)
```

##### H3b(1) Ideal Height (Importance) {.tabset}
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(imp_height, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_imp_height = data_included_documented_reg_wide %>%
  select(-imp_height) %>%
  map(~lm(data_included_documented_reg_wide$imp_height ~ .x,
      data = data_included_documented_reg_wide)) %>%
  map(lm.beta)

models_imp_height_coef = models_imp_height %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_imp_height_se = models_imp_height %>%
  map(tidy) %>%
  tibble(models_pref_politicalsim_lin_se = ., Names = names(.)) %>%
  hoist(models_pref_politicalsim_lin_se, coefficients = "std.error") %>%
  select(-models_pref_politicalsim_lin_se) %>%
  unnest_wider(., coefficients, names_sep = "_") %>%
  select(coefficients_2, Names) %>%
  rename("name" = "Names",
         "se" = "coefficients_2") %>%
  mutate(name = ifelse(name == "South & East Asia",
                       "South...East.Asia",
                       ifelse(name == "Latin & South America",
                       "Latin...South.America",
                       ifelse(name == "North America",
                       "North.America",
                       name))))


models_imp_height_analyses = left_join(models_imp_height_coef,
                                            models_imp_height_se,
                                            by = "name") %>%
  mutate(outcome = "H4b(1)) Ideal Height (Importance)")

countries_reg =
  data_included_documented_reg %>%
  filter(!is.na(imp_height)) %>%
  select(region_final) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_imp_height_analyses$n = countries_reg$Freq
sum(models_imp_height_analyses$n)

model = mvmeta(mean ~ 1, data = models_imp_height_analyses, S = se^2,
               method = "fixed")
summary(model)
```

##### H3b(2) Ideal Height (Level) {.tabset}
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(ideal_height, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_ideal_height = data_included_documented_reg_wide %>%
  select(-ideal_height) %>%
  map(~lm(data_included_documented_reg_wide$ideal_height ~ .x,
      data = data_included_documented_reg_wide)) %>%
  map(lm.beta)

models_ideal_height_coef = models_ideal_height %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_ideal_height_se = models_ideal_height %>%
  map(tidy) %>%
  tibble(models_pref_politicalsim_lin_se = ., Names = names(.)) %>%
  hoist(models_pref_politicalsim_lin_se, coefficients = "std.error") %>%
  select(-models_pref_politicalsim_lin_se) %>%
  unnest_wider(., coefficients, names_sep = "_") %>%
  select(coefficients_2, Names) %>%
  rename("name" = "Names",
         "se" = "coefficients_2") %>%
  mutate(name = ifelse(name == "South & East Asia",
                       "South...East.Asia",
                       ifelse(name == "Latin & South America",
                       "Latin...South.America",
                       ifelse(name == "North America",
                       "North.America",
                       name))))


models_ideal_height_analyses = left_join(models_ideal_height_coef,
                                            models_ideal_height_se,
                                            by = "name") %>%
  mutate(outcome = "H4b(2)) Ideal Height (Level)")

countries_reg =
  data_included_documented_reg %>%
  filter(!is.na(ideal_height)) %>%
  select(region_final) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_ideal_height_analyses$n = countries_reg$Freq
sum(models_ideal_height_analyses$n)

model = mvmeta(mean ~ 1, data = models_ideal_height_analyses, S = se^2,
               method = "fixed")
summary(model)
```


### Graphs
#### Models
##### H1a Preference for similarity in political beliefs
###### H1a(1) Linear Effect
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(
    pref_politicalsim, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_pref_politicalsim = data_included_documented_reg_wide %>%
  select(-pref_politicalsim) %>%
  map( ~ lm(
    scale(data_included_documented_reg_wide$pref_politicalsim) ~ scale(.x),
    data = data_included_documented_reg_wide
  )) %>%
  map(lm.beta)

models_pref_politicalsim_lin_coef = models_pref_politicalsim %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_politicalsim_lin_confint_low = models_pref_politicalsim %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname  == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 7))

models_pref_politicalsim_lin_confint_high = models_pref_politicalsim %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname  == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 8))

models_pref_politicalsim_lin_graph = left_join(
  left_join(
    models_pref_politicalsim_lin_coef,
    models_pref_politicalsim_lin_confint_low,
    by = "name"
  ),
  models_pref_politicalsim_lin_confint_high,
  by = "name"
) %>%
  mutate(outcome = "H1a(1)) Preferred Political \nSimilarity - Linear Effect")
```

###### H1a(2) Quadratic Effect
####### Regression 1 (x <= breaking_point)
```{r}
data_included_documented_reg_wide_reg1 = data_included_documented_reg %>%
  dplyr::filter(political_orientation <= 3) %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(
    pref_politicalsim, Europe, 'South & East Asia', 'Latin & South America', 'North America')



models_pref_politicalsim_reg1 = data_included_documented_reg_wide_reg1 %>%
  select(-pref_politicalsim) %>%
  map( ~ lm(
    scale(
      data_included_documented_reg_wide_reg1$pref_politicalsim
    ) ~
      scale(.x),
    data = data_included_documented_reg_wide_reg1
  )) %>%
  map(lm.beta)

models_pref_politicalsim_quad_coef_reg1 = models_pref_politicalsim_reg1 %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_politicalsim_quad_confint_low_reg1 = models_pref_politicalsim_reg1 %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname  == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 7))

models_pref_politicalsim_quad_confint_high_reg1 = models_pref_politicalsim_reg1 %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname  == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 8))

models_pref_politicalsim_quad_graph_reg1 = left_join(
  left_join(
    models_pref_politicalsim_quad_coef_reg1,
    models_pref_politicalsim_quad_confint_low_reg1,
    by = "name"
  ),
  models_pref_politicalsim_quad_confint_high_reg1,
  by = "name"
) %>%
  mutate(outcome = "H1a(2)) Preferred Political \nSimilarity - Quadratic Effect \nPO <= 3")
```


####### Regression 2 (x >= breaking_point)
```{r}
data_included_documented_reg_wide_reg2 = data_included_documented_reg %>%
  dplyr::filter(political_orientation >= 3) %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(
    pref_politicalsim, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_pref_politicalsim_reg2 = data_included_documented_reg_wide_reg2 %>%
  select(-pref_politicalsim) %>%
  map( ~ lm(
    scale(
      data_included_documented_reg_wide_reg2$pref_politicalsim
    ) ~
      scale(.x),
    data = data_included_documented_reg_wide_reg2
  )) %>%
  map(lm.beta)

models_pref_politicalsim_quad_coef_reg2 = models_pref_politicalsim_reg2 %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_politicalsim_quad_confint_low_reg2 = models_pref_politicalsim_reg2 %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname  == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 7))

models_pref_politicalsim_quad_confint_high_reg2 = models_pref_politicalsim_reg2 %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname  == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 8))

models_pref_politicalsim_quad_graph_reg2 = left_join(
  left_join(
    models_pref_politicalsim_quad_coef_reg2,
    models_pref_politicalsim_quad_confint_low_reg2,
    by = "name"
  ),
  models_pref_politicalsim_quad_confint_high_reg2,
  by = "name"
) %>%
  mutate(outcome = "H1a(2)) Preferred Political \nSimilarity - Quadratic Effect \nPO >= 3")
```

##### H1b Preference for similarity in ethnicity/race
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(
    pref_ethnicalsim, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_pref_ethnicalsim = data_included_documented_reg_wide %>%
  select(-pref_ethnicalsim) %>%
  map( ~ lm(
    scale(data_included_documented_reg_wide$pref_ethnicalsim) ~ scale(.x) +
      I(scale(.x) ^ 2),
    data = data_included_documented_reg_wide
  )) %>%
  map(lm.beta)

models_pref_ethnicalsim_coef = models_pref_ethnicalsim %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_ethnicalsim_confint_low = models_pref_ethnicalsim %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname  == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 7))

models_pref_ethnicalsim_confint_high = models_pref_ethnicalsim %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname  == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 8))

models_pref_ethnicalsim_graph = left_join(
  left_join(
    models_pref_ethnicalsim_coef,
    models_pref_ethnicalsim_confint_low,
    by = "name"
  ),
  models_pref_ethnicalsim_confint_high,
  by = "name"
) %>%
  mutate(outcome = "H1b) Preferred \nEthnic Similarity")
```

##### H1c Preference for similarity in religion
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(
    pref_religioussim, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_pref_religioussim = data_included_documented_reg_wide %>%
  select(-pref_religioussim) %>%
  map( ~ lm(
    scale(data_included_documented_reg_wide$pref_religioussim) ~ scale(.x) +
      I(scale(.x) ^ 2),
    data = data_included_documented_reg_wide
  )) %>%
  map(lm.beta)

models_pref_religioussim_coef = models_pref_religioussim %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_religioussim_confint_low = models_pref_religioussim %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname  == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 7))

models_pref_religioussim_confint_high = models_pref_religioussim %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname  == "scale(.x)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 8))

models_pref_religioussim_graph = left_join(
  left_join(
    models_pref_religioussim_coef,
    models_pref_religioussim_confint_low,
    by = "name"
  ),
  models_pref_religioussim_confint_high,
  by = "name"
) %>%
  mutate(outcome = "H1c) Preferred \nReligious Similarity")
```

##### H2a Preference for the level of financial security- successfulness 
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(
    pref_level_financially_secure_successful_ambitious, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_pref_level_financially_secure_successful_ambitious = data_included_documented_reg_wide %>%
  select(-pref_level_financially_secure_successful_ambitious) %>%
  map(
    ~ lm(
      data_included_documented_reg_wide$pref_level_financially_secure_successful_ambitious ~ .x,
      data = data_included_documented_reg_wide
    )
  ) %>%
  map(lm.beta)

models_pref_level_financially_secure_successful_ambitious_coef = models_pref_level_financially_secure_successful_ambitious %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_level_financially_secure_successful_ambitious_confint_low = models_pref_level_financially_secure_successful_ambitious %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 7))

models_pref_level_financially_secure_successful_ambitious_confint_high = models_pref_level_financially_secure_successful_ambitious %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 8))

models_pref_level_financially_secure_successful_ambitious_graph = left_join(
  left_join(
    models_pref_level_financially_secure_successful_ambitious_coef,
    models_pref_level_financially_secure_successful_ambitious_confint_low,
    by = "name"
  ),
  models_pref_level_financially_secure_successful_ambitious_confint_high,
  by = "name"
) %>%
  mutate(outcome = "H2a) Financial Security-\nSuccessfulness")
```

##### H2b Preference for the level of confidence-assertiveness
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(
    pref_level_confident_assertive, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_pref_level_confident_assertive = data_included_documented_reg_wide %>%
  select(-pref_level_confident_assertive) %>%
  map(
    ~ lm(
      data_included_documented_reg_wide$pref_level_confident_assertive ~ .x,
      data = data_included_documented_reg_wide
    )
  ) %>%
  map(lm.beta)

models_pref_level_confident_assertive_coef = models_pref_level_confident_assertive %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_level_confident_assertive_confint_low = models_pref_level_confident_assertive %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 7))

models_pref_level_confident_assertive_confint_high = models_pref_level_confident_assertive %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 8))

models_pref_level_confident_assertive_graph = left_join(
  left_join(
    models_pref_level_confident_assertive_coef,
    models_pref_level_confident_assertive_confint_low,
    by = "name"
  ),
  models_pref_level_confident_assertive_confint_high,
  by = "name"
) %>%
  mutate(outcome = "H2b) Confidence-\nAssertiveness")
```

##### H2c Preference for the level of education-intelligence
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(
    pref_level_intelligence_educated, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_pref_level_intelligence_educated = data_included_documented_reg_wide %>%
  select(-pref_level_intelligence_educated) %>%
  map(
    ~ lm(
      data_included_documented_reg_wide$pref_level_intelligence_educated ~ .x,
      data = data_included_documented_reg_wide
    )
  ) %>%
  map(lm.beta)

models_pref_level_intelligence_educated_coef = models_pref_level_intelligence_educated %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_level_intelligence_educated_confint_low = models_pref_level_intelligence_educated %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 7))

models_pref_level_intelligence_educated_confint_high = models_pref_level_intelligence_educated %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 8))

models_pref_level_intelligence_educated_graph = left_join(
  left_join(
    models_pref_level_intelligence_educated_coef,
    models_pref_level_intelligence_educated_confint_low,
    by = "name"
  ),
  models_pref_level_intelligence_educated_confint_high,
  by = "name"
) %>%
  mutate(outcome = "H2c) Education-\nIntelligence")
```

##### H2d Preference for the level of kindness-supportiveness
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(
    pref_level_kind_supportive, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_pref_level_kind_supportive = data_included_documented_reg_wide %>%
  select(-pref_level_kind_supportive) %>%
  map(
    ~ lm(
      data_included_documented_reg_wide$pref_level_kind_supportive ~ .x,
      data = data_included_documented_reg_wide
    )
  ) %>%
  map(lm.beta)

models_pref_level_kind_supportive_coef = models_pref_level_kind_supportive %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_level_kind_supportive_confint_low = models_pref_level_kind_supportive %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 7))

models_pref_level_kind_supportive_confint_high = models_pref_level_kind_supportive %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 8))

models_pref_level_kind_supportive_graph = left_join(
  left_join(
    models_pref_level_kind_supportive_coef,
    models_pref_level_kind_supportive_confint_low,
    by = "name"
  ),
  models_pref_level_kind_supportive_confint_high,
  by = "name"
) %>%
  mutate(outcome = "H2d) Kindness-\nSupportiveness")
```

##### H2e Preference for the level of attractiveness
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(
    pref_level_attractiveness, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_pref_level_attractiveness = data_included_documented_reg_wide %>%
  select(-pref_level_attractiveness) %>%
  map(
    ~ lm(
      data_included_documented_reg_wide$pref_level_attractiveness ~ .x,
      data = data_included_documented_reg_wide
    )
  ) %>%
  map(lm.beta)

models_pref_level_attractiveness_coef = models_pref_level_attractiveness %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_pref_level_attractiveness_confint_low = models_pref_level_attractiveness %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 7))

models_pref_level_attractiveness_confint_high = models_pref_level_attractiveness %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 8))

models_pref_level_attractiveness_graph = left_join(
  left_join(
    models_pref_level_attractiveness_coef,
    models_pref_level_attractiveness_confint_low,
    by = "name"
  ),
  models_pref_level_attractiveness_confint_high,
  by = "name"
) %>%
  mutate(outcome = "H2e) Attractiveness")
```


##### H3a(1) Ideal age (importance)
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(imp_age, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_imp_age = data_included_documented_reg_wide %>%
  select(-imp_age) %>%
  map(
    ~ lm(data_included_documented_reg_wide$imp_age ~ .x,
         data = data_included_documented_reg_wide)
  ) %>%
  map(lm.beta)

models_imp_age_coef = models_imp_age %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_imp_age_confint_low = models_imp_age %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 7))

models_imp_age_confint_high = models_imp_age %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 8))

models_imp_age_graph = left_join(
  left_join(models_imp_age_coef,
            models_imp_age_confint_low,
            by = "name"),
  models_imp_age_confint_high,
  by = "name"
) %>%
  mutate(outcome = "H3a(1)) Ideal Age \n(Importance)")
```

##### H3a(2) Ideal age (level)
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(ideal_age_rel, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_ideal_age_rel = data_included_documented_reg_wide %>%
  select(-ideal_age_rel) %>%
  map(
    ~ lm(
      data_included_documented_reg_wide$ideal_age_rel ~ .x,
      data = data_included_documented_reg_wide
    )
  ) %>%
  map(lm.beta)

models_ideal_age_rel_coef = models_ideal_age_rel %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_ideal_age_rel_confint_low = models_ideal_age_rel %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 7))

models_ideal_age_rel_confint_high = models_ideal_age_rel %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 8))

models_ideal_age_rel_graph = left_join(
  left_join(
    models_ideal_age_rel_coef,
    models_ideal_age_rel_confint_low,
    by = "name"
  ),
  models_ideal_age_rel_confint_high,
  by = "name"
) %>%
  mutate(outcome = "H3a(2)) Ideal Age \n(Level)")
```

##### H3b(1) Ideal height (importance)
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(imp_height, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_imp_height = data_included_documented_reg_wide %>%
  select(-imp_height) %>%
  map(
    ~ lm(data_included_documented_reg_wide$imp_height ~ .x,
         data = data_included_documented_reg_wide)
  ) %>%
  map(lm.beta)

models_imp_height_coef = models_imp_height %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_imp_height_confint_low = models_imp_height %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 7))

models_imp_height_confint_high = models_imp_height %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 8))

models_imp_height_graph = left_join(
  left_join(models_imp_height_coef,
            models_imp_height_confint_low,
            by = "name"),
  models_imp_height_confint_high,
  by = "name"
) %>%
  mutate(outcome = "H3b(1)) Ideal Height \n(Importance)")
```

##### H3b(2) Ideal height (level)
```{r}
data_included_documented_reg_wide = data_included_documented_reg %>%
  pivot_wider(names_from = region_final, values_from = political_orientation) %>%
  select(ideal_height, Europe, 'South & East Asia', 'Latin & South America', 'North America')

models_ideal_height = data_included_documented_reg_wide %>%
  select(-ideal_height) %>%
  map(
    ~ lm(data_included_documented_reg_wide$ideal_height ~ .x,
         data = data_included_documented_reg_wide)
  ) %>%
  map(lm.beta)

models_ideal_height_coef = models_ideal_height %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_ideal_height_confint_low = models_ideal_height %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 7))

models_ideal_height_confint_high = models_ideal_height %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name) - 8))

models_ideal_height_graph = left_join(
  left_join(
    models_ideal_height_coef,
    models_ideal_height_confint_low,
    by = "name"
  ),
  models_ideal_height_confint_high,
  by = "name"
) %>%
  mutate(outcome = "H3b(2)) Ideal Height \n(Level)")
```

#### Combine Graph One
```{r}
data_graph = rbind(
  models_pref_politicalsim_lin_graph,
  models_pref_politicalsim_quad_graph_reg1,
  models_pref_politicalsim_quad_graph_reg2,
  models_pref_ethnicalsim_graph,
  models_pref_religioussim_graph
) %>%
  mutate(outcome = factor(
    outcome,
    levels = c(
      "H1c) Preferred \nReligious Similarity",
      "H1b) Preferred \nEthnic Similarity",
      "H1a(2)) Preferred Political \nSimilarity - Quadratic Effect \nPO >= 3",
      "H1a(2)) Preferred Political \nSimilarity - Quadratic Effect \nPO <= 3",
      "H1a(1)) Preferred Political \nSimilarity - Linear Effect"
    )
  ))


data_graph$name = factor(rep(
  c(
    paste0(
      "Europe (n = ",
      sum(data_included_documented_reg$region_final == "Europe"),
      ")"
    ),
    paste0(
      "South & East Asia (n = ",
      sum(data_included_documented_reg$region_final == "South & East Asia"),
      ")"
    ),
    paste0(
      "Latin & South America (n = ",
      sum(
        data_included_documented_reg$region_final == "Latin & South America"
      ),
      ")"
    ),
    paste0(
      "North America (n = ",
      sum(data_included_documented_reg$region_final == "North America"),
      ")"
    )
  ),
  5
))

l_countries = levels(data_graph$name)
data_graph$name = factor(data_graph$name,
                         levels = rev(
                           c(
                             l_countries[1],
                             l_countries[2],
                             l_countries[3],
                             l_countries[4])
                         ))
```

#### Graph One Multiplot {.active}
```{r}
multiplot = ggplot(data_graph, aes(outcome, mean)) +
  geom_hline(yintercept = 0, linewidth = 1.5)  +
  geom_hline(yintercept = -.05,
             linetype = "dotted",
             linewidth = 1.5) +
  geom_hline(yintercept = .05,
             linetype = "dotted",
             linewidth = 1.5) +
  geom_pointrange(
    data = data_graph,
    mapping = aes(
      x = outcome,
      y = mean,
      ymin = conf_low ,
      ymax = conf_high ,
      group = name,
      color = name
    ),
    position = position_dodge(width = 0.4)
  ) +
  coord_flip() +
  apatheme +
  scale_colour_brewer(palette = "Dark2")  +
  labs(y = "Effect of Political Orientation", x = "Outcome") +
  theme(
    text = element_text(size = 20),
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    legend.text = element_text(size = 15),
    plot.title = element_text(hjust = 0),
    legend.background = element_rect(
      fill = "grey",
      linewidth = 0.5,
      linetype = "solid"
    )
  ) +
  guides(col = guide_legend(reverse = TRUE))
multiplot
```

##### Save image
```{r}
jpeg(
  "kuschel-figure_exploratiory_regions1.jpeg",
  width = 2*5000,
  height = 2*3000,
  res = 600
)
multiplot
dev.off()
```

#### Combine Graph Two
```{r}
data_graph2 = rbind(
  models_pref_level_financially_secure_successful_ambitious_graph,
  models_pref_level_kind_supportive_graph,
  models_pref_level_attractiveness_graph,
  models_pref_level_confident_assertive_graph,
  models_pref_level_intelligence_educated_graph,
  models_imp_age_graph,
  models_ideal_age_rel_graph,
  models_imp_height_graph,
  models_ideal_height_graph
) %>%
  mutate(outcome = factor(
    outcome,
    levels = c(
      "H3b(2)) Ideal Height \n(Level)",
      "H3b(1)) Ideal Height \n(Importance)",
      "H3a(2)) Ideal Age \n(Level)",
      "H3a(1)) Ideal Age \n(Importance)",
      "H2e) Attractiveness",
      "H2d) Kindness-\nSupportiveness",
      "H2c) Education-\nIntelligence",
      "H2b) Confidence-\nAssertiveness",
      "H2a) Financial Security-\nSuccessfulness"
    )
  ))



data_graph2$name = factor(rep(
  c(
    paste0(
      "Europe (n = ",
      sum(data_included_documented_reg$region_final == "Europe"),
      ")"
    ),
    paste0(
      "South & East Asia (n = ",
      sum(data_included_documented_reg$region_final == "South & East Asia"),
      ")"
    ),
    paste0(
      "Latin & South America (n = ",
      sum(
        data_included_documented_reg$region_final == "Latin & South America"
      ),
      ")"
    ),
    paste0(
      "North America (n = ",
      sum(data_included_documented_reg$region_final == "North America"),
      ")"
    )
  ),
  9
))

l_countries = levels(data_graph2$name)
data_graph2$name = factor(data_graph2$name,
                         levels = rev(
                           c(
                             l_countries[1],
                             l_countries[2],
                             l_countries[3],
                             l_countries[4])
                         ))
```

#### Graph Two Multiplot
```{r}
multiplot2 = ggplot(data_graph2, aes(outcome, mean)) +
  geom_hline(yintercept = 0, linewidth = 1.5)  +
  geom_hline(yintercept = -.05,
             linetype = "dotted",
             linewidth = 1.5) +
  geom_hline(yintercept = .05,
             linetype = "dotted",
             linewidth = 1.5) +
  geom_pointrange(
    data = data_graph2,
    mapping = aes(
      x = outcome,
      y = mean,
      ymin = conf_low ,
      ymax = conf_high ,
      group = name,
      color = name
    ),
    position = position_dodge(width = 0.4)
  ) +
  coord_flip() +
  apatheme +
  scale_colour_brewer(palette = "Dark2")  +
  labs(y = "Effect of Political Orientation", x = "Outcome") +
  theme(
    text = element_text(size = 20),
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    legend.text = element_text(size = 15),
    plot.title = element_text(hjust = 0),
    legend.background = element_rect(
      fill = "grey",
      linewidth = 0.5,
      linetype = "solid"
    )
  ) +
  guides(col = guide_legend(reverse = TRUE))
multiplot2
```

##### Save image
```{r}
jpeg(
  "kuschel-figure_exploratiory_regions2.jpeg",
  width = 2*5000,
  height = 2*3000,
  res = 2*300
)
multiplot2
dev.off()
```

