---
title: <font color="#66C2A5">Graphs Exploratory Analysis</font>
csl: apa-custom-no-issue.csl
output: 
  html_document:
    code_folding: "hide"
editor_options: 
  chunk_output_type: console
---

## {.tabset}
## Preferred Relationship Options Graph Exploratory Analysis
### Library
```{r Library}
library(formr)
library(effects)
library(effectsize)
library(lme4)
library(sjstats)
library(lmerTest)
library(ggplot2)
library(tidyr)
library(ggpubr)
library(RColorBrewer)
library(coefplot)
library(tibble)
library(purrr) # for running multiple regression
library(broom)
library(lm.beta)
library(dplyr)
library(stringr)
library(tidyr)

apatheme = theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(),
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5))
```

### Data
Load selected data based on 03_codebook
```{r}
data_included_documented = read.csv(file = "data_included_documented.csv")[,-1]
```

### Inclusion of data
```{r}
countries = as.data.frame(table(data_included_documented$country)) %>%
  arrange(-Freq)

countries
```
We will include all countries with more than 500 participants. This allows us to show effect sizes for a diverse range of countries.
Diversity of countries is indicated by:

* location: European (France, Germany, Italy, Spain); North American (United States of America); South American (Mexico, Brazil)
* language: French (France); German (Germany); English (United States of America); Spanish (Mexico, Spain); Italian (Italy); Portuguese (Brazil)
* culture: Western (France, Germany, Italy, Spain, United States of America); Non-Western (Mexico, Brazil)

Sample sizes of other countries are too small (n < 500) to reach any conclusions.

```{r}
seven_countries = countries %>% filter(Freq > 500)
data_included_documented_rescon = data_included_documented %>%
  filter(country %in% seven_countries$Var1)
```

```{r}
countries_rescon = as.data.frame(table(data_included_documented_rescon$country)) %>%
  arrange(-Freq)
countries_rescon
```

### Models
#### S1 Interest in Single Life
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(interest_single, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_interest_single = data_included_documented_rescon_wide %>%
  select(-interest_single) %>%
  map(~lm(data_included_documented_rescon_wide$interest_single ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_interest_single_coef = models_interest_single %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_interest_single_confint_low = models_interest_single %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name)-7))

models_interest_single_confint_high = models_interest_single %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name)-8))

models_interest_single_graph = left_join(left_join(models_interest_single_coef,
                                         models_interest_single_confint_low,
                                         by = "name"),
                                         models_interest_single_confint_high,
                                         by = "name") %>%
  mutate(outcome = "S1) Interest in Single Life")
```

####  S2 Interest in sexual, non-romantic relationships
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(interest_sexrel, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_interest_sexrel = data_included_documented_rescon_wide %>%
  select(-interest_sexrel) %>%
  map(~lm(data_included_documented_rescon_wide$interest_sexrel ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_interest_sexrel_coef = models_interest_sexrel %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_interest_sexrel_confint_low = models_interest_sexrel %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name)-7))

models_interest_sexrel_confint_high = models_interest_sexrel %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name)-8))

models_interest_sexrel_graph = left_join(left_join(models_interest_sexrel_coef,
                                         models_interest_sexrel_confint_low,
                                         by = "name"),
                                         models_interest_sexrel_confint_high,
                                         by = "name") %>%
  mutate(outcome = "S2) Interest in Sexual,\nNon-Romantic Relationships")
```

#### S3 Interest in non-monogamous relationships
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(interest_nonmonrel, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_interest_nonmonrel = data_included_documented_rescon_wide %>%
  select(-interest_nonmonrel) %>%
  map(~lm(data_included_documented_rescon_wide$interest_nonmonrel ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_interest_nonmonrel_coef = models_interest_nonmonrel %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_interest_nonmonrel_confint_low = models_interest_nonmonrel %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name)-7))

models_interest_nonmonrel_confint_high = models_interest_nonmonrel %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name)-8))

models_interest_nonmonrel_graph = left_join(left_join(models_interest_nonmonrel_coef,
                                         models_interest_nonmonrel_confint_low,
                                         by = "name"),
                                         models_interest_nonmonrel_confint_high,
                                         by = "name") %>%
  mutate(outcome = "S3) Interest in \nNon-Monogamous Relationships")
```

#### S4 Interest in monogamous relationships
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(interest_monrel, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_interest_monrel = data_included_documented_rescon_wide %>%
  select(-interest_monrel) %>%
  map(~lm(data_included_documented_rescon_wide$interest_monrel ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_interest_monrel_coef = models_interest_monrel %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_interest_monrel_confint_low = models_interest_monrel %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "0.15")) %>%
  rename(conf_low = value) %>%
  mutate(name = substr(name, 1, nchar(name)-7))

models_interest_monrel_confint_high = models_interest_monrel %>%
  map(confint, level = 0.997)  %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  filter(str_detect(name, "99.85")) %>%
  rename(conf_high = value) %>%
  mutate(name = substr(name, 1, nchar(name)-8))

models_interest_monrel_graph = left_join(left_join(models_interest_monrel_coef,
                                         models_interest_monrel_confint_low,
                                         by = "name"),
                                         models_interest_monrel_confint_high,
                                         by = "name") %>%
  mutate(outcome = "S4) Interest in \nMonogamous Relationships")
```

### Combine Graph One
```{r}
data_graph = rbind(models_interest_single_graph, models_interest_sexrel_graph,
                   models_interest_nonmonrel_graph, models_interest_monrel_graph
                   ) %>%
  mutate(outcome = factor(outcome,
                          levels = c(
                                     "S4) Interest in \nMonogamous Relationships",
                                     "S3) Interest in \nNon-Monogamous Relationships",
                                     "S2) Interest in Sexual,\nNon-Romantic Relationships",
                                   "S1) Interest in Single Life")))


data_graph$name = factor(rep(c(
  paste0("France (n = ",
         sum(data_included_documented_rescon$country == "France"), ")"),
  paste0("Germany (n = ",
         sum(data_included_documented_rescon$country == "Germany"), ")"),
  paste0("United States of America (n = ",
         sum(data_included_documented_rescon$country == "United States of America"),
         ")"),
  paste0("Mexico (n = ",
         sum(data_included_documented_rescon$country == "Mexico"), ")"),
  paste0("Italy (n = ",
         sum(data_included_documented_rescon$country == "Italy"), ")"),
  paste0("Brazil (n = ",
         sum(data_included_documented_rescon$country == "Brazil"), ")"),
  paste0("Spain (n = ",
         sum(data_included_documented_rescon$country == "Spain"), ")")),
  4))

l_countries = levels(data_graph$name)
data_graph$name = factor(data_graph$name,
                         levels = rev(c(l_countries[2], l_countries[3],
                                    l_countries[7], l_countries[5],
                                    l_countries[4], l_countries[1],
                                    l_countries[6])))
```

### Graph One Multiplot {.active}
```{r}
multiplot = ggplot(data_graph, aes(outcome, mean)) +
  geom_hline(yintercept = 0, size = 1.5)  +
  geom_hline(yintercept = -.05, linetype = "dotted", size = 1.5) + 
  geom_hline(yintercept = .05, linetype = "dotted", size = 1.5) +
  geom_pointrange(data = data_graph,
                  mapping = aes(x = outcome, y = mean,
                                ymin = conf_low , ymax = conf_high , group = name,
                                color = name),
                  position = position_dodge(width=0.4)) + 
  coord_flip() +
  apatheme +
  scale_colour_brewer(palette = "Dark2")  +
  labs(y = "Effect of Right-Wing Political Orientation", x = "Outcome") +
  theme(text = element_text(size=20), axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        plot.title = element_text(hjust = 0),
        legend.background = element_rect(fill="grey", 
                                         size=0.5, linetype="solid")) +
  guides(col = guide_legend(reverse= TRUE))
multiplot
```

#### Save image
```{r}
jpeg("Exploratory_relationship_options.jpeg", width = 5000, height = 3000, res=300)
multiplot
dev.off()
```

## Preferred Relationship Options Exploratory Analysis
### Library
```{r Library}
library(formr)
library(effects)
library(effectsize)
library(lme4)
library(sjstats)
library(lmerTest)
library(ggplot2)
library(tidyr)
library(ggpubr)
library(RColorBrewer)
library(coefplot)
library(tibble)
library(purrr) # for running multiple regression
library(broom)
library(mvmeta)
library(lm.beta)
library(dplyr)
library(stringr)
library(tidyr)

apatheme = theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(),
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5))
```

### Data
Load selected data based on 03_codebook
```{r}
data_included_documented = read.csv(file = "data_included_documented.csv")[,-1]
```

### Inclusion of Data
```{r}
countries = as.data.frame(table(data_included_documented$country)) %>%
  arrange(-Freq)

countries
```
We will include all countries with more than 500 participants. This allows us to show effect sizes for a diverse range of countries.
Diversity of countries is indicated by:

* location: European (France, Germany, Italy, Spain); North American (United States of America); South American (Mexico, Brazil)
* language: French (France); German (Germany); English (United States of America); Spanish (Mexico, Spain); Italian (Italy); Portuguese (Brazil)
* culture: Western (France, Germany, Italy, Spain, United States of America); Non-Western (Mexico, Brazil)

Sample sizes of other countries are too small (n < 500) to reach any conclusions.

```{r}
seven_countries = countries %>% filter(Freq > 500)
data_included_documented_rescon = data_included_documented %>%
  filter(country %in% seven_countries$Var1)
```

```{r}
countries_rescon =
  data_included_documented_rescon %>%
  select(country) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)


countries_rescon
```

### Models {.tabset .active}
#### Preferred Relationship Options {.tabset .active}
##### S1 Interest in Single Life {.tabset .active}
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(interest_single, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_interest_single = data_included_documented_rescon_wide %>%
  select(-interest_single) %>%
  map(~lm(data_included_documented_rescon_wide$interest_single ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_interest_single_coef = models_interest_single %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_interest_single_se = models_interest_single %>%
  map(summary) %>%
  tibble(models_interest_single_se = ., Names = names(.)) %>%
  hoist(models_interest_single_se, coefficients = "coefficients") %>%
  select(-models_interest_single_se) %>%
  unnest_wider(., coefficients, names_repair = "universal") %>%
  select(...5, Names) %>%
  rename("name" = "Names",
         "se" = "...5") %>%
  mutate(name = ifelse(name == "United States of America",
                       "United.States.of.America", name))


models_interest_single_analyses = left_join(models_interest_single_coef,
                                            models_interest_single_se,
                                            by = "name") %>%
  mutate(outcome = "H1a) Interest in Single Life")

countries_rescon =
  data_included_documented_rescon %>%
  filter(!is.na(interest_single)) %>%
  select(country) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_interest_single_analyses$n = countries_rescon$Freq

model = mvmeta(mean ~ 1, data = models_interest_single_analyses, S = se^2,
               method = "fixed")
summary(model)
```

##### S2 Interest in Sexual, Non-Romantic Relationships {.tabset}
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(interest_sexrel, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_interest_sexrel = data_included_documented_rescon_wide %>%
  select(-interest_sexrel) %>%
  map(~lm(data_included_documented_rescon_wide$interest_sexrel ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_interest_sexrel_coef = models_interest_sexrel %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_interest_sexrel_se = models_interest_sexrel %>%
  map(summary) %>%
  tibble(models_interest_sexrel_se = ., Names = names(.)) %>%
  hoist(models_interest_sexrel_se, coefficients = "coefficients") %>%
  select(-models_interest_sexrel_se) %>%
  unnest_wider(., coefficients, names_repair = "universal") %>%
  select(...5, Names) %>%
  rename("name" = "Names",
         "se" = "...5") %>%
  mutate(name = ifelse(name == "United States of America",
                       "United.States.of.America", name))


models_interest_sexrel_analyses = left_join(models_interest_sexrel_coef,
                                            models_interest_sexrel_se,
                                            by = "name") %>%
  mutate(outcome = "H1b) Interest in Sexual, Non-Romantic Relationships")

countries_rescon =
  data_included_documented_rescon %>%
  filter(!is.na(interest_sexrel)) %>%
  select(country) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_interest_sexrel_analyses$n = countries_rescon$Freq

model = mvmeta(mean ~ 1, data = models_interest_sexrel_analyses, S = se^2,
               method = "fixed")
summary(model)
```

##### S3 Interest in Non-Monogamous Relationships {.tabset}
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(interest_nonmonrel, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_interest_nonmonrel = data_included_documented_rescon_wide %>%
  select(-interest_nonmonrel) %>%
  map(~lm(data_included_documented_rescon_wide$interest_nonmonrel ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_interest_nonmonrel_coef = models_interest_nonmonrel %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_interest_nonmonrel_se = models_interest_nonmonrel %>%
  map(summary) %>%
  tibble(models_interest_nonmonrel_se = ., Names = names(.)) %>%
  hoist(models_interest_nonmonrel_se, coefficients = "coefficients") %>%
  select(-models_interest_nonmonrel_se) %>%
  unnest_wider(., coefficients, names_repair = "universal") %>%
  select(...5, Names) %>%
  rename("name" = "Names",
         "se" = "...5") %>%
  mutate(name = ifelse(name == "United States of America",
                       "United.States.of.America", name))


models_interest_nonmonrel_analyses = left_join(models_interest_nonmonrel_coef,
                                            models_interest_nonmonrel_se,
                                            by = "name") %>%
  mutate(outcome = "H1c) Interest in Non-Monogamous Relationships")

countries_rescon =
  data_included_documented_rescon %>%
  filter(!is.na(interest_nonmonrel)) %>%
  select(country) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_interest_nonmonrel_analyses$n = countries_rescon$Freq

model = mvmeta(mean ~ 1, data = models_interest_nonmonrel_analyses, S = se^2,
               method = "fixed")
summary(model)
```

##### S4 Interest in Monogamous Relationships {.tabset}
```{r}
data_included_documented_rescon_wide = data_included_documented_rescon %>%
  pivot_wider(names_from = country, values_from = political_orientation) %>%
  select(interest_monrel, France, Germany, `United States of America`, Mexico,
         Italy, Brazil, Spain)

models_interest_monrel = data_included_documented_rescon_wide %>%
  select(-interest_monrel) %>%
  map(~lm(data_included_documented_rescon_wide$interest_monrel ~ .x,
      data = data_included_documented_rescon_wide)) %>%
  map(lm.beta)

models_interest_monrel_coef = models_interest_monrel %>%
  map(coef) %>%
  as.data.frame() %>%
  rownames_to_column(var = "rowname") %>%
  filter(rowname != "(Intercept)") %>%
  pivot_longer(cols = -rowname) %>%
  select(-rowname) %>%
  rename(mean = value)

models_interest_monrel_se = models_interest_monrel %>%
  map(summary) %>%
  tibble(models_interest_monrel_se = ., Names = names(.)) %>%
  hoist(models_interest_monrel_se, coefficients = "coefficients") %>%
  select(-models_interest_monrel_se) %>%
  unnest_wider(., coefficients, names_repair = "universal") %>%
  select(...5, Names) %>%
  rename("name" = "Names",
         "se" = "...5") %>%
  mutate(name = ifelse(name == "United States of America",
                       "United.States.of.America", name))


models_interest_monrel_analyses = left_join(models_interest_monrel_coef,
                                            models_interest_monrel_se,
                                            by = "name") %>%
  mutate(outcome = "H1c) Interest in Monogamous Relationships")

countries_rescon =
  data_included_documented_rescon %>%
  filter(!is.na(interest_monrel)) %>%
  select(country) %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq)

models_interest_monrel_analyses$n = countries_rescon$Freq

model = mvmeta(mean ~ 1, data = models_interest_monrel_analyses, S = se^2,
               method = "fixed")
summary(model)
```
