---
title: "01_datawrangling"
author: "Laura Botzet"
date: "6 August 2019"
output: html_document
---

## Library
```{r Library}
library(formr)
library(dplyr)
```


## Data
Load selected data based on 00_dataimport
```{r Data}
fulldata_selected = read.csv(file = "fulldata_selected.csv")[,-1]
```

## Inspect Data
```{r Inspect Data}
colnames(fulldata_selected)

fulldata_selected_wrangled = fulldata_selected
```

### Age
Participants younger than 18 were able to insert age but the survey was ended for them afterwards.
```{r Age}
table(fulldata_selected_wrangled$age)
```

@PROBLEM: Variable age was not restricted to a reasonable number, thus numbers larger than 100 were possible. To deal with this we will set all numbers > 100 as missing. This was not mentioned in the preregistration. (@Tanja, @preregistration)
```{r Age 2}
sum(fulldata_selected_wrangled$age > 100)
# This means that age is set as missing for 15 people

fulldata_selected_wrangled = fulldata_selected_wrangled %>%
  mutate(age = ifelse(age > 100, NA, age))

table(is.na(fulldata_selected_wrangled$age))

table(fulldata_selected_wrangled$age < 18)
# 26638 people were not allowed to participate in the survey because they were younger than 18
```

### Partner Preferences
All partner preference items should range from 0 to 6
```{r Partner preferences}
fulldata_selected_wrangled %>%
  select(starts_with("pref_")) %>%
  select(-pref_age_min, -pref_age_max) %>%
  lapply(table)

fulldata_selected_wrangled %>%
  select(starts_with("pref_")) %>%
  select(-pref_age_min, -pref_age_max) %>%
  missingness_patterns()
```

### Prefered Age Range
```{r Prefered age range}
fulldata_selected_wrangled %>%
  select(pref_age_min, pref_age_max) %>%
  lapply(table)
```
@PROBLEM: Variable pref_age_min and pref_age_max were not restricted to a reasonable number, thus numbers larger than 100 were possible. To deal with this we will set all numbers >= 100 as missing. This was not mentioned in the preregistration. (@Tanja, @preregistration)

```{r Prefered age range 2}
sum(fulldata_selected_wrangled$pref_age_min > 100, na.rm = T)
# This means that pref_age_min is set as missing for 2 people

sum(fulldata_selected_wrangled$pref_age_max > 100, na.rm = T)
# This means that pref_age_min is set as missing for 1 participant


fulldata_selected_wrangled = fulldata_selected_wrangled %>%
  mutate(pref_age_min = ifelse(pref_age_min > 100, NA, pref_age_min),
         pref_age_max = ifelse(pref_age_max > 100, NA, pref_age_max))

table(is.na(fulldata_selected_wrangled$pref_age_min))
table(is.na(fulldata_selected_wrangled$pref_age_max))

fulldata_selected_wrangled %>%
  select(pref_age_min, pref_age_max) %>%
  lapply(table)
```

### Country
```{r Country}
table(fulldata_selected_wrangled$country)
table(is.na(fulldata_selected_wrangled$country))
```

### Language
Chinese, Danish, English, French, German, Japanese, Portuguese, Russian, Spanish,
```{r Language}
table(fulldata_selected_wrangled$language)
table(is.na(fulldata_selected_wrangled$country))
```
--> Italian is missing in the preregistration (@preregistration)
  

### Sex
Categories: Woman; Genderqueer/Nonbinary; Man; None of the above; Prefer not to say; Other
```{r Sex}
table(fulldata_selected_wrangled$sex)

# Set missing values as NA
fulldata_selected_wrangled = fulldata_selected_wrangled %>%
  mutate(sex = as.character(sex),
         sex = ifelse(sex == "", NA, sex),
         sex = factor(sex))

table(fulldata_selected_wrangled$sex)

table(is.na(fulldata_selected_wrangled$sex))
```

### Sexual Orientation
heterosexual; Lesbian/Gay/Homosexual; Bisexual/Pansexual; Queer; Asexual; Prefer not to say; Other
```{r Sexual orientation}
table(fulldata_selected_wrangled$sexual_orientation)

# Set missing values as NA
fulldata_selected_wrangled = fulldata_selected_wrangled %>%
  mutate(sexual_orientation = as.character(sexual_orientation),
         sexual_orientation = ifelse(sexual_orientation == "", NA, sexual_orientation),
         sexual_orientation = factor(sexual_orientation))

table(fulldata_selected_wrangled$sexual_orientation)

table(is.na(fulldata_selected_wrangled$sexual_orientation))
```

### Relationship
```{r Relationship}
table(fulldata_selected_wrangled$relationship) #No romantic or sexual relationships during the past 3 months
table(fulldata_selected_wrangled$relationship1) #Other
table(fulldata_selected_wrangled$relationship2) #Short-term (casual) sexual relationship (e.g. hookups or one-night-stands)
table(fulldata_selected_wrangled$relationship3) #New (less than 1 month old) romantic and/or sexual relationship 
table(fulldata_selected_wrangled$relationship4) #Ongoing (longer than 1 month) uncommitted/non-exclusive romantic and/or sexual relationship
table(fulldata_selected_wrangled$relationship5)#Long-term committed/exclusive sexual relationship with one or more partners

fulldata_selected_wrangled = fulldata_selected_wrangled %>%
  mutate(relationship = ifelse(relationship == "True",
                               "No romantic or sexual relationships during the past 3 months, ",
                               ""),
         relationship = ifelse(relationship1 == "True",
                               paste(relationship,
                                     "Other, "),
                               relationship),
         relationship = ifelse(relationship2 == "True",
                               paste(relationship,
                                     "Short-term (casual) sexual relationship (e.g. hookups or one-night-stands), "),
                               relationship),
         relationship = ifelse(relationship3 == "True",
                               paste(relationship,
                                     "New (less than 1 month old) romantic and/or sexual relationship, "),
                               relationship),
         relationship = ifelse(relationship4 == "True",
                               paste(relationship,
                                     "Ongoing (longer than 1 month) uncommitted/non-exclusive romantic and/or sexual relationship, "),
                               relationship),
         relationship = ifelse(relationship5 == "True", 
                               paste(relationship,
                                     "Long-term committed/exclusive sexual relationship with one or more partners, "), 
                               relationship),
         relationship = ifelse(relationship == "", NA, relationship))

table(fulldata_selected_wrangled$relationship)

# Check whether command worked correctly
table(fulldata_selected_wrangled$relationship %contains% "No romantic or sexual relationships during the past 3 months")
```
 

### Answer Accuracy
I took the survey seriously; please use my information in the study.; I did not answer seriously, please disregard my information; I choose not to answer
```{r Answer Accuracy}
table(fulldata_selected_wrangled$answer_accuracy)

# Set missing values as NA
fulldata_selected_wrangled = fulldata_selected_wrangled %>%
  mutate(answer_accuracy = as.character(answer_accuracy),
         answer_accuracy = ifelse(answer_accuracy == "", NA, answer_accuracy),
         answer_accuracy = factor(answer_accuracy))

table(fulldata_selected_wrangled$answer_accuracy)

table(is.na(fulldata_selected_wrangled$answer_accuracy))

fulldata_selected_wrangled %>%
  select(sex, answer_accuracy) %>%
  missingness_patterns()
```
@PROBLEM: We have 7051 missings here, that did answer the rest of the survey. We did not mention in the preregistration what to do with these cases. (@Tanja, @preregistration)

## Save Data
```{r Save data}
write.csv(fulldata_selected_wrangled, file = "fulldata_selected_wrangled.csv")
```

