---
title: "05_analyses"
author: "Laura Botzet"
date: "10 August 2019"
output: 
  html_document:
    code_folding: "hide"
---

## Analyses {.tabset}

### Library
```{r Library}
library(formr)
library(effects)
library(effectsize)
library(lme4)
library(sjstats)
library(lmerTest)
library(dplyr)
```


### Functions
```{r}
model_age_rmslope_rmintercept = function(outcome){
  lmer(outcome ~ age + (1 + age | country),
       data = data_included_documented %>%
         select(outcome = outcome,
                age, country))
}

model_age_rmintercept = function(outcome){
  lmer(outcome ~ age + (1 | country),
       data = data_included_documented %>%
         select(outcome = outcome,
                age, country))
}

runbothmodels = function(outcome){
  model = suppressWarnings(model_age_rmslope_rmintercept(outcome))
  if(!is.null(model@optinfo$conv$lme4$code)){
    print("Model including random slope did not converge. --> Exclude random slope.")
    model =  model_age_rmintercept(outcome)
  }
  else{
    print("Model including random slope did converge.")
    model = model
  }
}

```

### Data
Load selected data based on 03_codebook
```{r}
data_included_documented = read.csv(file = "data_included_documented.csv")[,-1]
```


### Analysis {.tabset}
If the model does not converge, we will first exclude the random slope for country. If the model does still not converge, we will subsequently exclude the random intercept for country.
Instead we will z-standardize outcomes separately for each country.

#### Ideal Partner Preferences {.tabset}
##### 3.1.1. Hypotheses on kindness and supportiveness. - Importance {.tabset}
3.1.1.1. There is no link between age and women’s importance ratings for partner’s kindness and supportiveness (~ warmth-trustworthiness).
Outcome: Importance ratings for partner’s kindness and supportiveness. Predictor: Age. Random intercept and random slope for country.

###### Models
```{r}
model_ippref_kind_supportive = runbothmodels(outcome = 'ippref_kind_supportive')
```

###### Summary
```{r}
summary(model_ippref_kind_supportive)
confint(model_ippref_kind_supportive, level = 0.995)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_ippref_kind_supportive, method = "basic")
ci(standardize_parameters(model_ippref_kind_supportive, method = "basic", ci = 0.995))
```

###### Plot
```{r}
lmer(ippref_kind_supportive ~ age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### 3.1.1. Hypotheses on kindness and supportiveness. - Level {.tabset}
3.1.1.2. There is no link between age and women’s preferences for the levels of kindness and supportiveness (~ warmth-trustworthiness).
Outcome: Preferences for the levels of kindness and supportiveness. Predictor: Age. Random intercept and random slope for country.

###### Models
```{r}
model_ippref_level_kind_supportive = runbothmodels(outcome = 'ippref_level_kind_supportive')
```

###### Summary
```{r}
summary(model_ippref_level_kind_supportive)
confint(model_ippref_level_kind_supportive, level = 0.995)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_ippref_level_kind_supportive, method = "basic")
ci(standardize_parameters(model_ippref_level_kind_supportive, method = "basic", ci = 0.995))
```

###### Plot
```{r}
lmer(ippref_level_kind_supportive ~ age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```


##### 3.1.2. Hypotheses on attractiveness. - Importance {.tabset}
3.1.2.1. There is no link between age and women’s importance ratings for partner’s attractiveness (~ vitality-attractiveness).
8.2.1.2.1. Outcome: Importance ratings for partner’s attractiveness. Predictor: Age. Random intercept and random slope for country.

###### Models
```{r}
model_ippref_attractiveness = runbothmodels(outcome = 'ippref_attractiveness')
```

###### Summary
```{r}
summary(model_ippref_attractiveness)
confint(model_ippref_attractiveness, level = 0.995)

```

###### Standardized Coefficients
```{r}
standardize_parameters(model_ippref_attractiveness, method = "basic")
ci(standardize_parameters(model_ippref_attractiveness, method = "basic", ci = 0.995))
```

###### Plot
```{r}
lmer(ippref_attractiveness ~ age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### 3.1.2. Hypotheses on attractiveness. - Level {.tabset}
3.1.2.2. There is no link between age and women’s preferences for the levels of attractiveness (~ vitality-attractiveness).
Outcome: Preferences for the levels of attractiveness. Predictor: Age. Random intercept and random slope for country.

###### Models
```{r}
model_ippref_level_attractiveness = runbothmodels(outcome = 'ippref_level_attractiveness')
```

###### Summary
```{r}
summary(model_ippref_level_attractiveness)
confint(model_ippref_level_attractiveness, level = 0.995)

```

###### Standardized Coefficients
```{r}
standardize_parameters(model_ippref_level_attractiveness, method = "basic")
ci(standardize_parameters(model_ippref_level_attractiveness, method = "basic", ci = 0.995))

```

###### Plot
```{r}
lmer(ippref_level_attractiveness ~ age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### 3.1.3. Hypotheses on financial security and successfulness. - Importance {.tabset}
3.1.3.1. There is no link between age and women’s importance ratings for partner’s financial security and successfulness (~ status-ressources).
Outcome: Importance ratings for partner’s financial security and successfulness. Predictor: Age. Random intercept and random slope for country.

###### Models
```{r}
model_ippref_financiallysecure_sussessful = runbothmodels(outcome = 'ippref_financiallysecure_sussessful')

```

###### Summary
```{r}
summary(model_ippref_financiallysecure_sussessful)
confint(model_ippref_financiallysecure_sussessful, level = 0.995)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_ippref_financiallysecure_sussessful, method = "basic")
ci(standardize_parameters(model_ippref_financiallysecure_sussessful, method = "basic", ci = 0.995))
```

###### Plot
```{r}
lmer(ippref_financiallysecure_sussessful ~ age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### 3.1.3. Hypotheses on financial security and successfulness. - Level {.tabset}
3.1.3.2. There is no link between age and women’s preferences for the levels of financial security and successfulness (~ status-ressources).
Outcome: Preferences for the levels of financial security and successfulness. Predictor: Age. Random intercept and random slope for country.

###### Models
```{r}
model_ippref_level_financiallysecure_sussessful = runbothmodels(outcome = 'ippref_level_financiallysecure_sussessful')
```

###### Summary
```{r}
summary(model_ippref_level_financiallysecure_sussessful)
confint(model_ippref_financiallysecure_sussessful, level = 0.995)

```

###### Standardized Coefficients
```{r}
standardize_parameters(model_ippref_level_financiallysecure_sussessful, method = "basic")
ci(standardize_parameters(model_ippref_level_financiallysecure_sussessful, method = "basic", ci = 0.995))
```

###### Plot
```{r}
lmer(ippref_level_financiallysecure_sussessful ~ age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### 3.1.4. Hypotheses on confidence and assertiveness. - Importance {.tabset}
3.1.4.1. There is no link between age and women’s importance ratings for partner’s confidence and assertiveness.
Outcome: Importance ratings for partner’s confidence and assertiveness. Predictor: Age. Random intercept and random slope for country.

###### Models
```{r}
model_ippref_confident_assertive = runbothmodels(outcome = 'ippref_confident_assertive')
```

###### Summary
```{r}
summary(model_ippref_confident_assertive)
confint(model_ippref_confident_assertive, level = 0.995)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_ippref_confident_assertive, method = "basic")
ci(standardize_parameters(model_ippref_confident_assertive, method = "basic", ci = 0.995))
```

###### Plot
```{r}
lmer(ippref_confident_assertive ~ age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### 3.1.4. Hypotheses on confidence and assertiveness. - Level {.tabset}
3.1.4.2. There is no link between age and women’s preferences for the levels of confidence and assertiveness.
Outcome: Preferences for the levels of confidence and assertiveness. Predictor: Age. Random intercept and random slope for country.

###### Models
```{r}
model_ippref_level_confident_assertive = runbothmodels(outcome = 'ippref_level_confident_assertive')
```

###### Summary
```{r}
summary(model_ippref_level_confident_assertive)
confint(model_ippref_level_confident_assertive, level = 0.995)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_ippref_level_confident_assertive, method = "basic")
ci(standardize_parameters(model_ippref_level_confident_assertive, method = "basic", ci = 0.995))
```

###### Plot
```{r}
lmer(ippref_level_confident_assertive ~ age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### 3.1.5. Hypotheses on education and intelligence. - Importance {.tabset}
3.1.5.1. There is no link between age and women’s importance ratings for partner’s education and intelligence.
Outcome: Importance ratings for partner’s education and intelligence. Predictor: Age. Random intercept and random slope for country.

###### Models
```{r}
model_ippref_intelligence_educated = runbothmodels(outcome = 'ippref_intelligence_educated')
```

###### Summary
```{r}
summary(model_ippref_intelligence_educated)
confint(model_ippref_intelligence_educated, level = 0.995)

```

###### Standardized Coefficients
```{r}
standardize_parameters(model_ippref_intelligence_educated, method = "basic")
ci(standardize_parameters(model_ippref_intelligence_educated, method = "basic", ci = 0.995))
```

###### Plot
```{r}
lmer(ippref_intelligence_educated ~ age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### 3.1.5. Hypotheses on education and intelligence. - Level {.tabset}
3.1.5.2. There is no link between age and women’s preferences for the levels of education and intelligence.
Outcome: Preferences for the levels of education and intelligence. Predictor: Age. Random intercept and random slope for country.

###### Models
```{r}
model_ippref_leve_intelligence_educated = runbothmodels(outcome = 'ippref_level_intelligence_educated')
model_ippref_leve_intelligence_educated = lmer(ippref_level_intelligence_educated ~ age + (1| country),
                                data = data_included_documented)
```

###### Summary
```{r}
summary(model_ippref_leve_intelligence_educated)
confint(model_ippref_leve_intelligence_educated, level = 0.995)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_ippref_leve_intelligence_educated, method = "basic")
ci(standardize_parameters(model_ippref_leve_intelligence_educated, method = "basic", ci = 0.995))

```

###### Plot
```{r}
lmer(ippref_level_intelligence_educated ~ age + (1 + age | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### 3.1.6. Hypotheses on parenting intention. - Importance Linear {.tabset}
3.1.6.1.1. There is a positive linear link between age and women’s importance rating for a partner sharing their preference for number of children.
Outcome: Importance rating for a partner sharing their preference for number of children. Predictor: Age. Random intercept and random slope for country.

###### Models
```{r}
model_pref_imp_parenting = lmer(pref_imp_parenting ~ age + (1 + age| country),
                                data = data_included_documented)
```
"Model including random slope did not converge. --> Exclude random slope."
```{r}
model_pref_imp_parenting = lmer(pref_imp_parenting ~ age + (1| country),
                                data = data_included_documented)
```

###### Summary
```{r}
summary(model_pref_imp_parenting)
confint(model_pref_imp_parenting, level = 0.995)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_imp_parenting, method = "basic")
ci(standardize_parameters(model_pref_imp_parenting, method = "basic", ci = 0.995))
```

###### Plot
```{r}
lmer(pref_imp_parenting ~ age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### 3.1.6. Hypotheses on parenting intention. - Importance Quadratic {.tabset}
3.1.6.1.2. In addition, there is a negative quadratic link between age and women’s importance rating for a partner sharing their preference for number of children.
Outcome: Importance rating for a partner sharing their preference for number of children. Predictors: Age, quadratic effect of age. Random intercept and random slope for country.
###### Models
```{r}
model_pref_imp_parenting = lmer(pref_imp_parenting ~ age + I(age^2) +
                                  (1 + age| country),
                                data = data_included_documented %>% filter(!is.na(age)))
```
"Model including random slope did not converge. --> Exclude random slope."
```{r}
model_pref_imp_parenting = lmer(pref_imp_parenting ~ age + I(age^2) +
                                  (1| country),
                                data = data_included_documented %>% filter(!is.na(age)))
```

###### Summary
```{r}
summary(model_pref_imp_parenting)
confint(model_pref_imp_parenting, level = 0.995)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_imp_parenting, method = "basic")
ci(standardize_parameters(model_pref_imp_parenting, method = "basic", ci = 0.995))
```

###### Plot
```{r}
lmer(pref_imp_parenting ~ age + I(age^2) + (1| country),
     data = data_included_documented %>% filter(!is.na(age))) %>%
  allEffects() %>%
  plot()
```

##### 3.1.6. Hypotheses on parenting intention. - Level Linear {.tabset}
3.1.6.2.1. There is a positive linear link between age and women’s preference for the level of partner’s intention to become a parent.
Outcome: Preference for the level of partner’s intention to become a parent. Predictor: Age. Random intercept and random slope for country.

###### Models
```{r}
model_pref_level_parenting = lmer(pref_level_parenting ~ age + (1 + age| country),
                                data = data_included_documented)
```
"Model including random slope did not converge. --> Exclude random slope."
```{r}
model_pref_level_parenting = lmer(pref_level_parenting ~ age + (1| country),
                                data = data_included_documented)
```

###### Summary
```{r}
summary(model_pref_level_parenting)
confint(model_pref_level_parenting, level = 0.995)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_level_parenting, method = "basic")
ci(standardize_parameters(model_pref_level_parenting, method = "basic", ci = 0.995))
```

###### Plot
```{r}
lmer(pref_level_parenting ~ age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### 3.1.6. Hypotheses on parenting intention. - Level Quadratic {.tabset}
3.1.6.2.2. In addition, there is a negative quadratic link between age and women’s preference for the level of partner’s intention to become a parent.
Outcome: Preference for the level of partner’s intention to become a parent. Predictors: Age, quadratic effect of age. Random intercept and random slope for country.

###### Models
```{r}
model_pref_level_parenting = lmer(pref_level_parenting ~ age + I(age^2) + (1 + age| country),
                                data = data_included_documented %>% filter(!is.na(age)))
```
"Model including random slope did not converge. --> Exclude random slope."
```{r}
model_pref_level_parenting = lmer(pref_level_parenting ~ age + I(age^2) + (1| country),
                                data = data_included_documented %>% filter(!is.na(age)))
```

###### Summary
```{r}
summary(model_pref_level_parenting)
confint(model_pref_level_parenting, level = 0.995)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_level_parenting, method = "basic")
ci(standardize_parameters(model_pref_level_parenting, method = "basic", ci = 0.995))
```

###### Plot
```{r}
lmer(pref_level_parenting ~ I(age^2) + (1| country),
     data = data_included_documented %>% filter(!is.na(age))) %>%
  allEffects() %>%
  plot()
```

#### Age Range {.tabset}
##### Age Range {.tabset}
3.2.1. There is no link between age and age-range deemed acceptable by women in an ideal partner.
Outcome: Age-range deemed acceptable. Predictor: Age. Random intercept and random slope for country.
###### Models
```{r}
model_pref_age_range = runbothmodels(outcome = 'pref_age_range')
```

###### Summary
```{r}
summary(model_pref_age_range)
confint(model_pref_age_range, level = 0.995)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_age_range, method = "basic")
ci(standardize_parameters(model_pref_age_range, method = "basic", ci = 0.995))
```

###### Plot
```{r}
lmer(pref_age_range ~ age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```

##### Youngest Age acceptable {.tabset}
3.2.2. There is a positive link between age and youngest age deemed acceptable by women in an ideal partner.
Outcome: Youngest age deemed acceptable relative to own age. Predictor: Age. Random intercept and random slope for country.

###### Models
```{r}
model_pref_age_min_rel = runbothmodels(outcome = 'pref_age_min_rel')
```

###### Summary
```{r}
summary(model_pref_age_min_rel)
confint(model_pref_age_min_rel, level = 0.995)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_age_min_rel, method = "basic")
ci(standardize_parameters(model_pref_age_min_rel, method = "basic", ci = 0.995))
```

###### Plot
```{r}
lmer(pref_age_min_rel ~ age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```


##### Oldest Age acceptable {.tabset}
3.2.3. There is a negative link between age and oldest age deemed acceptable by women in an ideal partner.
Outcome: Oldest age deemed acceptable relative to own age. Predictor: Age. Random intercept and random slope for country.

###### Models
```{r}
model_pref_age_max_rel = runbothmodels(outcome = 'pref_age_max_rel')
```

###### Summary
```{r}
summary(model_pref_age_max_rel)
confint(model_pref_age_max_rel, level = 0.995)
```

###### Standardized Coefficients
```{r}
standardize_parameters(model_pref_age_max_rel, method = "basic")
ci(standardize_parameters(model_pref_age_max_rel, method = "basic", ci = 0.995))
```

###### Plot
```{r}
lmer(pref_age_max_rel ~ age + (1 | country),
       data = data_included_documented) %>%
    allEffects() %>%
    plot()
```
